### 2014-10-23 writeups/data_sources.tex
start some writtings

\documentclass[]{article}

\usepackage{amsmath, amsfonts, amsthm, amssymb}

% bibliography
\usepackage{natbib}
% \bibpunct{(}{)}{;}{a}{}{,}

%opening
\title{}
\author{}

\begin{document}

\maketitle

\begin{abstract}
Discuss my data sources
\end{abstract}

\section{Ethnic fractionalization}

\cite[p. 190]{Gandhi2008}. (1946-2002, but constant across the period). Degree of polarization among a country's ethnic groups. Calculated as $1 - \sum(0.5 - p_i)^2 \times \frac{p_i}{0.25}$, where$p_i$ is the share of the population that belongs to ethnic group $i$, as defined and measured in \cite{Fearon2003} (which also gives a number to a country instead of time series).

\section{Violence}

\section{Other democracies}

Polity IV (1800 - 2012), \verb`polity_binary` is created as \verb`Polity2` $> 0$.

Democracy and Dictatorship (1946 - 2008)

\bibliographystyle{chicago}
\bibliography{library}

\end{document}

### 2014-10-23 writeups/multilevel.tex

\documentclass[12pt]{article}

% This first part of the file is called the PREAMBLE. It includes
% customizations and command definitions. The preamble is everything
% between \documentclass and \begin{document}.

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath}               % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments

% various theorems, numbered by section

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}

\DeclareMathOperator{\id}{id}

\newcommand{\bd}[1]{\mathbf{#1}}  % for bolding symbols
\newcommand{\RR}{\mathbb{R}}      % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}}      % for Integers
\newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}

\begin{document}

\nocite{*}

\title{A Sample Mathematics Paper}

\author{Anh Le\thanks{Grant support listed here.} \\ 
Department of Political Science \\
Duke University \\
Durham, NC 27708 USA}

\maketitle

\begin{abstract}
  Mathematical model of my authoritarian violence paper
\end{abstract}

\section{Multilevel model with instrumental variable}

Unit indexed by $i$, group indexed by $j$. Model with treatment $T$ and IV $z$ both at the group level. There are also covariates at the group level, and none at the individual level.

\begin{align}
y_i &\sim N(\alpha_{j[i]}, \sigma_y^2) \\
\col{\alpha_j \\ T_j} &\sim 
N \left(
    \col{\gamma_0 + \gamma_1 T_j + \gamma_2 x_j\\\mu_0 + \mu_1 z_j} ,
    \left[
    \begin{matrix}
      \sigma^2_\alpha & \rho \sigma_\alpha \sigma_T \\
      \rho \sigma_\alpha \sigma_T & \sigma^2_T
    \end{matrix}
    \right]
\right)
\end{align}

In our paper,

\begin{align}
T_j &= \text{legislature in country-year}_j \\
z_j &= \text{inherited parties in country-year}_j \\
x_j &= \text{other covariates in country-year}_j
\end{align}

Notice that in the model, $T_j$ is not assumed to be uncorrelated with the error term of $\alpha_j$ (the non-diagonal covariance is non-zero), but $z_j$ is (implicitly since it's un-modeled). Writing it out in non-multilevel form:

\begin{align}
\alpha_j &= \gamma_0 + \gamma_1 T_j + \gamma_2 x_j + \epsilon_\alpha = N(\gamma_0 + \gamma_1 T_j + \gamma_2 x_j, \sigma_\alpha)\\
T_j &= \mu_0 + \mu_1 + \epsilon_T = N(\mu_0 + \mu_1, \sigma_T)
\end{align}

In the multilevel model, we allow $T_j$ to be correlated with $\epsilon_\alpha$ via $\rho \sigma_\alpha \sigma_T$

\end{document}

### 2014-10-23 R/instrumental_variable.R
first stab at IV model

@@ -1,10 +1,10 @@
 # ---- Set up workspace ----
 rm(list=ls())
 source("./R/functions.R")
-packs <- c("WDI", "psData", "foreign", "countrycode", "MatchIt", "Amelia", "plyr", "dplyr")
+packs <- c("WDI", "psData", "foreign", "countrycode", "RMySQL", "sem", "plyr", "dplyr", "plm")
 f_install_and_load(packs) ; rm(packs)
 
-# ---- Load data ----
+# ---- Weak instrument test (Gandhi data) ----
 d_gandhi_raw <- read.csv("./data/private/Pol_Inst_Dictatorship_Data.csv")
 d_gandhi <- d_gandhi_raw %>% 
   filter(Year >= 1991) %>%
@@ -13,16 +13,14 @@ d_gandhi <- d_gandhi_raw %>%
   mutate(year = Year) %>%
   select(-Capital.stock.growth, -Labor.force.growth, -Education.growth)
 
-# ---- Weak instrument test ----
 
 m_ftest <- lm(Institutions ~ Other.democracies, data=d_gandhi)
 summary(m_ftest)
-
 m_ftestbinary <- lm(Institutions.binary ~ Other.democracies, data=d_gandhi)
-summary(m_ftestbinary)
+summary(m_ftestbinary) # F statistic = 30, > 10 --> OK
 
-# ---- Construct my own data ----
-d_dd <- read.dta("./data/public//ddrevisited_data_v1.dta") # Only cover upto 2008
+# ---- Weak instrument test (Polity data) ----
+# d_dd <- read.dta("./data/public//ddrevisited_data_v1.dta") # Only cover upto 2008
 
 # Calculate other democracies percentage
 d_polity_raw <- PolityGet(vars="polity2")
@@ -35,6 +33,58 @@ d_dpi <- d_dpi_raw  %>%
   mutate(liec7 = ifelse(liec >= 7, 1, 0))
 
 d_iv_test <- merge(d_dpi, d_other_dem, by=c("year"), all=T)
-
+# Run test
 summary(lm(liec7 ~ Other.democracies, data=d_iv_test))
 summary(lm(liec7 ~ Other.democracies, data=filter(d_iv_test, year >= 1991)))
+with(d_iv_test, cor(liec7, Other.democracies, use="complete.obs"))
+with(filter(d_iv_test, year >= 1991), cor(liec7, Other.democracies, use="complete.obs"))
+
+# ----- Instrumental variable regression ----
+# Download violence data
[…]

### 2014-10-24 R/functions.R
instrumental variable with longer data 1991 - 2010

@@ -25,3 +25,32 @@ f_stata_to_df <- function(df) {
                        var.label = attr(d_tmp, "var.labels"))
   return(lab_df)
 }
+
+# Re-order columns
+# http://stackoverflow.com/questions/18339370/reordering-columns-in-a-large-dataframe
+moveMe <- function(data, tomove, where = "last", ba = NULL) {
+  temp <- setdiff(names(data), tomove)
+  x <- switch(
+    where,
+    first = data[c(tomove, temp)],
+    last = data[c(temp, tomove)],
+    before = {
+      if (is.null(ba)) stop("must specify ba column")
+      if (length(ba) > 1) stop("ba must be a single character string")
+      data[append(temp, values = tomove, after = (match(ba, temp)-1))]
+    },
+    after = {
+      if (is.null(ba)) stop("must specify ba column")
+      if (length(ba) > 1) stop("ba must be a single character string")
+      data[append(temp, values = tomove, after = (match(ba, temp)))]
+    })
+  x
+}
+
+# Check if all rows are unique
+f_is_unique <- function(df, vars=NULL) {
+  if (!(is.null(vars))) {
+    df <- df[, vars]
+  }
+  nrow(df) == nrow(unique(df))
+}

### 2014-11-06 data/public/GWF_Autocratic_Regimes_1_2/README.tex
add Makefile, change script to match data folder

``New Data on Autocratic Breakdown and Regime Transitions''

Version 1.2 June 23, 2012

Barbara Geddes, UCLA 
Joseph Wright, Pennsylvania State
Erica Frantz, Bridgewater State

Corresponding author: Joe Wright (josephgwright@gmail.com)

GWF Codebook.pdf		contains definitions coding rules; explanations of difficult cases; and narratives of regime Start and End events

GWF Autocratic Regimes:

	GWF Autocratic Regimes.xls 	contains three tabs: a list of regime cases; tables for the codebook; and TSCS data

	GWFtscs.txt					contains the regime TSCS data in a txt file

	GWFcases.dta				contains the regime cases in a Stata file

	GWFtscs.dta					contains the regime TSCS data in a Stata file

	clean.do						Stata code to transform the list of cases into TSCS data

GWF All Political Regimes:

	GWF All Political Regimes Case List.xls		contains a list of all political regimes that includes autocratic regime types and democracies

	GWF_AllPoliticalRegimes.dta				contains TSCS data on all political regimes (autocratic regime types and democracies)

	GWF_AllPoliticalRegimes.txt				contains TSCS data on all political regimes (autocratic regime types and democracies)

Research for this project is supported by the National Science Foundation (BCS-0904478 and BCS-090463).

Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) 
and do not necessarily reflect the views of the National Science Foundation.

### 2014-11-06 data/public/GWF_Autocratic_Regimes_1_2/UPDATES.tex
add Makefile, change script to match data folder

Data first made publicly available in October 2012 (Version 1.0)

CORRECTIONS in Feburary 2013 (Version 1.1):

(1) 2/22/13: Corrected Paraguay 1939-1948; it was 1940-1948 now it is 1939-1948; corrected start year, duration spell, and duration time

(2) 2/22/13: Corrected Greece 1948-1967; it was coded democracy from Jan 1 1948 to Jan 1 1967; now correctly coded democracy from Jan 1 1947 to Jan 1 1967. Updated Global case list and Global regimes. (h/t Kerim Can Kavakli)

CORRECTIONS in June 2014 (Version 1.2):

(3) 6/20/14: Corrected Togo 1967-; it was coded democracy from Jan 1 1964 to Jan 1 1967; now correctly coded as autocratic from Jan 13, 1963 coup led by ex-Sgt Eyadema; the May 1963 election of Grunitzkey was not democratic. A New York Times article states: "With only a single slate of candidates yesterday, the result was a foregone conclusion."  ("Grunitzky Is Declared Winner in Togo's Election" New York Times, May 7 1963.)  First (1970, 207 ) writes: ``The army installed a civilian government, presided over by Olympia's political rival, Nicholas Grunitzky. Bodjolle made himself colonel, commander and chief-of-staff, while a former sergeant in the French army, Etienne Eyadema (who, it is widely believed, fired the shots that killed Olympio) became a major in an army expanded to 1,200 men. Two years later Eyadema ousted Bodjolle, to make himself colonel and commander, and subsequently to become Togo's head of state.'' (h/t Tyson Chandler)

(4) 6/20/14: Corrected Iran 1925-1979; previously the clean.do code and thus the GWFtscs.txt & GWFtscs.dta files had this regime incorrectly coded as gwf_party and gwf_monarch; only the latter is correct; all the GWFglobal data was correct (h/t Wonjun Song)

(5) 6/20/14: Corrected El Salvador 1932-1948; previously was military in GWFcases.dta and GWF Autocratic Regimes.xls but should be military-personal; this information was correct in the GWFglobal data (h/t Brett Ashley Leeds)

(6) 6/20/14: Corrected Cambodia 53-70 end date from March 17 to March 18, 1970; also corrected this date for the Cambodia 70-75 start date; GWFglobal data does not contain start dates so was not updated  (h/t John Chen) "Shinaouk Reported Out in a Coup By His Premier". New York Times, March 18, 1970 (page 1): "Prince Norodom Sihanouk... was overthrown today in his absence, the Pnompenh radio announced."

(7) 6/20/14: JW checked that all data has the correct date for end of the Mauritania 60-78 regime: it is July 10, 1978.  There do not appear to be any instances where this date was incorrectly entered as October 7, 1978. (h/t John Chen)

### 2014-11-06 R/0_clean_actorlevel.R

@@ -54,7 +54,7 @@ d_wdi <- d_wdi_raw %>%
 
 # ---- Load Geddes autocracy type data ----
 # emil, royal, otherwise civilian
-d_geddes_raw <- read.table("./data/public/GWF Autocratic Regimes 1.2/GWF_AllPoliticalRegimes.txt", 
+d_geddes_raw <- read.table("./data/public/GWF_Autocratic_Regimes_1_2/GWF_AllPoliticalRegimes.txt", 
                            header=TRUE, sep="\t")
 d_geddes <- d_geddes_raw %>%
   mutate(iso3c = countrycode(cowcode, "cown", "iso3c")) %>%
@@ -96,3 +96,4 @@ d_exp_before_trans_full <- Reduce(function(...) merge(..., match=c("iso3c", "yea
 # ---- Save cleaned data ----
 save(d_disgov_merged_full, d_disgovsect_merged_full, d_exp_before_trans_full,
      file='./data/private/actorsectlevel.RData')
+

### 2014-11-06 R/functions.R

@@ -1,7 +1,7 @@
 # Install and load packages
 f_install_and_load <- function(packs) {
   new.packs <- packs[!(packs %in% installed.packages()[ ,"Package"])]
-  lapply(new.packs, install.packages, repos="http://cran.rstudio.com/")
+  lapply(new.packs, install.packages, repos="http://cran.rstudio.com/", dependencies=TRUE)
   lapply(packs, library, character.only=TRUE)
 }
 

### 2014-11-08 R/0_clean_countrylevel.R
working on matching panel

@@ -35,11 +35,11 @@ d_wdi <- d_wdi_raw %>%
   arrange(iso3c, year)
 
 # Geddes data: authoritarian type (1946 - 2010)
-d_geddes_raw <- read.table("./data/public/GWF Autocratic Regimes 1.2/GWF_AllPoliticalRegimes.txt", 
+d_geddes_raw <- read.table("./data/public/GWF_Autocratic_Regimes_1_2/GWF_AllPoliticalRegimes.txt", 
                            header=TRUE, sep="\t")
 d_geddes <- d_geddes_raw %>%
   mutate(iso3c = countrycode(cowcode, "cown", "iso3c")) %>%
-  select(iso3c, year, country=gwf_country, 
+  select(iso3c, year,
          gwf_military, gwf_personal, gwf_party, gwf_monarchy)
 
 # Gandhi data: fractionalization
@@ -59,10 +59,10 @@ qr_disgov = dbSendQuery(db.my_tables, "SELECT * FROM anh_dis_and_gov_aggregate_c
 d_disgov_raw = fetch(qr_disgov, n=-1)
 d_disgov <- d_disgov_raw %>%
   select(iso3c = country_ISOA3Code, year,
-         country = country_name,
          goldstein_avg, goldstein_sum, goldstein_pos_count, goldstein_neg_count)
 
 # ---- Merge data ----
+
 d_merged <- Reduce(function(...) merge(..., by=c("iso3c", "year"), sort=T),
                    list(d_disgov, d_dpi, d_wdi, d_geddes)) %>%
   mutate(country = country.x) %>%

### 2014-11-08 R/1_analysis.R

@@ -6,7 +6,7 @@ source("./R/functions.R")
 packs <- c("lme4", "arm", "nlme", "plyr", "dplyr", "ggplot2")
 f_install_and_load(packs)
 # Load data
-load('./data/private/data_final.RData')
+load('./data/private/actorsectlevel.RData')
 
 # Rescale data
 vars <- c("liec", "legis_multi", "gdp", "gdppc", "milexp", 

### 2014-11-08 R/matching.R

@@ -1,9 +1,86 @@
+# ---- Plan ----
+# We match on country level characteristics, get the id of the treated and untreated
+# Then go back to actor level dataset with those id
+# --------------
+
 # ---- Set up workspace ----
 rm(list=ls())
+# Load external functions
 source("./R/functions.R")
-packs <- c("plyr")
-f_install_and_load(packs) ; rm(packs)
+# Load packages
+packs <- c("plyr", "dplyr", "ggplot2")
+f_install_and_load(packs)
 
-# ---- Load data ----
+# Load data
+load('./data/private/countrylevel.RData')
 
-load("./data/private/countrylevel.RData")
+f_turn_country_into_panel <- function(df, t=5, idvar="country", timevar="year", drop=NULL) {
+  n <- length(unique(df$year))
+  # Create moving windows of length t. First window starts at 1, last window starts at n - t + 1
+  idx <- lapply(1:(n-t+1), FUN=`+`, 0:(t-1))
+  # Create a list of short panels
+  short_panels <- lapply(idx, function(i) 
+    data.frame(df[i, setdiff(names(df), "year")], year=0:4))
+  # Name that list
+  names(short_panels) <- df$year[1:(n-4)]
+  # Convert each short panel in the list from long to wide
+  widened_short_panels <- lapply(short_panels, reshape, 
+                                 idvar=idvar, timevar=timevar, drop=drop, direction="wide")
+  # rbind and returns those widened panels
+  res <- do.call(rbind, args=widened_short_panels)
+  res <- data.frame(start.year = rownames(res), res)
+  return(res)
+}
+
+d_long <- select(d_countrylevel, country, year, goldstein_avg, resource.pc,
+                               land, population, gdp, gdppc, milexp.pc, 
+                               gwf_military, gwf_personal, gwf_party, gwf_monarchy,
+                               ethnic.polarization)
+
+d_wide <- ddply(d_long, .(country),
+             f_turn_country_into_panel, t=5, idvar="country", timevar="year")
+d_wide <- merge(d_wide, d_countrylevel[ , c("country", "year", "liec7")], 
+                     by.x=c("country", "start.year"), by.y=c("country", "year"))
+d_wide <- na.omit(d_wide)
+
+# Model propensity
[…]

### 2014-11-17 R/multilevel.R
switch to using loop to set prior distribution

@@ -19,12 +19,12 @@ d_eventlevel <- na.omit(d_eventlevel)
 # ---- Set up index link ----
 d_countryyear <- unique(select(d_eventlevel,
                                countryyear, country, resource.pc, milexp.pc,
-                               liec, liec5, liec6, liec7, 
+                               liec, liec5, liec6, liec7,
                                gwf_military, gwf_party, gwf_personal, gwf_duration))
 d_country <- unique(select(d_eventlevel, 
                            country, ethnic.polarization, region))
 d_event <- unique(select(d_eventlevel,
-                         event_id, countryyear, goldstein))
+                         event_id, countryyear, goldstein, dissident_sector_name))
 
 N <- nrow(d_event)
 J <- nrow(d_countryyear)
@@ -42,24 +42,21 @@ for (k in (1:K)) {
 # ---- Set up data ----
 goldstein <- d_event$goldstein
 liec <- d_countryyear$liec6
-milexp.pc <- d_countryyear$milexp.pc
-resource.pc <- d_countryyear$resource.pc
-duration <- d_countryyear$gwf_duration
-military <- d_countryyear$gwf_military
-personal <- d_countryyear$gwf_personal
-party <- d_countryyear$gwf_party
+Xa <- with(d_countryyear, 
+           cbind.data.frame(milexp.pc, resource.pc, gwf_duration, 
+                            gwf_military, gwf_personal, gwf_party))
 ethnic <- d_country$ethnic.polarization
 
 # Set up JAGS model
 # JAGS needs a list of names that contain the data
-reg.data = list("goldstein", "liec", "milexp.pc", "resource.pc", "duration","ethnic",
-                "military", "personal", "party",
+reg.data = list("goldstein", "liec", "Xa",
+                "ethnic",
                 "countryyear.idx", "country.idx",
                 "N", "J", "K")
 
 # JAGS also needs a list of names of parameters
 reg.params = c("a", "sigma.goldstein", "phi.goldstein",
-               "b", "g.liec", "g.mil", "g.res", "g.dur", "g.military", "g.personal", "g.party", "sigma.a", "phi.a",
+               "b", "g.liec", "G", "sigma.a", "phi.a",
[…]

### 2014-11-17 R/multilevel.R
add sector covariates to event level

@@ -41,21 +41,26 @@ for (k in (1:K)) {
 
 # ---- Set up data ----
 goldstein <- d_event$goldstein
-liec <- d_countryyear$liec6
+liec <- d_countryyear$liec5
 Xa <- with(d_countryyear, 
            cbind.data.frame(milexp.pc, resource.pc, gwf_duration, 
                             gwf_military, gwf_personal, gwf_party))
+dimXa <- dim(Xa)
+
+Xgoldstein <- model.matrix(~ dissident_sector_name - 1, data=d_event)[, -1]
+dimXgoldstein <- dim(Xgoldstein)
+
 ethnic <- d_country$ethnic.polarization
 
 # Set up JAGS model
 # JAGS needs a list of names that contain the data
-reg.data = list("goldstein", "liec", "Xa",
+reg.data = list("goldstein", "Xgoldstein", "dimXgoldstein",
+                "liec", "Xa", "dimXa",
                 "ethnic",
-                "countryyear.idx", "country.idx",
-                "N", "J", "K")
+                "countryyear.idx", "country.idx", "N", "J", "K")
 
 # JAGS also needs a list of names of parameters
-reg.params = c("a", "sigma.goldstein", "phi.goldstein",
+reg.params = c("a", "A", "sigma.goldstein", "phi.goldstein",
                "b", "g.liec", "G", "sigma.a", "phi.a",
                "d.ethnic", "sigma.b", "phi.b")
 
@@ -67,10 +72,14 @@ reg.params = c("a", "sigma.goldstein", "phi.goldstein",
 reg.model <- function() {
   # Model structure
   for (i in 1:N){
-    goldstein[i] ~ dnorm(a[countryyear.idx[i]], sigma.goldstein)
+    goldstein[i] ~ dnorm(a[countryyear.idx[i]] + A %*% Xgoldstein[i, ], 
+                         sigma.goldstein)
   }
   sigma.goldstein <- 1 / phi.goldstein
   phi.goldstein ~ dgamma(1, 1)
+  for (i in 1:dimXgoldstein[2]) {
+    A[i] ~ dnorm(0, .0001)
+  }
   
   for (j in 1:J) {
     a[j] ~ dnorm(b[country.idx[j]] + g.liec*liec[j] + G %*% Xa[j, ], 
@@ -79,7 +88,7 @@ reg.model <- function() {
   sigma.a <- 1 / phi.a
   phi.a ~ dgamma(1, 1)
[…]

### 2014-11-18 R/functions.R
checking balance on experimental data

@@ -21,8 +21,8 @@ f_stata_to_env <- function(df) {
 }
 
 f_stata_to_df <- function(df) {
-  lab_df <- data.frame(var.name = names(d_tmp),
-                       var.label = attr(d_tmp, "var.labels"))
+  lab_df <- data.frame(var.name = names(df),
+                       var.label = attr(df, "var.labels"))
   return(lab_df)
 }
 

### 2014-11-18 R/pci_experiment.R

@@ -1,0 +1,74 @@
+# ---- Set up workspace ----
+rm(list=ls())
+# Load external functions
+source("./R/functions.R")
+# Load packages
+packs <- c("foreign", "Matching", "lme4", "plyr", "dplyr")
+f_install_and_load(packs)
+
+# ---- Constants ----
+c_northprovinces <- c("Ha Giang", "Cao Bang", "Lai Chau", "Lao Cai", "Yen Bai", 
+                      "Tuyen Quang", "Bac Kan", "Thai Nguyen", "Lang Son",
+                      "Son La", "Phu Tho", "Vinh Phuc", "Ha Noi", "Bac Ninh", 
+                      "Bac Giang", "Quang Ninh", "Hai Phong", "Hai Duong", "Ha Nam", 
+                      "Nam Dinh", "Thai Binh", "Ninh Binh")
+c_southprovinces <- c("Lam Dong", "Ninh Thuan", "Binh Thuan", "Tay Ninh", "Binh Phuoc",
+                      "Binh Duong", "TP HCM", "Dong Nai", "BRVT", "Long An", "Dong Thap",
+                      "Tien Giang", "Ben Tre", "Tra Vinh", "Vinh Long", "An Giang", "Can Tho",
+                      "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang")
+
+# ---- Load data ----
+
+d_pci <- read.dta("./data/private/PCI2014_DDI_cleanJ.dta")
+d_lab <- f_stata_to_df(d_pci)
+
+d_pci <- d_pci %>% 
+  mutate(treat = ifelse(form=="B", 1, 0)) %>%
+  mutate(whether.north = ifelse(province %in% c_northprovinces, 1, 
+                                ifelse(province %in% c_southprovinces, 0, NA))) %>%
+  mutate(communication = ifelse(i_4_1=="Yes", 1, ifelse(i_4_1=="No", 0, NA))) %>%
+  mutate(representation = ifelse(i_4_2=="Yes", 1, ifelse(i_4_2=="No", 0, NA)))
+# ---- Check balance ----
+
+MatchBalance(treat ~ a7_1 + a8_1,data = d_pci)
+
+m_bal_comm <- MatchBalance(treat ~ a4 + a5_1 + a5_2 + a5_3 + a5_4 + a5_5 + 
+                a7_1 + a8_1, data=filter(d_pci, !is.na(communication)))$BeforeMatching
+
+with(d_pci, levels)
[…]

### 2014-11-18 R/functions.R
interacting survey treatment with covariates

@@ -193,3 +193,32 @@ f_pad_countryyear <- function(df, idvar="country", timevar="year") {
   colnames(res) <- c(idvar, timevar)
   return(res)
 }
+
+# Get level names from variables (for balance table)
+f_getlevelnames <- function(df, vars) {
+  unlist(sapply(vars, function(var) paste(var, levels(df[ , var])[-1], sep="_")))
+}
+
+# Add significance level star to table
+f_addstar <- function(df, pvaluevar="p.value") {
+  pval <- df[ , pvaluevar]
+  if (is.null(pval)) {
+    stop("Variable not found.")
+  } else {
+    stars <- ifelse(pval <= .001, "***",
+                    ifelse(pval <= .05, "**",
+                           ifelse(pval <= .1, "*", "")))
+  }
+  return(cbind.data.frame(df, stars))
+}
+
+# Create a balance table based on MatchBalance result
+f_create_balancetable <- function(df, balance_vars, bal_result) {
+  f_addstar(
+    cbind.data.frame(
+      f_getlevelnames(d_pci, balance_vars),
+      ldply(bal_result, function(x) 
+        data.frame(mean.Tr=x$mean.Tr, mean.Co=x$mean.Co, p.value=x$p.value))
+    )
+  ) 
+}

### 2014-11-18 R/pci_experiment.R

@@ -24,40 +24,63 @@ d_lab <- f_stata_to_df(d_pci)
 
 d_pci <- d_pci %>% 
   mutate(treat = ifelse(form=="B", 1, 0)) %>%
-  mutate(whether.north = ifelse(province %in% c_northprovinces, 1, 
-                                ifelse(province %in% c_southprovinces, 0, NA))) %>%
+  mutate(whether.north = as.factor(ifelse(province %in% c_northprovinces, 1, 
+                                ifelse(province %in% c_southprovinces, 0, NA)))) %>%
   mutate(communication = ifelse(i_4_1=="Yes", 1, ifelse(i_4_1=="No", 0, NA))) %>%
-  mutate(representation = ifelse(i_4_2=="Yes", 1, ifelse(i_4_2=="No", 0, NA)))
+  mutate(representation = ifelse(i_4_2=="Yes", 1, ifelse(i_4_2=="No", 0, NA))) %>%
+  mutate(responded.comm = ifelse(!is.na(communication), 1, 0)) %>%
+  mutate(responded.rep = ifelse(!is.na(representation), 1, 0))
+           
+
 # ---- Check balance ----
 
-MatchBalance(treat ~ a7_1 + a8_1,data = d_pci)
+c_balance_vars <- c("a4", "a5_1", "a5_2", "a5_3", "a5_4", "a5_5", "a7_1", "a8_1",
+                    "a13_1", "a13_2", "a13_3", "a14_1", "a14_2", "a14_3", "a14_4", 
+                    "a14_5", "a14_6", "whether.north")
+fm_balance <- as.formula(paste("treat ~", paste(c_balance_vars, collapse=" + ")))
 
-m_bal_comm <- MatchBalance(treat ~ a4 + a5_1 + a5_2 + a5_3 + a5_4 + a5_5 + 
-                a7_1 + a8_1, data=filter(d_pci, !is.na(communication)))$BeforeMatching
+# Balance among those responded to communication question
+m_bal_comm <- MatchBalance(fm_balance,
+                data=filter(d_pci, !is.na(communication)))$BeforeMatching
+f_create_balancetable(df=d_pci, balance_vars=c_balance_vars, bal_result=m_bal_comm)
 
-with(d_pci, levels)
-cbind.data.frame(c(levels(d_pci$a7_1)[-1], levels(d_pci$a8_1)[-1]),
-  ldply(m_bal_comm, function(x) data.frame(mean.Tr=x$mean.Tr, mean.Co=x$mean.Co,
[…]

### 2014-11-19 R/functions.R
add matching for experimental design

@@ -216,7 +216,7 @@ f_addstar <- function(df, pvaluevar="p.value") {
 f_create_balancetable <- function(df, balance_vars, bal_result) {
   f_addstar(
     cbind.data.frame(
-      f_getlevelnames(d_pci, balance_vars),
+      f_getlevelnames(df, balance_vars),
       ldply(bal_result, function(x) 
         data.frame(mean.Tr=x$mean.Tr, mean.Co=x$mean.Co, p.value=x$p.value))
     )

### 2014-11-19 R/pci_experiment.R

@@ -3,7 +3,7 @@ rm(list=ls())
 # Load external functions
 source("./R/functions.R")
 # Load packages
-packs <- c("foreign", "Matching", "lme4", "plyr", "dplyr")
+packs <- c("arm", "foreign", "Matching", "lme4", "plyr", "dplyr")
 f_install_and_load(packs)
 
 # ---- Constants ----
@@ -21,6 +21,7 @@ c_southprovinces <- c("Lam Dong", "Ninh Thuan", "Binh Thuan", "Tay Ninh", "Binh 
 
 d_pci <- read.dta("./data/private/PCI2014_DDI_cleanJ.dta")
 d_lab <- f_stata_to_df(d_pci)
+d_distance <- read.csv("./data/public/distance_from_hanoi.csv")
 
 d_pci <- d_pci %>% 
   mutate(treat = ifelse(form=="B", 1, 0)) %>%
@@ -29,14 +30,15 @@ d_pci <- d_pci %>%
   mutate(communication = ifelse(i_4_1=="Yes", 1, ifelse(i_4_1=="No", 0, NA))) %>%
   mutate(representation = ifelse(i_4_2=="Yes", 1, ifelse(i_4_2=="No", 0, NA))) %>%
   mutate(responded.comm = ifelse(!is.na(communication), 1, 0)) %>%
-  mutate(responded.rep = ifelse(!is.na(representation), 1, 0))
-           
+  mutate(responded.rep = ifelse(!is.na(representation), 1, 0)) %>%
+  inner_join(d_distance, by=c("province")) %>%
+  rename(distance.from.hn = distance)
 
 # ---- Check balance ----
 
-c_balance_vars <- c("a4", "a5_1", "a5_2", "a5_3", "a5_4", "a5_5", "a7_1", "a8_1",
-                    "a13_1", "a13_2", "a13_3", "a14_1", "a14_2", "a14_3", "a14_4", 
-                    "a14_5", "a14_6", "whether.north")
+c_balance_vars <- c("a4", "a5_1", "a5_2", "a5_3", "a5_4", "a5_5", "a7_1", "a8_1", "a11",
+                    "a13_1", "a13_2", "a13_3", "a13_4", "a13_5", "a14_1", "a14_2", "a14_3", "a14_4", 
+                    "a14_5", "a14_6")
 fm_balance <- as.formula(paste("treat ~", paste(c_balance_vars, collapse=" + ")))
 
[…]

### 2014-11-19 R/pci_experiment.R
genetic matching for pci experiment

@@ -3,7 +3,7 @@ rm(list=ls())
 # Load external functions
 source("./R/functions.R")
 # Load packages
-packs <- c("arm", "foreign", "Matching", "lme4", "plyr", "dplyr")
+packs <- c("arm", "foreign", "snow", "Matching", "lme4", "plyr", "dplyr")
 f_install_and_load(packs)
 
 # ---- Constants ----
@@ -88,10 +88,10 @@ ranef(m_whether.north)
 
 # ---- Matching to see if effect changes ----
 d_pci_match <- na.omit(d_pci[ , c("treat", c_balance_vars)])
-d_pci_match[ , which(sapply(d_pci_match, is.factor))] <- lapply(d_pci_match[ , which(sapply(d_pci_match, is.factor))], as.numeric)
 Tr <- d_pci_match[ , "treat"]
-X <- d_pci_match[ , c_balance_vars]
-gen1 <- GenMatch(Tr=Tr, X=X, pop.size=10000)
+X <- model.matrix(as.formula(paste("~", paste(c_balance_vars, collapse=" + "))), 
+                  data=d_pci_match)[ , -1]
+gen1 <- GenMatch(Tr=Tr, X=X, BalanceMatrix=X, pop.size=10000)
 mgen1 <- Match(Tr=Tr, X=X, Weight.matrix=gen1)
 MatchBalance(fm_balance, data=d_pci_match, match.out=mgen1, nboots=1000)
 

### 2014-11-20 R/pci_experiment.R
ran pci matching

@@ -3,7 +3,7 @@ rm(list=ls())
 # Load external functions
 source("./R/functions.R")
 # Load packages
-packs <- c("arm", "foreign", "Matching", "lme4", "plyr", "dplyr")
+packs <- c("arm", "foreign", "snow", "Matching", "lme4", "plyr", "dplyr")
 f_install_and_load(packs)
 
 # ---- Constants ----
@@ -32,7 +32,8 @@ d_pci <- d_pci %>%
   mutate(responded.comm = ifelse(!is.na(communication), 1, 0)) %>%
   mutate(responded.rep = ifelse(!is.na(representation), 1, 0)) %>%
   inner_join(d_distance, by=c("province")) %>%
-  rename(distance.from.hn = distance)
+  rename(distance.from.hn = distance) %>%
+  mutate(province = as.factor(province))
 
 # ---- Check balance ----
 
@@ -78,7 +79,7 @@ summary(glm(communication ~ treat + whether.north + whether.north:treat, data=d_
 
 # ---- Heterogeneity analysis ----
 
-m_whether.north <- glmer(communication ~ treat + (1 + treat | whether.north), 
+m_whether.north <- glmer(communication ~ treat + (1 + treat | province), 
                          data=d_pci, family="binomial")
 summary(m_whether.north)
 
@@ -91,7 +92,9 @@ d_pci_match <- na.omit(d_pci[ , c("treat", c_balance_vars)])
 d_pci_match[ , which(sapply(d_pci_match, is.factor))] <- lapply(d_pci_match[ , which(sapply(d_pci_match, is.factor))], as.numeric)
 Tr <- d_pci_match[ , "treat"]
 X <- d_pci_match[ , c_balance_vars]
-gen1 <- GenMatch(Tr=Tr, X=X, pop.size=10000)
+
+cl <- makeCluster(c("localhost", "localhost", "localhost", "localhost"), type = "SOCK")
+gen1 <- GenMatch(Tr=Tr, X=X, BalanceMatrix=X, cluster=cl, pop.size=10000)
 mgen1 <- Match(Tr=Tr, X=X, Weight.matrix=gen1)
 MatchBalance(fm_balance, data=d_pci_match, match.out=mgen1, nboots=1000)
 

### 2014-11-20 writeups/multilevel.tex

@@
 
+\section{Multilevel model}
+
+\begin{align}
+&\text{goldstein}_i &&\sim N(\alpha^{countryyear}_{j[i]}, \sigma^2_{goldstein}) \\
+&\alpha_j^{countryyear} &&\sim N(\beta_{k[j]}^{country} + \gamma \cdot \text{liec}_j + \Gamma X_j, \sigma_{\alpha}^2) \\
+&\beta_k^{country} &&\sim N(\delta_{ethnic} \cdot \text{ethnic}_k, \sigma_\beta^2) 
+\end{align}
+
 \section{Multilevel model with instrumental variable}

### 2014-11-21 R/0_clean_countrylevel.R
start writing

@@ -23,6 +23,7 @@ d_dpi_raw <- DpiGet(vars=c("liec"))
 d_dpi <- d_dpi_raw  %>%
   filter(!(iso2c=="KH" & liec==3)) %>% # For some reasons Cambodia has duplicates liec = 3 the whole time series...
   mutate(liec = ifelse(liec==-999.0, NA, liec)) %>%
+  mutate(liec_cat = ifelse(liec <= 5, 0, ifelse(liec == 6, 1, ifelse(liec == 7, 2, NA)))) %>%
   mutate(liec5 = ifelse(liec >= 5, 1, 0)) %>%
   mutate(liec6 = ifelse(liec >= 6, 1, 0)) %>%
   mutate(liec7 = ifelse(liec >= 7, 1, 0)) %>%

### 2014-11-21 R/inherited_parties.R

@@ -1,0 +1,15 @@
+# ---- Set up workspace ----
+rm(list=ls())
+# Load external functions
+source("./R/functions.R")
+# Load packages
+packs <- c("plyr", "dplyr")
+f_install_and_load(packs)
+
+# ---- Load data ----
+
+d_inherited <- read.csv("./data//private/Pol_Inst_Dictatorship_Data.csv")
+tmp <- d_inherited %>%  
+  select(Country.name, Year, Inherited.parties) %>%
+  group_by(Country.name) %>%
+  summarize(inherited.distinct = n_distinct(Inherited.parties))

### 2014-11-21 R/load_macro_data.R

@@ -8,11 +8,12 @@ d_dpi_raw <- DpiGet(vars=c("liec"))
 d_dpi <- d_dpi_raw  %>%
   filter(!(iso2c=="KH" & liec==3)) %>% # For some reasons Cambodia has duplicates liec = 3 the whole time series...
   mutate(liec = ifelse(liec==-999.0, NA, liec)) %>%
+  mutate(liec_cat = ifelse(liec <= 5, 0, ifelse(liec == 6, 1, ifelse(liec == 7, 2, NA)))) %>%
   mutate(liec5 = ifelse(liec >= 5, 1, 0)) %>%
   mutate(liec6 = ifelse(liec >= 6, 1, 0)) %>%
   mutate(liec7 = ifelse(liec >= 7, 1, 0)) %>%
   mutate(iso3c = countrycode(iso2c, origin="iso2c", destination="iso3c", warn=T)) %>%
-  select(iso3c, year, liec, liec5, liec6, liec7) %>%
+  select(iso3c, year, liec, liec_cat, liec5, liec6, liec7) %>%
   filter(year >= c_startyear)
 d_dpi <- unique(d_dpi)
 

### 2014-11-21 R/multilevel.R

@@ -19,8 +19,10 @@ d_eventlevel <- na.omit(d_eventlevel)
 # ---- Set up index link ----
 d_countryyear <- unique(select(d_eventlevel,
                                countryyear, country, resource.pc, milexp.pc,
-                               liec, liec5, liec6, liec7,
-                               gwf_military, gwf_party, gwf_personal, gwf_duration))
+                               liec, liec_cat, liec5, liec6, liec7,
+                               lgdp, lgdppc,
+                               gwf_military, gwf_party, gwf_personal, gwf_monarchy,
+                               gwf_duration))
 d_country <- unique(select(d_eventlevel, 
                            country, ethnic.polarization, region))
 d_event <- unique(select(d_eventlevel,
@@ -41,28 +43,30 @@ for (k in (1:K)) {
 
 # ---- Set up data ----
 goldstein <- d_event$goldstein
+Xdissident_sector <- model.matrix(~ dissident_sector_name - 1, data=d_event)[, -1]
+dimXdissident_sector <- dim(Xdissident_sector)
+
 liec <- d_countryyear$liec5
 Xa <- with(d_countryyear, 
-           cbind.data.frame(milexp.pc, resource.pc, gwf_duration, 
+           cbind.data.frame(lgdppc, lgdp, resource.pc, milexp.pc, gwf_duration,
                             gwf_military, gwf_personal, gwf_party))
 dimXa <- dim(Xa)
 
-Xgoldstein <- model.matrix(~ dissident_sector_name - 1, data=d_event)[, -1]
-dimXgoldstein <- dim(Xgoldstein)
-
 ethnic <- d_country$ethnic.polarization
+Xregion <- model.matrix(~ region - 1, data=d_country)[, -1]
+dimXregion <- dim(Xregion)
 
 # Set up JAGS model
 # JAGS needs a list of names that contain the data
-reg.data = list("goldstein", "Xgoldstein", "dimXgoldstein",
+reg.data = list("goldstein", "dimXdissident_sector", "Xdissident_sector",
                 "liec", "Xa", "dimXa",
-                "ethnic",
+                "ethnic", "Xregion", "dimXregion",
                 "countryyear.idx", "country.idx", "N", "J", "K")
 
[…]

### 2014-11-21 R/pci_experiment.R

@@ -68,8 +68,6 @@ f_create_balancetable(d_pci, c_balance_vars, m_bal_resrep)
 
 # ---- Analyze treatment effect ----
 
-summary(glm(communication ~ treat, data=d_pci, family="binomial"))
-
 summary(glm(communication ~ treat + a13_2 + a13_2:treat, data=d_pci, family="binomial"))
 summary(glm(communication ~ treat + a13_2 + a13_2:treat + a7_3, data=d_pci, family="binomial")) # Central SOE equitized
 summary(glm(communication ~ treat + a14_5 + a14_5:treat, data=d_pci, family="binomial"))
@@ -97,4 +95,5 @@ cl <- makeCluster(c("localhost", "localhost", "localhost", "localhost"), type = 
 gen1 <- GenMatch(Tr=Tr, X=X, BalanceMatrix=X, cluster=cl, pop.size=10000)
 mgen1 <- Match(Tr=Tr, X=X, Weight.matrix=gen1)
 MatchBalance(fm_balance, data=d_pci_match, match.out=mgen1, nboots=1000)
+stopCluster(cl)
 

### 2014-11-21 writeups/draft.tex
write up: finish matching section

\documentclass[12pt]{article}
% This first part of the file is called the PREAMBLE. It includes
% customizations and command definitions. The preamble is everything
% between \documentclass and \begin{document}.

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath}               % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments

\usepackage{rotating} % for sideway table
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

% various theorems, numbered by section

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}

\DeclareMathOperator{\id}{id}

\newcommand{\bd}[1]{\mathbf{#1}}  % for bolding symbols
\newcommand{\RR}{\mathbb{R}}      % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}}      % for Integers
\newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}

\begin{document}

\section{Introduction}

Once disregarded as mere ``window-dressing'', authoritarian institutions have garnered the attention of scholars as an important tool for power sharing, which, in turn, leads to various substantive effect, including regime survival, increased investment, better economic performance.

While our understanding of authoritarian institution has branched to numerous substantive topics, its causal root deserves more careful studies. Given its common definition as the ``rule of the game'', institutions are fundamentally a set of constraints of human interactions, and thus its effect must be most evident in the interaction between the strategic actors itself.  When scholars study the effect of institutions on various substantive areas, inevitably the causal chain must pass through the strategic actions of the actors, mostly through the logic of credible and regular spoil sharing (cite Przworski, Svolik). This causal step is theoretically crucial to all of our findings regarding authoritarian institutions – the goal of this article is, therefore, to empirically examine it.

Beyond its theoretical contribution, a study of violence in partially liberalized dictatorship has immense real-world importance. Indeed, violence during political liberalization is the greatest concern of many would-be democrats living under authoritarian regimes. For example, Chinese citizens show overwhelming enthusiasm when asked about democratic features such as popular accountability, separation of power, and political liberalism, yet remain consistently cautious of instability caused by transition (Chu 2008, 309). Understanding whether and why countries experience increased violence during liberalization is crucial for the prospect of democracy.

\section{Argument and Structure}

This article argues that if the authoritarian legislature is indeed a credible commitment and informational device, then we should see decreased level of violence between the regime and the dissdent in the presence of an authoritarian legislature. Indeed, taking a page from the rationalist war literature, I explains how political violence should only happen when the regime and the opposition misjudge one another's capacity and preference. Given transparent information and a commitment device, regardless of the capacity and preference of both sides, negotiating to reach an agreement is always preferable to violence due to the savings in the social cost of violence.

Armed with this theoretical argument, I empirically examine the level of violence in regime-dissident interaction using a novel event dataset across authoritarian regime post Cold War. I constructed the data by looking explicitly at countries that create their legislature during their authoritarian spells and matched these countries with those of the same conditions but did not create legislature. In addition to this large-n investigation, I zoom in at the causal mechanism with a survey experiment implemented in Vietnam, a hard case for the theory of legislature on regime-dissident interaction. These studies show that blah blah blah.

The article will proceed as follows:

\section{Theory: Authoritarian legislature and its effect on political violence}

\subsection{Legislature reducing violence}

To consider whether violent means is chosen to reach their goal, we need a theoretical framework to understand how the opposition and the regime engage in the bargaining game. A possible starting point is the bargaining models developed for democratic legislatures, where bargaining outcomes are driven by various institutional rules (positive and negative rule, sequencing of these powers, first-mover advantage, etc.) (Baron and Ferejohn 1989; Cox 2006). However, this type model is not suited to analyze the bargaining under an authoritarian regime, where the institutional rules themselves are under constant threat of being revised by the final arbiter that is violence. In other words, the end game of legislative bargaining now has an extra node that is whether either side will violently suppress the other’s demand. Given this context, the decision of the autocrat and the opposition is better characterized as a bargaining game in anarchy, very much like the bargaining between two sovereign states with the option of going to war (Fearon 1995).

To formally model the interaction, let the negotiation between the opposition and the regime be about the share $x$, $(0 < x < 1)$ of a good (normalized as 1) given to the opposition. (For concreteness we can think of this as the share of the economy’s rent or capital stock). Both sides have the option 1) to bargain and decide on x, or 2) to engage in violent protest / repression. Violence is costly compared to peaceful negotiation---we call this difference in relative cost $c_A$ and $c_O$ for the autocrat and the opposition, respectively. If violence happens, whichever side emerges victorious decides the share x to his heart’s desire---i.e. the winning autocrat would give 0 to the opposition and the winning opposition would give 1 to itself.

Given the uncertain nature of collective action battles, the utility of engaging in violence for the two sides is best formulated as an expected utility that depends on the probability of the opposition winning (call this probability $p$). Thus, the expected utility of the opposition is $p – c_O$, while the expected utility of the ruling regime is $1 - p - c_A$. These two expected utilities sum to less than one, which raises the puzzle why the two sides fail to engage in ex-ante bargaining that splits the difference, giving both sides a higher payoff than the expected utility of violence. Indeed, any amount of x between $(p - c_O, p + c_A)$, i.e. the bargaining range, is more desirable than violence to both sides.

Yet war happens between states and so does violence under authoritarian regimes. The international relations literature suggests three factors that may lead to violence, all of which having a legislature can help alleviate.

\begin{enumerate}
\item Information asymmetry regarding $p$

Due to the incentive to bluff, both sides only have incomplete information about the capability of the other. This leads to differing estimate of $p$, leading to non-overlapping preferences. This information asymmetry can be alleviated by having an elected legislature that helps the autocrat identify the collective action capability of the opposition. During regular legislative sessions, the regime can observe the position of opposition legislators to gauge their unity strength. Furthermore, during elections, both sides’ mobilization effort provides information to the other about its collective action capability without actually resorting to violence. The real, competitive stake of these elections also means that both sides are exerting its best effort, reducing the risk of bluffing and deception. Therefore, the autocrat can trust the information it receives about the opposition’s capability $(p)$, and consequently has a better idea about the political constraint that it faces.

\item The bargaining range $(p - c_O, p + c_A)$ depends on the value of $c_O and c_A$

Having an elected legislature can also increase $c_A$ and $c_O$, i.e. the cost of violence compared to peaceful negotiation. First, elections provide the opposition with a platform to influence policy making without resorting to violence (Rigger 1999, 14). Despite inevitable electoral manipulations, voters still know who the candidates are and can vote in support of their message. While these votes will not dethrone the regime, they serve as an informal referendum that alerts the regime about the popularity of its policies. In this way, the opposition can influence the agenda without winning the election itself. Indeed, if participation in the electoral game proves to be an attractive option to the opposition, radicalizing becomes relatively more costly as a means of gaining influence.

Second, in Dahlian terms, elections also tempt the ruling regime to stay within the institutionalized game by raising the cost of repression (Dahl 1971, 15). Indeed, elections “open up avenues of collective protest” by creating convergent social expectations that are both large in scope (affecting all citizens) and concentrated in time frame (Schedler 2009). Furthermore, by participating in elections, the opposition builds up its organizational strength, which can be used to mobilizing votes as well as organizing protest (Thompson and Kuntz 2004).

In addition, upholding elections and institutional bargaining is an attractive option for regimes to build their legitimacy and assuage grievances about past infractions (Lindberg 2009, 339). By adapting its policies based on election results, the regime can also bring its position closer to the popular will in incremental steps, each with acceptable cost. Indeed, it is not contradictory to say that an authoritarian regime may protect voters’ rights or respond to their demands as a strategy for the regime to stay in power, because there are often hard-liners and reformists within the regime. If the reformists’ strategy of electoral engagement proves to be a successful alternative to maintain power, more members of the regime will be tempted to become liberal-minded.

\item Unit indivisibility: the contested good may not be divided continuously

A final possibility that leads to violence is that the opposition and the ruling regime may be fighting over issues that cannot be continuously divided. For example, were the contested issue about whether religious law should be adopted, it may not be possible to split the issue space to arrive at a compromise within the (p - cO, p + cA) range. An elected legislature again ameliorates this problem. By providing an arena in which both sides can engage in multiple negotiations along many policy issues, it provides more opportunities for side payments. In contrast, were the opposition shut out of the policy making entirely, the only way they could gain influence is to arouse the populace to violent protest. The best way to do so is not via a nuanced discussion of multiple policy points but an intense focus on a highly contentious issue, further exacerbating the problem of unit indivisibility. Therefore, we should expect elected legislature to provide better opportunities for negotiation.

In sum, the overarching of over these causal mechanisms is that the elected legislature provides an arena for the ruling and the opposition to interact, gain information, and adjust strategies. In game theoretic sense, by lengthening the horizon and improve the regularity of stakes, repeated interaction encourage players to think about the future and deter the temptation to radicalize. Overall, these effects encourage incremental changes over radical tactic and favor cooperation over defection (Axelrod 1984). This leads to our hypothesis that:

H1: Authoritarian regimes that create a legislature will experience less violence in its interaction with the dissidents.
\end{enumerate}

\subsection{Legislature increasing violence}
Throughout the previous model, it is implied that the actors’ utility functions remain static with the only parameters being the cost of violence and the share of the issue space. Yet this assumption may miss the dynamism of the opposition’s democratic expectation, which becomes increasingly demanding as the regime starts liberalizing.

Speaking about this issue, Ted Gurr hypothesizes, “The potential for collective violence varies strongly with the intensity and the scope of relative deprivation among members of a collectivity.” Relative deprivation, in turn, is defined as the perceived discrepancy between value expectation (what people believe they are entitled to) and value capability (what the people believe they are able to attain) (1970, 24). Seen under this light, repeated elections may increase the potential for political violence by raising the democratic expectation, which can lead to violent protest if unfulfilled. The effect of elections is especially potent because it affects all citizens, thus raising not only the intensity but also the scope of relative deprivation.

Indeed, unfulfilled political expectation is a common case of relative deprivation causing violence. Historical examples are numerous, spanning various time periods as well as scopes of conflict: from the Puritan Revolution of 1640-60, which was sparked by attempts of the Stuart kings to reinstate royal absolutism, to the protest in twentieth-century colonies, which often followed the imposition of restrictions after a period of political liberalization (1970, 115). This pattern makes sense because, when people have tasted freedom, not only do they want more rights but they also consider rights more important. In other words, the opposition may not simply optimize its share of the issue space but also develops a minimum level of acceptable concession. If opposition’s expectation rises too quickly, the ruling regime may not have enough time to appropriate adjust their position especially if the hard-liners are also trying to retrench given signs of a political spiral. For this reason, it is plausible that electoral authoritarianism leads to more violent interaction between the ruling regime and the opposition.

\section{Empirics}

\subsection{Introducing the database}

Using a dataset of machine coded news reports around the world from 1991-2001, I am able to look at individual events that happened between the regime and the dissident, enabling an analysis at a highly granular level. These event data come from ICEWS (Integrated Crisis Early Warning System), a project funded by DARPA (Defense Advanced Research Projects Agency) to aid the US policy makers in predicting and responding to crises around the world . These news articles are harvested from “over 75 international sources (AP, UPI, and BBC Monitor) as well as regional sources (India Today, Jakarta Post, Pakistan Newswire, and Saigon Times),” ensuring comprehensive coverage  (cite O'Brien 2010 (94), 2013). These text data are then processed with Schrodt's TABARI event data coding system to determine the nature and the intensity of the reported political activity. In addition, the event is matched with a dictionary of actors (with over 8,000 entries) that further divides into five broad categories: religious, governmental, dissidents, business, and other. In sum, from this database I am able to extract any interaction between the government and the dissident, where and when it happens, and its level of violence (measured by the Goldstein score\footnote{The Goldstein score is a measure of intensity of conflict or cooperation, developed by Joshua S. Goldstein, "A Conflict-Cooperation Scale for WEIS Events Data," Journal of Conflict Resolution, 36, 2 (June 1992). The score has values from -10 (Military attack; clash; assault), 0 (Explain or state policy; state future position) to 8.3(Extend military assistance)} See Goldstein 375 for how the event types are coded into this scale).

\subsection{Empirical strategy}

First, my empirical strategy improves over the extant literature with a careful choice of country-years to study. Scholars in the authoritarian legislature have customarily count all authoritarian country-years with an existing legislature in the sample. However, this risks including dictatorships that passively inherited the legislature from the previous regime, who would rather abolish the institution if not for the fear of backlash. On the spreadsheet, such cases would look identical to an autocrat opening up to co-opt the opposition, yet the logic is entirely different. To use a cautionary example, in Preworski and Gandhi (1283), the legally enforced two-party legislature under the Brazilian junta government is not a reformist institution created by the autocrat to facilitate power sharing but a gutted down legislature when the election result did not go the regime's way. To guard against this possibility, I only look at authoritarian regimes that created  legislature during its rule as the ``treatment'' group. (From now on, I will use ``treatment'' as a shorthand for the creation of the legislature).

Second, it is important to recognize that an authoritarian regime without a legislature is not the correct counter factual, and thus make a very poor control group. Indeed, a regime may not create a co-opting legislature because there is never a sufficient threat of violence from the opposition. Therefore, even though we may see that regimes without legislature are very peaceful, this does not mean that a legislature has no effect on regime-dissident interaction. Conversely, a regime under rising violent threat may institute a legislature that successfully puts a lid on the growing discontent. However, since the level of violence is now constant, it will look as though the legislature had no effect.

To setup the correct counter factual, I use matching to create a sample of comparable cases. The crux of the strategy is to find two country years similar along all covariates in year $t$ (including $\text{violence}_t$), but one has a legislature in the next year while the other does not. Then, the difference in violence between these two cases in the ensuing period is attributable to the legislature.

This strategy is implemented as follows. First, to construct the treated population, I look at all country years in which an authoritarian legislature is created and build a four-year panel around it, including the one year before the treatment, and the three years after. Second, to construct the control population, I build similar four-year panels from all the other authoritarian country years without a legislature. Finally, for each panel in my treated population, I find its closest match from the control population based on their first year (which is the pre-treatment year for the treated countries). I match on level of violence and other covariates as reported in \autoref{tab:matching_balance_largen}, significantly improving the balance across the board. The matched pairs of panel are reported in \autoref{tab:matched_pairs}. Given that factors that affect violence may have various non-linear effect, matching alleviates the serious concern about functional misspecification.

In general, matching alone does not recover the correct causal inference when there is selection based on unobservables. However, in this case, it addresses the most important concerns. First, as discussed above, matching on the level of violence in the pre-treatment year creates a sample of regimes with similar violence trajectory, and thus sets up the correct counter factual. Second, even though there is a risk of regimes creating legislature in anticipation of violence, this requires a significant ability from the regime to monitor the capability and the preference of the opposition. In the absence of a legislature, this information is likely to come from the security apparatus---therefore, the military expenditure (as a percentage of GDP) is matched on as a proxy control for the regime's capacity to anticipate violence.

\begin{sidewaystable}[ht]
\centering
\begin{tabular}{lrrlrrrl}
  \hline
 & \multicolumn{2}{c}{Pre-Match} &   \multicolumn{2}{c}{Post-Match} \\
Covariate & Treated mean & Control mean & p-value & Treated mean & Control mean & p-value &  \\ 
  \hline
Ethnic Fractionalization \_ & 0.61 & 0.59 & 0.59 & 0.61 & 0.60 & 0.81 &  \\ 
Violence (Goldstein score) & -4.50 & -4.05 & 0.51 & -4.50 & -4.49 & 0.94 &  \\ 
$\text{Violence}^2$ & 29.84 & 23.22 & 0.34 & 29.84 & 29.03 & 0.65 &  \\ 
Regime duration (years) & 12.08 & 34.30 & 0.00*** & 12.08 & 12.71 & 0.71 &  \\ 
$\text{Regime duration}^2$ & 278.00 & 2783.57 & 0.00** & 278.00 & 287.38 & 0.89 &  \\ 
Military & 0.08 & 0.06 & 0.67 & 0.08 & 0.12 & 0.57 &  \\ 
Monarchy & 0.04 & 0.25 & 0.00*** & 0.04 & 0.04 & 1.00 &  \\ 
Party & 0.29 & 0.48 & 0.07* & 0.29 & 0.29 & 1.00 &  \\ 
log(gdp) & 22.65 & 23.95 & 0.00*** & 22.65 & 22.78 & 0.67 &  \\ 
log(gdp per capita) & 7.63 & 8.58 & 0.00*** & 7.63 & 7.65 & 0.95 &  \\ 
Military expenditure (\% of GDP) & 2.44 & 4.34 & 0.00*** & 2.44 & 2.40 & 0.89 &  \\
Land (1000 $\text{km}^2$)& 760.22 & 1674.68 & 0.00*** & 760.21 & 783.37 & 0.80 &  \\ 
Population (million) & 22.62 & 140.73 & 0.00*** & 22.62 & 21.74 & 0.90 &  \\
Natural Resource Export (\% of GDP) & 14.79 & 22.64 & 0.03** & 14.79 & 14.16 & 0.72 &  \\ 
Resource $\times$ Ethnic & 8.61 & 14.43 & 0.01** & 8.61 & 8.33 & 0.82 &  \\ 
   \hline
\end{tabular}
\caption{Pre and Post-Matching Balance}
\label{tab:matching_balance_largen}
\end{sidewaystable}

\begin{table}[ht]
\centering
\begin{tabular}{lrlr}
  \hline
 \multicolumn{2}{c}{Treatment} &   \multicolumn{2}{c}{Control} \\
Country & Year & Country & Year \\ 
  \hline
Algeria & 1996 & Sudan & 1992 \\ 
  Angola & 1992 & Angola & 2000 \\ 
  Azerbaijan & 1992 & Uganda & 1991 \\ 
  Belarus & 2004 & Belarus & 2000 \\ 
  Cambodia & 1993 & Laos & 1999 \\ 
  Central African Republic & 2005 & Uganda & 2001 \\ 
  Chad & 1997 & Central African Republic & 1992 \\ 
  Congo, Republic & 2002 & Nigeria & 1994 \\ 
  Congo, Dem Rep & 2006 & Congo, Dem Rep & 1996 \\ 
  Ethiopia & 1995 & Ethiopia & 1993 \\ 
  Gambia & 1996 & Belarus & 2001 \\ 
  Ghana & 1995 & Belarus & 2000 \\ 
  Jordan & 1993 & Swaziland & 2007 \\ 
  Kazakhstan & 1995 & Sudan & 1994 \\ 
  Kenya & 1992 & Laos & 1997 \\ 
  Kyrgyzstan & 1995 & Belarus & 1998 \\ 
  Pakistan & 2002 & Algeria & 1993 \\ 
  Rwanda & 2003 & Rwanda & 1999 \\ 
  Sudan & 2000 & Sudan & 2006 \\ 
  Tajikistan & 1995 & Belarus & 1999 \\ 
  Tanzania & 1995 & Sierra Leone & 1992 \\ 
  Togo & 1994 & Togo & 1991 \\ 
  Uganda & 2006 & Uganda & 1998 \\ 
  Uzbekistan & 1999 & Ethiopia & 1993 \\ 
   \hline
\end{tabular}
\caption{The matched sample of country years}
\label{tab:matched_pairs}
\end{table}

\end{document}

### 2014-11-21 R/matching_genetic.R

@@ -8,7 +8,7 @@ rm(list=ls())
 # Load external functions
 source("./R/functions.R")
 # Load packages
-packs <- c("gridExtra", "Matching", "plyr", "dplyr", "ggplot2")
+packs <- c("gridExtra", "snow", "Matching", "plyr", "dplyr", "ggplot2")
 f_install_and_load(packs) ; rm(packs)
 
 # ---- Some constant ----
@@ -63,12 +63,14 @@ BalanceMatrix <- X %>%
          resource.ethnic = resource.pc.0 * ethnic.polarization.0)
 
 # ---- Do the matching ----
+cl <- makeCluster(c("localhost", "localhost", "localhost", "localhost"), type = "SOCK")
 gen1 <- GenMatch(Tr=Tr, X=X, BalanceMatrix=BalanceMatrix, pop.size=10000)
 mgen1 <- Match(Tr=Tr, X=X, Weight.matrix=gen1)
 
 balance_vars <- paste(c(names(BalanceMatrix)[1], paste("+", names(BalanceMatrix)[-1])), collapse=" ")
 fm_gen1 <- as.formula(paste(paste0(c_treatmentvar, ".", c_pretreat_length), "~", balance_vars))
 MatchBalance(fm_gen1, data=cbind.data.frame(liec6.1=Tr, BalanceMatrix), match.out=mgen1, nboots=1000)
+stopCluster(cl)
 
 par(mfrow=c(1, 2))
 with(d_to_be_matched, 

### 2014-11-21 writeups/appendix_modeldiagnostic.tex
finish model description

\section{Appendix A: Bayesian hierarchical model diagnostic}
\label{sec:modeldiagnostic}

### 2014-11-21 writeups/draft.tex
finish model description

@@
 
+\usepackage{array,tabularx}
+
+\newenvironment{conditions*}
+  {\par\vspace{\abovedisplayskip}\noindent
+   \tabularx{\columnwidth}{>{$}l<{$} @{${}={}$} >{\raggedright\arraybackslash}X}}
+  {\endtabularx\par\vspace{\belowdisplayskip}}
+
+\title{Prelim paper}
+\author{Anh Le}
+
 \begin{document}
+\maketitle
 
-\section{Introduction}
+\input{introduction}
+\input{theory}
+\input{empirics_largeN}
+\input{multilevel}
 
-Once disregarded as mere ``window-dressing'', authoritarian institutions have garnered the attention of scholars as an important tool for power sharing, which, in turn, leads to various substantive effect, including regime survival, increased investment, better economic performance.
-
-While our understanding of authoritarian institution has branched to numerous substantive topics, its causal root deserves more careful studies.
-Given its common definition as the ``rule of the game'', institutions are fundamentally a set of constraints of human interactions, and thus its effect must be most evident in the interaction between the strategic actors itself.
-When scholars study the effect of institutions on various substantive areas, inevitably the causal chain must pass through the strategic actions of the actors, mostly through the logic of credible and regular spoil sharing (cite Przworski, Svolik).
-This causal step is theoretically crucial to all of our findings regarding authoritarian institutions – the goal of this article is, therefore, to empirically examine it.
-
-Beyond its theoretical contribution, a study of violence in partially liberalized dictatorship has immense real-world importance.
-Indeed, violence during political liberalization is the greatest concern of many would-be democrats living under authoritarian regimes.
-For example, Chinese citizens show overwhelming enthusiasm when asked about democratic features such as popular accountability, separation of power, and political liberalism, yet remain consistently cautious of instability caused by transition (Chu 2008, 309).
-Understanding whether and why countries experience increased violence during liberalization is crucial for the prospect of democracy.
-
-\section{Argument and Structure}
-
-This article argues that if the authoritarian legislature is indeed a credible commitment and informational device, then we should see decreased level of violence between the regime and the dissdent in the presence of an authoritarian legislature.
-Indeed, taking a page from the rationalist war literature, I explains how political violence should only happen when the regime and the opposition misjudge one another's capacity and preference.
-Given transparent information and a commitment device, regardless of the capacity and preference of both sides, negotiating to reach an agreement is always preferable to violence due to the savings in the social cost of violence.
-
-Armed with this theoretical argument, I empirically examine the level of violence in regime-dissident interaction using a novel event dataset across authoritarian regime post Cold War.
-I constructed the data by looking explicitly at countries that create their legislature during their authoritarian spells and matched these countries with those of the same conditions but did not create legislature.
-In addition to this large-n investigation, I zoom in at the causal mechanism with a survey experiment implemented in Vietnam, a hard case for the theory of legislature on regime-dissident interaction.
-These studies show that blah blah blah.
-
-The article will proceed as follows:
-
-\section{Theory: Authoritarian legislature and its effect on political violence}
-
-\subsection{Legislature reducing violence}
-
-To consider whether violent means is chosen to reach their goal, we need a theoretical framework to understand how the opposition and the regime engage in the bargaining game.
-A possible starting point is the bargaining models developed for democratic legislatures, where bargaining outcomes are driven by various institutional rules (positive and negative rule, sequencing of these powers, first-mover advantage, etc.) (Baron and Ferejohn 1989; Cox 2006).
-However, this type model is not suited to analyze the bargaining under an authoritarian regime, where the institutional rules themselves are under constant threat of being revised by the final arbiter that is violence.
-In other words, the end game of legislative bargaining now has an extra node that is whether either side will violently suppress the other’s demand.
-Given this context, the decision of the autocrat and the opposition is better characterized as a bargaining game in anarchy, very much like the bargaining between two sovereign states with the option of going to war (Fearon 1995).
-
-To formally model the interaction, let the negotiation between the opposition and the regime be about the share $x$, $(0 < x < 1)$ of a good (normalized as 1) given to the opposition.
-(For concreteness we can think of this as the share of the economy’s rent or capital stock).
-Both sides have the option 1) to bargain and decide on x, or 2) to engage in violent protest / repression.
-Violence is costly compared to peaceful negotiation---we call this difference in relative cost $c_A$ and $c_O$ for the autocrat and the opposition, respectively.
-If violence happens, whichever side emerges victorious decides the share x to his heart’s desire---i.e.
-the winning autocrat would give 0 to the opposition and the winning opposition would give 1 to itself.
-
-Given the uncertain nature of collective action battles, the utility of engaging in violence for the two sides is best formulated as an expected utility that depends on the probability of the opposition winning (call this probability $p$).
-Thus, the expected utility of the opposition is $p – c_O$, while the expected utility of the ruling regime is $1 - p - c_A$.
-These two expected utilities sum to less than one, which raises the puzzle why the two sides fail to engage in ex-ante bargaining that splits the difference, giving both sides a higher payoff than the expected utility of violence.
-Indeed, any amount of x between $(p - c_O, p + c_A)$, i.e.
-the bargaining range, is more desirable than violence to both sides.
-
-Yet war happens between states and so does violence under authoritarian regimes.
-The international relations literature suggests three factors that may lead to violence, all of which having a legislature can help alleviate.
-
-\begin{enumerate}
-\item Information asymmetry regarding $p$
-
-Due to the incentive to bluff, both sides only have incomplete information about the capability of the other.
-This leads to differing estimate of $p$, leading to non-overlapping preferences.
-This information asymmetry can be alleviated by having an elected legislature that helps the autocrat identify the collective action capability of the opposition.
-During regular legislative sessions, the regime can observe the position of opposition legislators to gauge their unity strength.
-Furthermore, during elections, both sides’ mobilization effort provides information to the other about its collective action capability without actually resorting to violence.
-The real, competitive stake of these elections also means that both sides are exerting its best effort, reducing the risk of bluffing and deception.
-Therefore, the autocrat can trust the information it receives about the opposition’s capability $(p)$, and consequently has a better idea about the political constraint that it faces.
-
-\item The bargaining range $(p - c_O, p + c_A)$ depends on the value of $c_O and c_A$
-
-Having an elected legislature can also increase $c_A$ and $c_O$, i.e.
-the cost of violence compared to peaceful negotiation.
-First, elections provide the opposition with a platform to influence policy making without resorting to violence (Rigger 1999, 14).
-Despite inevitable electoral manipulations, voters still know who the candidates are and can vote in support of their message.
-While these votes will not dethrone the regime, they serve as an informal referendum that alerts the regime about the popularity of its policies.
-In this way, the opposition can influence the agenda without winning the election itself.
-Indeed, if participation in the electoral game proves to be an attractive option to the opposition, radicalizing becomes relatively more costly as a means of gaining influence.
-
-Second, in Dahlian terms, elections also tempt the ruling regime to stay within the institutionalized game by raising the cost of repression (Dahl 1971, 15).
-Indeed, elections “open up avenues of collective protest” by creating convergent social expectations that are both large in scope (affecting all citizens) and concentrated in time frame (Schedler 2009).
-Furthermore, by participating in elections, the opposition builds up its organizational strength, which can be used to mobilizing votes as well as organizing protest (Thompson and Kuntz 2004).
-
-In addition, upholding elections and institutional bargaining is an attractive option for regimes to build their legitimacy and assuage grievances about past infractions (Lindberg 2009, 339).
-By adapting its policies based on election results, the regime can also bring its position closer to the popular will in incremental steps, each with acceptable cost.
-Indeed, it is not contradictory to say that an authoritarian regime may protect voters’ rights or respond to their demands as a strategy for the regime to stay in power, because there are often hard-liners and reformists within the regime.
-If the reformists’ strategy of electoral engagement proves to be a successful alternative to maintain power, more members of the regime will be tempted to become liberal-minded.
-
-\item Unit indivisibility: the contested good may not be divided continuously
-
-A final possibility that leads to violence is that the opposition and the ruling regime may be fighting over issues that cannot be continuously divided.
-For example, were the contested issue about whether religious law should be adopted, it may not be possible to split the issue space to arrive at a compromise within the (p - cO, p + cA) range.
-An elected legislature again ameliorates this problem.
-By providing an arena in which both sides can engage in multiple negotiations along many policy issues, it provides more opportunities for side payments.
-In contrast, were the opposition shut out of the policy making entirely, the only way they could gain influence is to arouse the populace to violent protest.
-The best way to do so is not via a nuanced discussion of multiple policy points but an intense focus on a highly contentious issue, further exacerbating the problem of unit indivisibility.
-Therefore, we should expect elected legislature to provide better opportunities for negotiation.
-
-In sum, the overarching of over these causal mechanisms is that the elected legislature provides an arena for the ruling and the opposition to interact, gain information, and adjust strategies.
-In game theoretic sense, by lengthening the horizon and improve the regularity of stakes, repeated interaction encourage players to think about the future and deter the temptation to radicalize.
-Overall, these effects encourage incremental changes over radical tactic and favor cooperation over defection (Axelrod 1984).
-This leads to our hypothesis that:
-
-H1: Authoritarian regimes that create a legislature will experience less violence in its interaction with the dissidents.
-\end{enumerate}
-
-\subsection{Legislature increasing violence}
-Throughout the previous model, it is implied that the actors’ utility functions remain static with the only parameters being the cost of violence and the share of the issue space.
-Yet this assumption may miss the dynamism of the opposition’s democratic expectation, which becomes increasingly demanding as the regime starts liberalizing.
-
-Speaking about this issue, Ted Gurr hypothesizes, “The potential for collective violence varies strongly with the intensity and the scope of relative deprivation among members of a collectivity.” Relative deprivation, in turn, is defined as the perceived discrepancy between value expectation (what people believe they are entitled to) and value capability (what the people believe they are able to attain) (1970, 24).
-Seen under this light, repeated elections may increase the potential for political violence by raising the democratic expectation, which can lead to violent protest if unfulfilled.
-The effect of elections is especially potent because it affects all citizens, thus raising not only the intensity but also the scope of relative deprivation.
-
-Indeed, unfulfilled political expectation is a common case of relative deprivation causing violence.
-Historical examples are numerous, spanning various time periods as well as scopes of conflict: from the Puritan Revolution of 1640-60, which was sparked by attempts of the Stuart kings to reinstate royal absolutism, to the protest in twentieth-century colonies, which often followed the imposition of restrictions after a period of political liberalization (1970, 115).
-This pattern makes sense because, when people have tasted freedom, not only do they want more rights but they also consider rights more important.
-In other words, the opposition may not simply optimize its share of the issue space but also develops a minimum level of acceptable concession.
-If opposition’s expectation rises too quickly, the ruling regime may not have enough time to appropriate adjust their position especially if the hard-liners are also trying to retrench given signs of a political spiral.
-For this reason, it is plausible that electoral authoritarianism leads to more violent interaction between the ruling regime and the opposition.
-
-\section{Empirics}
-
-\subsection{Introducing the database}
-
-Using a dataset of machine coded news reports around the world from 1991-2001, I am able to look at individual events that happened between the regime and the dissident, enabling an analysis at a highly granular level.
-These event data come from ICEWS (Integrated Crisis Early Warning System), a project funded by DARPA (Defense Advanced Research Projects Agency) to aid the US policy makers in predicting and responding to crises around the world .
-These news articles are harvested from “over 75 international sources (AP, UPI, and BBC Monitor) as well as regional sources (India Today, Jakarta Post, Pakistan Newswire, and Saigon Times),” ensuring comprehensive coverage  (cite O'Brien 2010 (94), 2013).
-These text data are then processed with Schrodt's TABARI event data coding system to determine the nature and the intensity of the reported political activity.
-In addition, the event is matched with a dictionary of actors (with over 8,000 entries) that further divides into five broad categories: religious, governmental, dissidents, business, and other.
-In sum, from this database I am able to extract any interaction between the government and the dissident, where and when it happens, and its level of violence (measured by the Goldstein score\footnote{The Goldstein score is a measure of intensity of conflict or cooperation, developed by Joshua S.
-Goldstein, "A Conflict-Cooperation Scale for WEIS Events Data," Journal of Conflict Resolution, 36, 2 (June 1992).
-The score has values from -10 (Military attack; clash; assault), 0 (Explain or state policy; state future position) to 8.3(Extend military assistance)} See Goldstein 375 for how the event types are coded into this scale).
-
-\subsection{Empirical strategy}
-
-First, my empirical strategy improves over the extant literature with a careful choice of country-years to study.
-Scholars in the authoritarian legislature have customarily count all authoritarian country-years with an existing legislature in the sample.
-However, this risks including dictatorships that passively inherited the legislature from the previous regime, who would rather abolish the institution if not for the fear of backlash.
-On the spreadsheet, such cases would look identical to an autocrat opening up to co-opt the opposition, yet the logic is entirely different.
-To use a cautionary example, in Preworski and Gandhi (1283), the legally enforced two-party legislature under the Brazilian junta government is not a reformist institution created by the autocrat to facilitate power sharing but a gutted down legislature when the election result did not go the regime's way.
-To guard against this possibility, I only look at authoritarian regimes that created  legislature during its rule as the ``treatment'' group.
-(From now on, I will use ``treatment'' as a shorthand for the creation of the legislature).
-
-Second, it is important to recognize that an authoritarian regime without a legislature is not the correct counter factual, and thus make a very poor control group.
-Indeed, a regime may not create a co-opting legislature because there is never a sufficient threat of violence from the opposition.
-Therefore, even though we may see that regimes without legislature are very peaceful, this does not mean that a legislature has no effect on regime-dissident interaction.
-Conversely, a regime under rising violent threat may institute a legislature that successfully puts a lid on the growing discontent.
-However, since the level of violence is now constant, it will look as though the legislature had no effect.
-
-To setup the correct counter factual, I use matching to create a sample of comparable cases.
-The crux of the strategy is to find two country years similar along all covariates in year $t$ (including $\text{violence}_t$), but one has a legislature in the next year while the other does not.
-Then, the difference in violence between these two cases in the ensuing period is attributable to the legislature.
-
-This strategy is implemented as follows.
-First, to construct the treated population, I look at all country years in which an authoritarian legislature is created and build a four-year panel around it, including the one year before the treatment, and the three years after.
-Second, to construct the control population, I build similar four-year panels from all the other authoritarian country years without a legislature.
-Finally, for each panel in my treated population, I find its closest match from the control population based on their first year (which is the pre-treatment year for the treated countries).
-I match on level of violence and other covariates as reported in \autoref{tab:matching_balance_largen}, significantly improving the balance across the board.
-The matched pairs of panel are reported in \autoref{tab:matched_pairs}.
-Given that factors that affect violence may have various non-linear effect, matching alleviates the serious concern about functional misspecification.
-
-In general, matching alone does not recover the correct causal inference when there is selection based on unobservables.
-However, in this case, it addresses the most important concerns.
-First, as discussed above, matching on the level of violence in the pre-treatment year creates a sample of regimes with similar violence trajectory, and thus sets up the correct counter factual.
-Second, even though there is a risk of regimes creating legislature in anticipation of violence, this requires a significant ability from the regime to monitor the capability and the preference of the opposition.
-In the absence of a legislature, this information is likely to come from the security apparatus---therefore, the military expenditure (as a percentage of GDP) is matched on as a proxy control for the regime's capacity to anticipate violence.
-
-\begin{sidewaystable}[ht]
-\centering
-\begin{tabular}{lrrlrrrl}
-  \hline
- & \multicolumn{2}{c}{Pre-Match} &   \multicolumn{2}{c}{Post-Match} \\
-Covariate & Treated mean & Control mean & p-value & Treated mean & Control mean & p-value &  \\ 
-  \hline
-Ethnic Fractionalization \_ & 0.61 & 0.59 & 0.59 & 0.61 & 0.60 & 0.81 &  \\ 
-Violence (Goldstein score) & -4.50 & -4.05 & 0.51 & -4.50 & -4.49 & 0.94 &  \\ 
-$\text{Violence}^2$ & 29.84 & 23.22 & 0.34 & 29.84 & 29.03 & 0.65 &  \\ 
-Regime duration (years) & 12.08 & 34.30 & 0.00*** & 12.08 & 12.71 & 0.71 &  \\ 
-$\text{Regime duration}^2$ & 278.00 & 2783.57 & 0.00** & 278.00 & 287.38 & 0.89 &  \\ 
-Military & 0.08 & 0.06 & 0.67 & 0.08 & 0.12 & 0.57 &  \\ 
-Monarchy & 0.04 & 0.25 & 0.00*** & 0.04 & 0.04 & 1.00 &  \\ 
-Party & 0.29 & 0.48 & 0.07* & 0.29 & 0.29 & 1.00 &  \\ 
-log(gdp) & 22.65 & 23.95 & 0.00*** & 22.65 & 22.78 & 0.67 &  \\ 
-log(gdp per capita) & 7.63 & 8.58 & 0.00*** & 7.63 & 7.65 & 0.95 &  \\ 
-Military expenditure (\% of GDP) & 2.44 & 4.34 & 0.00*** & 2.44 & 2.40 & 0.89 &  \\
-Land (1000 $\text{km}^2$)& 760.22 & 1674.68 & 0.00*** & 760.21 & 783.37 & 0.80 &  \\ 
-Population (million) & 22.62 & 140.73 & 0.00*** & 22.62 & 21.74 & 0.90 &  \\
-Natural Resource Export (\% of GDP) & 14.79 & 22.64 & 0.03** & 14.79 & 14.16 & 0.72 &  \\ 
-Resource $\times$ Ethnic & 8.61 & 14.43 & 0.01** & 8.61 & 8.33 & 0.82 &  \\ 
-   \hline
-\end{tabular}
-\caption{Pre and Post-Matching Balance}
-\label{tab:matching_balance_largen}
-\end{sidewaystable}
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{lrlr}
-  \hline
- \multicolumn{2}{c}{Treatment} &   \multicolumn{2}{c}{Control} \\
-Country & Year & Country & Year \\ 
-  \hline
-Algeria & 1996 & Sudan & 1992 \\ 
-  Angola & 1992 & Angola & 2000 \\ 
-  Azerbaijan & 1992 & Uganda & 1991 \\ 
-  Belarus & 2004 & Belarus & 2000 \\ 
-  Cambodia & 1993 & Laos & 1999 \\ 
-  Central African Republic & 2005 & Uganda & 2001 \\ 
-  Chad & 1997 & Central African Republic & 1992 \\ 
-  Congo, Republic & 2002 & Nigeria & 1994 \\ 
-  Congo, Dem Rep & 2006 & Congo, Dem Rep & 1996 \\ 
-  Ethiopia & 1995 & Ethiopia & 1993 \\ 
-  Gambia & 1996 & Belarus & 2001 \\ 
-  Ghana & 1995 & Belarus & 2000 \\ 
-  Jordan & 1993 & Swaziland & 2007 \\ 
-  Kazakhstan & 1995 & Sudan & 1994 \\ 
-  Kenya & 1992 & Laos & 1997 \\ 
-  Kyrgyzstan & 1995 & Belarus & 1998 \\ 
-  Pakistan & 2002 & Algeria & 1993 \\ 
-  Rwanda & 2003 & Rwanda & 1999 \\ 
-  Sudan & 2000 & Sudan & 2006 \\ 
-  Tajikistan & 1995 & Belarus & 1999 \\ 
-  Tanzania & 1995 & Sierra Leone & 1992 \\ 
-  Togo & 1994 & Togo & 1991 \\ 
-  Uganda & 2006 & Uganda & 1998 \\ 
-  Uzbekistan & 1999 & Ethiopia & 1993 \\ 
-   \hline
-\end{tabular}
-\caption{The matched sample of country years}
-\label{tab:matched_pairs}
-\end{table}
+\appendix
+\input{appendix_modeldiagnostic}
 

### 2014-11-21 writeups/empirics_largeN.tex
finish model description

\section{Empirics}

\subsection{Description of data}

\begin{itemize}

\item Dependent variable: \textit{legislature}, operationalized as $LIEC \geq 5$

As my theoretical argument emphasizes the role of the legislature as an informational and commitment device, I code a country-year as having a legislature if multiple parties are legal. Even if opposition parties do not win seat, the electoral process also conveys information about the organizational strength and the preference of both sides. This coding rule operationalizes as having LIEC (Legislative Index of Electoral Competitiveness) be 5 or higher in the DPI (Database of Political Institutions).\footnote{The values LIEC are as follows: 4---1 party, multiple candidates; 5---multiple parties are legal but only one party won seats; 6---multiple parties did win seats but the largest party received more than 75\% of the seats; 7---largest party got less than 75\% (DPI 14)}

\item Independent variable: \textit{violence} in regime-dissident interaction

Using a dataset of machine coded news reports around the world from 1991-2012, I am able to look at individual events that happened between the regime and the dissident, enabling an analysis at a highly granular level. These event data come from ICEWS (Integrated Crisis Early Warning System), a project funded by DARPA (Defense Advanced Research Projects Agency) to aid the US policy makers in predicting and responding to crises around the world . These news articles are harvested from ``over 75 international sources (AP, UPI, and BBC Monitor) as well as regional sources (India Today, Jakarta Post, Pakistan Newswire, and Saigon Times),'' ensuring comprehensive coverage  (cite O'Brien 2010 (94), 2013). While this dataset has been de-duplicated once so that an event covered by multiple news report only shows up once, I created my own filter to delete duplicates that share the same source actor, target actor, and happen at the same time and place.

These text data are then processed with Schrodt's TABARI event data coding system to determine the nature and the intensity of the reported political activity. In addition, the event is matched with a dictionary of actors (with over 8,000 entries) that further divides into five broad categories: religious, governmental, dissidents, business, and other. In sum, from this database I am able to extract any interaction between the government and the dissident, where and when it happens, and its level of violence (measured by the Goldstein score\footnote{The Goldstein score is a measure of intensity of conflict or cooperation, developed by Joshua S. Goldstein. The score has values from -10 (Military attack, clash, assault), 0 (Explain or state policy, state future position) to 8.3(Extend military assistance) See Goldstein 375 for how the event types are coded into this scale).}
\end{itemize}

\subsection{Empirical strategy}

First, my empirical strategy improves over the extant literature with a careful choice of country-years to study. Scholars in the authoritarian legislature have customarily count all authoritarian country-years with an existing legislature in the sample. However, this risks including dictatorships that passively inherited the legislature from the previous regime, who would rather abolish the institution if not for the fear of backlash. On the spreadsheet, such cases would look identical to an autocrat opening up to co-opt the opposition, yet the logic is entirely different. To use a cautionary example, in Preworski and Gandhi (1283), the legally enforced two-party legislature under the Brazilian junta government is not a reformist institution created by the autocrat to facilitate power sharing but a gutted down legislature when the election result did not go the regime's way. To guard against this possibility, I only look at authoritarian regimes that created  legislature during its rule as the ``treatment'' group. (From now on, I will use ``treatment'' as a shorthand for the creation of the legislature).

Second, it is important to recognize that an authoritarian regime without a legislature is not the correct counter factual, and thus make a very poor control group. Indeed, a regime may not create a co-opting legislature because there is never a sufficient threat of violence from the opposition. Therefore, even though we may see that regimes without legislature are very peaceful, this does not mean that a legislature has no effect on regime-dissident interaction. Conversely, a regime under rising violent threat may institute a legislature that successfully puts a lid on the growing discontent. However, since the level of violence is now constant, it will look as though the legislature had no effect.

To setup the correct counter factual, I use matching to create a sample of comparable cases. The crux of the strategy is to find two country years similar along all covariates in year $t$ (including $\text{violence}_t$), but one has a legislature in the next year while the other does not. Then, the difference in violence between these two cases in the ensuing period is attributable to the legislature.

This strategy is implemented as follows. First, to construct the treated population, I look at all country years in which an authoritarian legislature is created and build a four-year panel around it, including the one year before the treatment, and the three years after. Second, to construct the control population, I build similar four-year panels from all the other authoritarian country years without a legislature. Finally, for each panel in my treated population, I find its closest match from the control population based on their first year (which is the pre-treatment year for the treated countries). I match on level of violence and other covariates as reported in \autoref{tab:matching_balance_largen}, significantly improving the balance across the board. The matched pairs of panel are reported in \autoref{tab:matched_pairs}. Given that factors that affect violence may have various non-linear effect, matching alleviates the serious concern about functional misspecification.

In general, matching alone does not recover the correct causal inference when there is selection based on unobservables. However, in this case, it addresses the most important concerns. First, as discussed above, matching on the level of violence in the pre-treatment year creates a sample of regimes with similar violence trajectory, and thus sets up the correct counter factual. Second, even though there is a risk of regimes creating legislature in anticipation of violence, this requires a significant ability from the regime to monitor the capability and the preference of the opposition. In the absence of a legislature, this information is likely to come from the security apparatus---therefore, the military expenditure (as a percentage of GDP) is matched on as a proxy control for the regime's capacity to anticipate violence.

\begin{sidewaystable}[ht]
\centering
\begin{tabular}{lrrlrrrl}
  \hline
 & \multicolumn{2}{c}{Pre-Match} &   \multicolumn{2}{c}{Post-Match} \\
Covariate & Treated mean & Control mean & p-value & Treated mean & Control mean & p-value &  \\ 
  \hline
Ethnic Fractionalization \_ & 0.61 & 0.59 & 0.59 & 0.61 & 0.60 & 0.81 &  \\ 
Violence (Goldstein score) & -4.50 & -4.05 & 0.51 & -4.50 & -4.49 & 0.94 &  \\ 
$\text{Violence}^2$ & 29.84 & 23.22 & 0.34 & 29.84 & 29.03 & 0.65 &  \\ 
Regime duration (years) & 12.08 & 34.30 & 0.00*** & 12.08 & 12.71 & 0.71 &  \\ 
$\text{Regime duration}^2$ & 278.00 & 2783.57 & 0.00** & 278.00 & 287.38 & 0.89 &  \\ 
Military & 0.08 & 0.06 & 0.67 & 0.08 & 0.12 & 0.57 &  \\ 
Monarchy & 0.04 & 0.25 & 0.00*** & 0.04 & 0.04 & 1.00 &  \\ 
Party & 0.29 & 0.48 & 0.07* & 0.29 & 0.29 & 1.00 &  \\ 
log(gdp) & 22.65 & 23.95 & 0.00*** & 22.65 & 22.78 & 0.67 &  \\ 
log(gdp per capita) & 7.63 & 8.58 & 0.00*** & 7.63 & 7.65 & 0.95 &  \\ 
Military expenditure (\% of GDP) & 2.44 & 4.34 & 0.00*** & 2.44 & 2.40 & 0.89 &  \\
Land (1000 $\text{km}^2$)& 760.22 & 1674.68 & 0.00*** & 760.21 & 783.37 & 0.80 &  \\ 
Population (million) & 22.62 & 140.73 & 0.00*** & 22.62 & 21.74 & 0.90 &  \\
Natural Resource Export (\% of GDP) & 14.79 & 22.64 & 0.03** & 14.79 & 14.16 & 0.72 &  \\ 
Resource $\times$ Ethnic & 8.61 & 14.43 & 0.01** & 8.61 & 8.33 & 0.82 &  \\ 
   \hline
\end{tabular}
\caption{Pre and Post-Matching Balance}
\label{tab:matching_balance_largen}
\end{sidewaystable}

\begin{table}[ht]
\centering
\begin{tabular}{lrlr}
  \hline
 \multicolumn{2}{c}{Treatment} &   \multicolumn{2}{c}{Control} \\
Country & Year & Country & Year \\ 
  \hline
Algeria & 1996 & Sudan & 1992 \\ 
  Angola & 1992 & Angola & 2000 \\ 
  Azerbaijan & 1992 & Uganda & 1991 \\ 
  Belarus & 2004 & Belarus & 2000 \\ 
  Cambodia & 1993 & Laos & 1999 \\ 
  Central African Republic & 2005 & Uganda & 2001 \\ 
  Chad & 1997 & Central African Republic & 1992 \\ 
  Congo, Republic & 2002 & Nigeria & 1994 \\ 
  Congo, Dem Rep & 2006 & Congo, Dem Rep & 1996 \\ 
  Ethiopia & 1995 & Ethiopia & 1993 \\ 
  Gambia & 1996 & Belarus & 2001 \\ 
  Ghana & 1995 & Belarus & 2000 \\ 
  Jordan & 1993 & Swaziland & 2007 \\ 
  Kazakhstan & 1995 & Sudan & 1994 \\ 
  Kenya & 1992 & Laos & 1997 \\ 
  Kyrgyzstan & 1995 & Belarus & 1998 \\ 
  Pakistan & 2002 & Algeria & 1993 \\ 
  Rwanda & 2003 & Rwanda & 1999 \\ 
  Sudan & 2000 & Sudan & 2006 \\ 
  Tajikistan & 1995 & Belarus & 1999 \\ 
  Tanzania & 1995 & Sierra Leone & 1992 \\ 
  Togo & 1994 & Togo & 1991 \\ 
  Uganda & 2006 & Uganda & 1998 \\ 
  Uzbekistan & 1999 & Ethiopia & 1993 \\ 
   \hline
\end{tabular}
\caption{The matched sample of country years}
\label{tab:matched_pairs}
\end{table}

### 2014-11-21 writeups/introduction.tex
finish model description

\section{Introduction}

Once disregarded as mere ``window-dressing'', authoritarian institutions have garnered the attention of scholars as an important tool for power sharing, which, in turn, leads to various substantive effect, including regime survival, increased investment, better economic performance.

While our understanding of authoritarian institution has branched to numerous substantive topics, its causal root deserves more careful studies. Given its common definition as the ``rule of the game'', institutions are fundamentally a set of constraints of human interactions, and thus its effect must be most evident in the interaction between the strategic actors itself.  When scholars study the effect of institutions on various substantive areas, inevitably the causal chain must pass through the strategic actions of the actors, mostly through the logic of credible and regular spoil sharing (cite Przworski, Svolik). This causal step is theoretically crucial to all of our findings regarding authoritarian institutions – the goal of this article is, therefore, to empirically examine it.

Beyond its theoretical contribution, a study of violence in partially liberalized dictatorship has immense real-world importance. Indeed, violence during political liberalization is the greatest concern of many would-be democrats living under authoritarian regimes. For example, Chinese citizens show overwhelming enthusiasm when asked about democratic features such as popular accountability, separation of power, and political liberalism, yet remain consistently cautious of instability caused by transition (Chu 2008, 309). Understanding whether and why countries experience increased violence during liberalization is crucial for the prospect of democracy.

\section{Argument and Structure}

This article argues that if the authoritarian legislature is indeed a credible commitment and informational device, then we should see decreased level of violence between the regime and the dissdent in the presence of an authoritarian legislature. Indeed, taking a page from the rationalist war literature, I explains how political violence should only happen when the regime and the opposition misjudge one another's capacity and preference. Given transparent information and a commitment device, regardless of the capacity and preference of both sides, negotiating to reach an agreement is always preferable to violence due to the savings in the social cost of violence.

Armed with this theoretical argument, I empirically examine the level of violence in regime-dissident interaction using a novel event dataset across authoritarian regime post Cold War. I constructed the data by looking explicitly at countries that create their legislature during their authoritarian spells and matched these countries with those of the same conditions but did not create legislature. In addition to this large-n investigation, I zoom in at the causal mechanism with a survey experiment implemented in Vietnam, a hard case for the theory of legislature on regime-dissident interaction. These studies show that blah blah blah.

The article will proceed as follows:

### 2014-11-21 writeups/multilevel.tex
finish model description

--- 2014-10-23 writeups/multilevel.tex
@@
-\documentclass[12pt]{article}
+\subsection{The model}
 
-% This first part of the file is called the PREAMBLE. It includes
-% customizations and command definitions. The preamble is everything
-% between \documentclass and \begin{document}.
+Given that my dependent variable of interest (\textit{violence}) is at the event level, while my ``treatment'' (\textit{legislature}) is at the country year level, a Bayesian hierarchical model as the most appropriate choice.\footnote{The choice of Bayesian hierarchical model is largely practical: with 15,037 events, popular R packages to fit frequentist hierarchical model do not converge due to a high chance of numerical issues.}  Each event belongs to a country-year, and each country-year belongs to a country.
+The intercept at each level varies according to the group the unit belongs to.
+This model choice is superior to the alternative option, which is to aggregate the event-level data up to the country-year level and run a fixed effect model.
+Doing so will 1) ignore the variation at the event level, resulting in standard errors that are too small; 2) leave the aggregation mechanisms up to the researcher with no clear theoretical reasoning.\footnote{Should we measure the level of violence within a country year by averaging across events?
+Why not the median?
+Or count the number of positive / negative events?
+The choice is not likely to be theoretically driven and open to abuse.}
 
-\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
-\usepackage{graphicx}              % to include figures
-\usepackage{amsmath}               % great math stuff
-\usepackage{amsfonts}              % for blackboard bold, etc
-\usepackage{amsthm}                % better theorem environments
+All parameters have conjugate un-informative prior so that the result is driven entirely by the data instead of the prior.\footnote{More specifically, the prior for coefficient estimates is $Normal(\text{mean}=0, \text{precision}=.0001)$.
+The prior for the variance parameters is $Inverse-Gamma(1, 1)$} The model is thus:
 
-% various theorems, numbered by section
+\begin{alignat*}{2}
+&{event}_i &&\sim N(\alpha^{countryyear}_{j[i]} + A \cdot \text{sector}_i, \sigma^2_{event}) \\
+&\alpha_j^{countryyear} &&\sim N(\beta_{k[j]}^{country} + \gamma \cdot \text{legis}_j + \Gamma X_j, \sigma_{\alpha}^2) \\
+&\beta_k^{country} &&\sim N(\delta_0 + \delta_{ethnic} \cdot \text{ethnic}_k + D \cdot \text{region}, \sigma_\beta^2) 
+\end{alignat*}
 
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{conj}[thm]{Conjecture}
+At the event level:
 
-\DeclareMathOperator{\id}{id}
+\begin{conditions*}
+\alpha^{countryyear}_{j[i]}    &  intercept of $countryyear_j$ to which $event_i$ belongs\\
+\text{sector}_i     &  matrix of dummies for the dissident sector of $event_i$  \\
 
-\newcommand{\bd}[1]{\mathbf{#1}}  % for bolding symbols
-\newcommand{\RR}{\mathbb{R}}      % for Real numbers
-\newcommand{\ZZ}{\mathbb{Z}}      % for Integers
-\newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
-\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
+\end{conditions*}
 
-\begin{document}
+At the country year level:
+\begin{conditions*}
+\beta_{k[j]}^{country} &  intercept of $country_k$ to which $countryyear_j$ belongs. In traditional panel data model, this is the country fixed effect. \\
+\text{legis}_j & dummy variable for legislature. This is our parameter of interest. \\
+X_j & matrix of other control variables, including log(GDP), log(GDP per capita), military expenditure (as \% of GDP), oil and mineral export (as \% of GDP), regime duration (years), and authoritarian typology (military, personal, and party as coded by Geddes et.
+al)
+\end{conditions*}
 
-\nocite{*}
+At the country level:
+\begin{conditions*}
+\text{ethnic} & level of ethnic fractionalization as defined by Fearon \\
+\text{region} & matrix of regional dummies
+\end{conditions*}
 
-\title{A Sample Mathematics Paper}
-
-\author{Anh Le\thanks{Grant support listed here.} \\ 
-Department of Political Science \\
-Duke University \\
-Durham, NC 27708 USA}
-
-\maketitle
-
-\begin{abstract}
-  Mathematical model of my authoritarian violence paper
-\end{abstract}
-
-\section{Multilevel model with instrumental variable}
-
-Unit indexed by $i$, group indexed by $j$. Model with treatment $T$ and IV $z$ both at the group level. There are also covariates at the group level, and none at the individual level.
-
-\begin{align}
-y_i &\sim N(\alpha_{j[i]}, \sigma_y^2) \\
-\col{\alpha_j \\ T_j} &\sim 
-N \left(
-    \col{\gamma_0 + \gamma_1 T_j + \gamma_2 x_j\\\mu_0 + \mu_1 z_j} ,
-    \left[
-    \begin{matrix}
-      \sigma^2_\alpha & \rho \sigma_\alpha \sigma_T \\
-      \rho \sigma_\alpha \sigma_T & \sigma^2_T
-    \end{matrix}
-    \right]
-\right)
-\end{align}
-
-In our paper,
-
-\begin{align}
-T_j &= \text{legislature in country-year}_j \\
-z_j &= \text{inherited parties in country-year}_j \\
-x_j &= \text{other covariates in country-year}_j
-\end{align}
-
-Notice that in the model, $T_j$ is not assumed to be uncorrelated with the error term of $\alpha_j$ (the non-diagonal covariance is non-zero), but $z_j$ is (implicitly since it's un-modeled).
-Writing it out in non-multilevel form:
-
-\begin{align}
-\alpha_j &= \gamma_0 + \gamma_1 T_j + \gamma_2 x_j + \epsilon_\alpha = N(\gamma_0 + \gamma_1 T_j + \gamma_2 x_j, \sigma_\alpha)\\
-T_j &= \mu_0 + \mu_1 + \epsilon_T = N(\mu_0 + \mu_1, \sigma_T)
-\end{align}
-
-In the multilevel model, we allow $T_j$ to be correlated with $\epsilon_\alpha$ via $\rho \sigma_\alpha \sigma_T$
-
-\end{document}
+I fit this model with a Gibbs sampler written in JAGS, running 3 chains, each has 11,000 iterations with 1,000 burn-ins.
+The mixing is excellent and the result is consistent across 3 chains.
+More model diagnostics details can be seen in \autopageref{sec:modeldiagnostic}

### 2014-11-21 writeups/multilevel_instrumental.tex
finish model description

\section{Multilevel model with instrumental variable}

Unit indexed by $i$, group indexed by $j$. Model with treatment $T$ and IV $z$ both at the group level. There are also covariates at the group level, and none at the individual level.

\begin{align}
y_i &\sim N(\alpha_{j[i]}, \sigma_y^2) \\
\col{\alpha_j \\ T_j} &\sim 
N \left(
    \col{\gamma_0 + \gamma_1 T_j + \gamma_2 x_j\\\mu_0 + \mu_1 z_j} ,
    \left[
    \begin{matrix}
      \sigma^2_\alpha & \rho \sigma_\alpha \sigma_T \\
      \rho \sigma_\alpha \sigma_T & \sigma^2_T
    \end{matrix}
    \right]
\right)
\end{align}

In our paper,

\begin{align}
T_j &= \text{legislature in country-year}_j \\
z_j &= \text{inherited parties in country-year}_j \\
x_j &= \text{other covariates in country-year}_j
\end{align}

Notice that in the model, $T_j$ is not assumed to be uncorrelated with the error term of $\alpha_j$ (the non-diagonal covariance is non-zero), but $z_j$ is (implicitly since it's un-modeled). Writing it out in non-multilevel form:

\begin{align}
\alpha_j &= \gamma_0 + \gamma_1 T_j + \gamma_2 x_j + \epsilon_\alpha = N(\gamma_0 + \gamma_1 T_j + \gamma_2 x_j, \sigma_\alpha)\\
T_j &= \mu_0 + \mu_1 + \epsilon_T = N(\mu_0 + \mu_1, \sigma_T)
\end{align}

In the multilevel model, we allow $T_j$ to be correlated with $\epsilon_\alpha$ via $\rho \sigma_\alpha \sigma_T$

### 2014-11-21 writeups/theory.tex
finish model description

\section{Theory: Authoritarian legislature and its effect on political violence}

\subsection{Legislature reducing violence}

To consider whether violent means is chosen to reach their goal, we need a theoretical framework to understand how the opposition and the regime engage in the bargaining game. A possible starting point is the bargaining models developed for democratic legislatures, where bargaining outcomes are driven by various institutional rules (positive and negative rule, sequencing of these powers, first-mover advantage, etc.) (Baron and Ferejohn 1989; Cox 2006). However, this type model is not suited to analyze the bargaining under an authoritarian regime, where the institutional rules themselves are under constant threat of being revised by the final arbiter that is violence. In other words, the end game of legislative bargaining now has an extra node that is whether either side will violently suppress the other’s demand. Given this context, the decision of the autocrat and the opposition is better characterized as a bargaining game in anarchy, very much like the bargaining between two sovereign states with the option of going to war (Fearon 1995).

To formally model the interaction, let the negotiation between the opposition and the regime be about the share $x$, $(0 < x < 1)$ of a good (normalized as 1) given to the opposition. (For concreteness we can think of this as the share of the economy’s rent or capital stock). Both sides have the option 1) to bargain and decide on x, or 2) to engage in violent protest / repression. Violence is costly compared to peaceful negotiation---we call this difference in relative cost $c_A$ and $c_O$ for the autocrat and the opposition, respectively. If violence happens, whichever side emerges victorious decides the share x to his heart’s desire---i.e. the winning autocrat would give 0 to the opposition and the winning opposition would give 1 to itself.

Given the uncertain nature of collective action battles, the utility of engaging in violence for the two sides is best formulated as an expected utility that depends on the probability of the opposition winning (call this probability $p$). Thus, the expected utility of the opposition is $p – c_O$, while the expected utility of the ruling regime is $1 - p - c_A$. These two expected utilities sum to less than one, which raises the puzzle why the two sides fail to engage in ex-ante bargaining that splits the difference, giving both sides a higher payoff than the expected utility of violence. Indeed, any amount of x between $(p - c_O, p + c_A)$, i.e. the bargaining range, is more desirable than violence to both sides.

Yet war happens between states and so does violence under authoritarian regimes. The international relations literature suggests three factors that may lead to violence, all of which having a legislature can help alleviate.

\begin{enumerate}
\item Information asymmetry regarding $p$

Due to the incentive to bluff, both sides only have incomplete information about the capability of the other. This leads to differing estimate of $p$, leading to non-overlapping preferences. This information asymmetry can be alleviated by having an elected legislature that helps the autocrat identify the collective action capability of the opposition. During regular legislative sessions, the regime can observe the position of opposition legislators to gauge their unity strength. Furthermore, during elections, both sides’ mobilization effort provides information to the other about its collective action capability without actually resorting to violence. The real, competitive stake of these elections also means that both sides are exerting its best effort, reducing the risk of bluffing and deception. Therefore, the autocrat can trust the information it receives about the opposition’s capability $(p)$, and consequently has a better idea about the political constraint that it faces.

\item The bargaining range $(p - c_O, p + c_A)$ depends on the value of $c_O and c_A$

Having an elected legislature can also increase $c_A$ and $c_O$, i.e. the cost of violence compared to peaceful negotiation. First, elections provide the opposition with a platform to influence policy making without resorting to violence (Rigger 1999, 14). Despite inevitable electoral manipulations, voters still know who the candidates are and can vote in support of their message. While these votes will not dethrone the regime, they serve as an informal referendum that alerts the regime about the popularity of its policies. In this way, the opposition can influence the agenda without winning the election itself. Indeed, if participation in the electoral game proves to be an attractive option to the opposition, radicalizing becomes relatively more costly as a means of gaining influence.

Second, in Dahlian terms, elections also tempt the ruling regime to stay within the institutionalized game by raising the cost of repression (Dahl 1971, 15). Indeed, elections “open up avenues of collective protest” by creating convergent social expectations that are both large in scope (affecting all citizens) and concentrated in time frame (Schedler 2009). Furthermore, by participating in elections, the opposition builds up its organizational strength, which can be used to mobilizing votes as well as organizing protest (Thompson and Kuntz 2004).

In addition, upholding elections and institutional bargaining is an attractive option for regimes to build their legitimacy and assuage grievances about past infractions (Lindberg 2009, 339). By adapting its policies based on election results, the regime can also bring its position closer to the popular will in incremental steps, each with acceptable cost. Indeed, it is not contradictory to say that an authoritarian regime may protect voters’ rights or respond to their demands as a strategy for the regime to stay in power, because there are often hard-liners and reformists within the regime. If the reformists’ strategy of electoral engagement proves to be a successful alternative to maintain power, more members of the regime will be tempted to become liberal-minded.

\item Unit indivisibility: the contested good may not be divided continuously

A final possibility that leads to violence is that the opposition and the ruling regime may be fighting over issues that cannot be continuously divided. For example, were the contested issue about whether religious law should be adopted, it may not be possible to split the issue space to arrive at a compromise within the (p - cO, p + cA) range. An elected legislature again ameliorates this problem. By providing an arena in which both sides can engage in multiple negotiations along many policy issues, it provides more opportunities for side payments. In contrast, were the opposition shut out of the policy making entirely, the only way they could gain influence is to arouse the populace to violent protest. The best way to do so is not via a nuanced discussion of multiple policy points but an intense focus on a highly contentious issue, further exacerbating the problem of unit indivisibility. Therefore, we should expect elected legislature to provide better opportunities for negotiation.

In sum, the overarching of over these causal mechanisms is that the elected legislature provides an arena for the ruling and the opposition to interact, gain information, and adjust strategies. In game theoretic sense, by lengthening the horizon and improve the regularity of stakes, repeated interaction encourage players to think about the future and deter the temptation to radicalize. Overall, these effects encourage incremental changes over radical tactic and favor cooperation over defection (Axelrod 1984). This leads to our hypothesis that:

H1: Authoritarian regimes that create a legislature will experience less violence in its interaction with the dissidents.
\end{enumerate}

\subsection{Legislature increasing violence}
Throughout the previous model, it is implied that the actors’ utility functions remain static with the only parameters being the cost of violence and the share of the issue space. Yet this assumption may miss the dynamism of the opposition’s democratic expectation, which becomes increasingly demanding as the regime starts liberalizing.

Speaking about this issue, Ted Gurr hypothesizes, “The potential for collective violence varies strongly with the intensity and the scope of relative deprivation among members of a collectivity.” Relative deprivation, in turn, is defined as the perceived discrepancy between value expectation (what people believe they are entitled to) and value capability (what the people believe they are able to attain) (1970, 24). Seen under this light, repeated elections may increase the potential for political violence by raising the democratic expectation, which can lead to violent protest if unfulfilled. The effect of elections is especially potent because it affects all citizens, thus raising not only the intensity but also the scope of relative deprivation.

Indeed, unfulfilled political expectation is a common case of relative deprivation causing violence. Historical examples are numerous, spanning various time periods as well as scopes of conflict: from the Puritan Revolution of 1640-60, which was sparked by attempts of the Stuart kings to reinstate royal absolutism, to the protest in twentieth-century colonies, which often followed the imposition of restrictions after a period of political liberalization (1970, 115). This pattern makes sense because, when people have tasted freedom, not only do they want more rights but they also consider rights more important. In other words, the opposition may not simply optimize its share of the issue space but also develops a minimum level of acceptable concession. If opposition’s expectation rises too quickly, the ruling regime may not have enough time to appropriate adjust their position especially if the hard-liners are also trying to retrench given signs of a political spiral. For this reason, it is plausible that electoral authoritarianism leads to more violent interaction between the ruling regime and the opposition.

### 2014-11-21 writeups/multilevel_result.tex
start putting in results

\section{Result}

$Pr(liec > 0) = 0.8920333$ close to significant.

\begin{figure}[ht]
    \centering
    \includegraphics[width=.75\textwidth]{../fig/liec_posterior}
    \label{fig:liec_posterior}
\end{figure}

### 2014-11-21 R/matching_genetic.R

@@ -69,7 +69,6 @@ mgen1 <- Match(Tr=Tr, X=X, Weight.matrix=gen1)
 
 balance_vars <- paste(c(names(BalanceMatrix)[1], paste("+", names(BalanceMatrix)[-1])), collapse=" ")
 fm_gen1 <- as.formula(paste(paste0(c_treatmentvar, ".", c_pretreat_length), "~", balance_vars))
-MatchBalance(fm_gen1, data=cbind.data.frame(liec6.1=Tr, BalanceMatrix), match.out=mgen1, nboots=1000)
 stopCluster(cl)
 
 par(mfrow=c(1, 2))

### 2014-11-21 R/multilevel.R

@@ -133,7 +133,7 @@ reg.fit.mcmc = as.mcmc(reg.fit)
 # densityplot(reg.fit.mcmc)
 
 quantile(reg.fit$BUGSoutput$sims.matrix[,"g.liec"], c(.025, .05, .5, .95, .975))
+mean(reg.fit$BUGSoutput$sims.matrix[,"g.liec"] > 0)
+# HPDinterval(reg.fit.mcmc[,"g.liec"], prob=0.95
 
-plot(density(reg.fit$BUGSoutput$sims.matrix[,"g.liec"]))
-mean(reg.fit$BUGSoutput$sims.matrix[,"g.liec"] >= 0)
-# HPDinterval(reg.fit.mcmc[,"g.liec"], prob=0.95)
+save(reg.fit, reg.fit.mcmc, file="./data/private/multilevel_mcmc_result.RData")

### 2014-11-21 writeups/experiment_checking.tex
writing on experiment

\subsection{Checking the experimental assumption}

Since the two prompts are randomly sent out to business, we have excellent balance across observable co-variates as shown in \autoref{tab:balance}.

In addition, to guard against concerns that this question may be politically sensitive, leading to systematic bias in non-response, I also check and confirm that firms with the treatment form does not have a different non-response rate ($\textbf{p-value} = 0.12$).

\begin{table}[ht]
\centering
\begin{tabular}{rrrrl}
  \hline
 & Mean treated & Mean control & p-value &   \\ 
  \hline
Limited Liability & 0.54 & 0.57 & 0.09 & * \\ 
  Joint Stock & 0.23 & 0.23 & 0.84 &  \\ 
  Partnership & 0.00 & 0.00 & 0.38 &  \\ 
  Other form of ownership & 0.01 & 0.00 & 0.03 & ** \\ 
  Manufacturing & 0.08 & 0.09 & 0.57 &  \\ 
  Construction & 0.28 & 0.27 & 0.93 &  \\ 
  Service & 0.66 & 0.67 & 0.47 &  \\ 
  Agriculture & 0.10 & 0.08 & 0.01 & ** \\ 
  Mining & 0.02 & 0.03 & 0.09 & * \\ 
  Revenue (0.5-1 billion VND) & 0.22 & 0.22 & 0.98 &  \\ 
  Revenue (1-5 billion VND) & 0.43 & 0.43 & 0.71 &  \\ 
  Revenue (5-10 billion VND) & 0.07 & 0.08 & 0.23 &  \\ 
  Revenue (10-50 billion VND) & 0.05 & 0.06 & 0.39 &  \\ 
  Revenue (50-200 billion VND) & 0.01 & 0.01 & 0.94 &  \\ 
  Revenue (200-500 billion VND) & 0.00 & 0.00 & 0.81 &  \\ 
  Revenue (above 500 billion VND) & 0.00 & 0.00 & 0.53 &  \\ 
  Size (5-9 people) & 0.36 & 0.34 & 0.12 &  \\ 
  Size (10-49 people) & 0.21 & 0.24 & 0.05 & ** \\ 
  Size (50-199 people) & 0.06 & 0.05 & 0.49 &  \\ 
  Size (200-299 people) & 0.01 & 0.01 & 0.58 &  \\ 
  Size (300-499 people) & 0.00 & 0.00 & 0.20 &  \\ 
  Size (500-1000 people) & 0.00 & 0.00 & 0.81 &  \\ 
  Size (more than 1000 people) & 0.00 & 0.00 & 0.08 & * \\ 
  Main customer (State) & 0.19 & 0.19 & 0.57 &  \\ 
  Main customer (Private) & 0.58 & 0.62 & 0.02 & ** \\ 
  Main customer (Foreign in VN) & 0.05 & 0.04 & 0.33 &  \\ 
  Main customer (Foreign, direct) & 0.03 & 0.03 & 0.25 &  \\ 
  Main customer (Foreign, indirect) & 0.02 & 0.01 & 0.14 &  \\ 
  Equitized local state-owned enterprise & 0.05 & 0.06 & 0.21 &  \\ 
  Equitized central state-owned enterprise & 0.01 & 0.01 & 0.28 &  \\ 
  Firm with some state-owned equities & 0.03 & 0.02 & 0.26 &  \\ 
  Firm that was formerly household business & 0.74 & 0.73 & 0.24 &  \\ 
  Firm with shares listed & 0.01 & 0.00 & 0.39 &  \\ 
  Firm owner graduated from university & 0.62 & 0.63 & 0.91 &  \\ 
  Firm owner with MBA & 0.03 & 0.04 & 0.45 &  \\ 
  Firm owner was a leader of a State agency & 0.04 & 0.03 & 0.37 &  \\ 
  Firm owner was a military officer & 0.05 & 0.04 & 0.26 &  \\ 
  Firm owner was a manager of SOE & 0.13 & 0.12 & 0.22 &  \\ 
  Firm owner was an employee at SOE & 0.15 & 0.15 & 0.87 &  \\ 
   \hline
\end{tabular}
\caption{Covariate balance in survey experiment}
\label{tab:balance}
\end{table}

### 2014-11-21 writeups/experiment_description.tex
writing on experiment

\subsection{Design}

From the large-n analysis, we find suggestive evidence of an authoritarian legislature having a moderating effect on political violence. However, while the matching design alleviates our concern about functional misspecification and incorrect counterfactual, the threat of selection on unobservable remains. Indeed, large variation in the country and country-year intercepts suggests that our model of violence is not yet precise.

Therefore, I follow up the large-n analysis with a survey experiment that aims to affirm a causal prerequisite for my argument. The posited theory about the legislature functioning as an informational and commitment device hinges on the assumption that having legislature actually prompts the co-opted elites to participate in the forum. Otherwise, if the opposition does not consider the legislature to be an effective arena for policy change, then neither can the legislative bargaining provide an attractive alternative to violence nor can the regime gain information about the opposition's capability.

The survey experiment is as follows. Conceptually, the treatment is a country ``having an elected legislature,'' which cannot be randomized. However, in our survey design we can prompt the respondents to think about the legislature as a bargaining arena. My survey question is included in Vietnam's annual business survey PCI (Provincial Competitiveness Index) as follows:

\begin{quote}
(Control prompt) We want to understand how business participate in the process of economic policy making

(Treatment prompt) We want to understand how business participate in the process of economic policy making, \textit{especially since the National Assembly has recently included more delegates that are businessmen} (emphasis added)

Question: Approaching National Assembly delegates to express opinions about economic polices is effective or not?
\end{quote}

Vietnam is an appropriate case for the experiment because Vietnam's growing business sector is being co-opted into the National Assembly. Like China, Vietnam has liberalized its economy while resisting political liberalization. In its 1992 Constitution, drafted when economic reform was already started, the Vietnamese Communist Party (VCP) asserted its role as the vanguard party that commanded the leadership role of the country. At the same time, economic liberalization has created a new class of private entrepreneurs, whose growth becomes increasingly crucial to the country's prosperity and the regime's stability especially when the state-owned sector continues to sluggishly perform.

Given this mismatch between political and economic power, Vietnam is an insightful case study of the co-optation theory with the new class of capitalists being the potential opposition. Indeed, after the 1992 Constitutional revision, the Vietnamese National Assembly (VNA) has included more diverse and assertive, amending law proposed by the executive, albeit without rejecting it. The representation of businessmen and women in the National Assembly has also increased. In 2007 only 1 out of 30 self-nominated candidates won seat in the VNA, while in 2011 4 out of 15 candidates won seats, including two of the country's best known capitalists. (cite http://blogs.reuters.com/global/2011/06/04/party-wins-big-in-vietnam/)

### 2014-11-21 writeups/multilevel_result.tex
writing on experiment

@@
 
-$Pr(liec > 0) = 0.8920333$ close to significant.
+From the posterior distribution, we know that the probability of legislature have$Pr(liec > 0) = 0.89$ close to significant.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ & mean & 2.5\% & 97.5\% & Pr( $>$ 0) & Pr( $<$ 0) \\ 
+  \hline
+legislature & 0.48 & -0.29 & 1.25 & 0.89 &  \\ 
+  log(GDP percap) & -0.39 & -1.31 & 0.52 &  & 0.81 \\ 
+  log(GDP) & 0.37 & -0.19 & 0.92 & 0.91 &  \\ 
+  resource (\%GDP) & -0.01 & -0.04 & 0.02 &  & 0.78 \\ 
+  military exp (\%GDP) & -0.04 & -0.27 & 0.19 &  & 0.63 \\ 
+  regime duration & 0.02 & -0.03 & 0.08 & 0.78 &  \\ 
+  military regime & 2.10 & -1.79 & 5.84 & 0.86 &  \\ 
+  personal regime & 1.60 & -1.65 & 4.89 & 0.83 &  \\ 
+  party regime & 3.09 & -0.10 & 6.31 & 0.97 &  \\ 
+   \hline
+\end{tabular}
+\caption{Hierarchical model parameter estimates}
+\label{tab:hierarchical_estimate}
+\end{table}
 
@@
     \centering
-    \includegraphics[width=.75\textwidth]{../fig/liec_posterior}
-    \label{fig:liec_posterior}
+    \includegraphics[width=\textwidth]{../fig/mcmc_legis}
+    \label{fig:mcmc_legis}
 \end{figure}

### 2014-11-21 R/pci_result.R

@@ -1,0 +1,48 @@
+# ---- Set up workspace ----
+rm(list=ls())
+# Load external functions
+source("./R/functions.R")
+# Load packages
+packs <- c("arm", "foreign", "snow", "Matching", "lme4", "plyr", "dplyr")
+f_install_and_load(packs)
+
+# ---- Constants ----
+c_northprovinces <- c("Ha Giang", "Cao Bang", "Lai Chau", "Lao Cai", "Yen Bai", 
+                      "Tuyen Quang", "Bac Kan", "Thai Nguyen", "Lang Son",
+                      "Son La", "Phu Tho", "Vinh Phuc", "Ha Noi", "Bac Ninh", 
+                      "Bac Giang", "Quang Ninh", "Hai Phong", "Hai Duong", "Ha Nam", 
+                      "Nam Dinh", "Thai Binh", "Ninh Binh")
+c_southprovinces <- c("Lam Dong", "Ninh Thuan", "Binh Thuan", "Tay Ninh", "Binh Phuoc",
+                      "Binh Duong", "TP HCM", "Dong Nai", "BRVT", "Long An", "Dong Thap",
+                      "Tien Giang", "Ben Tre", "Tra Vinh", "Vinh Long", "An Giang", "Can Tho",
+                      "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang")
+
+# ---- Load data ----
+
+d_pci <- read.dta("./data/private/PCI2014_DDI_cleanJ.dta")
+d_lab <- f_stata_to_df(d_pci)
+d_distance <- read.csv("./data/public/distance_from_hanoi.csv")
+
+d_pci <- d_pci %>% 
+  mutate(treat = ifelse(form=="B", 1, 0)) %>%
+  mutate(whether.north = as.factor(ifelse(province %in% c_northprovinces, 1, 
+                                          ifelse(province %in% c_southprovinces, 0, NA)))) %>%
+  mutate(communication = ifelse(i_4_1=="Yes", 1, ifelse(i_4_1=="No", 0, NA))) %>%
+  mutate(representation = ifelse(i_4_2=="Yes", 1, ifelse(i_4_2=="No", 0, NA))) %>%
+  mutate(responded.comm = ifelse(!is.na(communication), 1, 0)) %>%
+  mutate(responded.rep = ifelse(!is.na(representation), 1, 0)) %>%
+  inner_join(d_distance, by=c("province")) %>%
+  rename(distance.from.hn = distance) %>%
[…]

### 2014-11-21 R/plot_result.R

@@ -1,0 +1,50 @@
+rm(list=ls())
+
+library(scales)
+
+load("./data/private/multilevel_mcmc_result.RData")
+
+quantile(reg.fit$BUGSoutput$sims.matrix[,"g.liec"], c(.025, .05, .5, .95, .975))
+mean(reg.fit$BUGSoutput$sims.matrix[,"g.liec"] > 0)
+
+varnames <- c("g.liec")
+printablenames <- c("legislature")
+pdf("./fig/mcmc_legis.pdf", 7, 4)
+par(mfrow=c(1, 2))
+for (i in seq_along(varnames)) {
+  plot(reg.fit$BUGSoutput$sims.matrix[, varnames[i]], type="l", 
+       main=paste("Traceplot of", printablenames[i]), ylab="Estimate")
+  plot(density(reg.fit$BUGSoutput$sims.matrix[, varnames[i]]),
+       main=paste("Posterior of", printablenames[i]))
+  abline(v=0, col="red")
+}
+par(mfrow=c(1, 1))
+dev.off()
+
+varnames <- c("G[1]", "G[2]", "G[3]", "G[4]")
+printablenames <- c("log(GDP percap)", "log(GDP)", "resource (%GDP)", "military exp (%GDP)")
+pdf("./fig/mcmc_diagnostic1.pdf", 8.5, 11)
+par(mfrow=c(length(varnames), 2))
+for (i in seq_along(varnames)) {
+  plot(reg.fit$BUGSoutput$sims.matrix[, varnames[i]], type="l", 
+       main=paste("Traceplot of", printablenames[i]), ylab="Estimate")
+  plot(density(reg.fit$BUGSoutput$sims.matrix[, varnames[i]]),
+       main=paste("Posterior distribution of", printablenames[i]))
+  abline(v=0, col="red")
+}
+par(mfrow=c(1, 1))
+dev.off()
+
+varnames <- c("G[5]", "G[6]", "G[7]", "G[8]")
+printablenames <- c("regime duration", "military regime", "personal regime", "party regime")
+pdf("./fig/mcmc_diagnostic2.pdf", 8.5, 11)
+par(mfrow=c(length(varnames), 2))
+for (i in seq_along(varnames)) {
+  plot(reg.fit$BUGSoutput$sims.matrix[, varnames[i]], type="l", 
+       main=paste("Traceplot of", printablenames[i]), ylab="Estimate")
[…]

### 2014-11-21 R/table_result.R

@@ -1,0 +1,28 @@
+rm(list=ls())
+
+library(scales)
+library(dplyr)
+library(xtable)
+load("./data/private/multilevel_mcmc_result.RData")
+
+varnames <- c("g.liec", "G[1]", "G[2]", "G[3]", "G[4]", "G[5]", "G[6]", "G[7]", "G[8]")
+printnames <- c("legislature", "log(GDP percap)", "log(GDP)", "resource (%GDP)", "military exp (%GDP)",
+                "regime duration", "military regime", "personal regime", "party regime")
+
+tmp <- lapply(1:length(varnames), function(i) {
+  c(quantile(reg.fit$BUGSoutput$sims.matrix[,varnames[i]], c(.5, .025, .975)),
+    mean(reg.fit$BUGSoutput$sims.matrix[, varnames[i]] > 0))
+})
+
+mcmc_result <- data.frame(matrix(unlist(tmp), nrow=9, byrow=T)) %>%
+  mutate(`95% interval` = paste(X2, X3)) %>%
+  mutate(`Pr(param < 0)` = ifelse(X4 > 0.5, NA, 1 - X4)) %>%
+  mutate(`Pr(param > 0)` = ifelse(X4 > 0.5, X4, NA)) %>%
+  select(mean = X1, `2.5% quantile`=X2, `97.5% quantile`=X3, `Pr(param > 0)`, `Pr(param < 0)`)
+rownames(mcmc_result) <- printnames
+
+mcmc_result_tab <- xtable(mcmc_result)
+digits(mcmc_result_tab) <- 2
+print(mcmc_result_tab)
+
+plot(density(reg.fit$BUGSoutput$sims.matrix[,"sigma.a"]))

### 2014-11-21 writeups/experiment_checking.tex
writing on survey result

@@
 Since the two prompts are randomly sent out to business, we have excellent balance across observable co-variates as shown in \autoref{tab:balance}.
-
-In addition, to guard against concerns that this question may be politically sensitive, leading to systematic bias in non-response, I also check and confirm that firms with the treatment form does not have a different non-response rate ($\textbf{p-value} = 0.12$).
 
@@
 \end{table}
+
+In addition, to guard against concerns that the treatment prompt may be politically sensitive, I also check and confirm that firms with the treatment form does not have a different non-response rate ($\textbf{p-value} = 0.12$).
+
+Finally, to guard against systematic bias in non-response, I check the co-variate balance between firms that responded and those that did not in \autopageref{tab:balance_response}.
+The results suggest some issues with co-variate balance: firms with educated CEOs and CEOs with former ties to state businesses respond slightly more.
+This means that the population observed in the experiment may be different, leading to difficulty in generalizing our ATE (average treatment effect) to PATE (population average treatment effect).
+However, educated businessmen with political ties are precisely the group most likely to be co-opted, this is in fact the group that we should pay most attention to.
+Therefore, while our treatment effect may not generalize to ordinary Vietnamese businessman, it does comport with the focus of our study on political elites.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrl}
+  \hline
+ & Mean (resp) & Mean (non-resp) & p-value &   \\ 
+  \hline
+Limited Liability & 0.55 & 0.56 & 0.81 &  \\ 
+  Joint Stock & 0.23 & 0.20 & 0.01 & ** \\ 
+  Partnership & 0.00 & 0.00 & 0.75 &  \\ 
+  Other form of ownership & 0.00 & 0.00 & 0.04 & ** \\ 
+  Manufacturing & 0.09 & 0.08 & 0.42 &  \\ 
+  Construction & 0.27 & 0.24 & 0.00 & *** \\ 
+  Service & 0.67 & 0.68 & 0.15 &  \\ 
+  Agriculture & 0.09 & 0.07 & 0.00 & *** \\ 
+  Mining & 0.02 & 0.02 & 0.03 & ** \\ 
+  Revenue (0.5-1 billion VND) & 0.22 & 0.22 & 0.98 &  \\ 
+  Revenue (1-5 billion VND) & 0.43 & 0.41 & 0.20 &  \\ 
+  Revenue (5-10 billion VND) & 0.08 & 0.08 & 0.84 &  \\ 
+  Revenue (10-50 billion VND) & 0.05 & 0.05 & 0.91 &  \\ 
+  Revenue (50-200 billion VND) & 0.01 & 0.01 & 0.52 &  \\ 
+  Revenue (200-500 billion VND) & 0.00 & 0.00 & 0.85 &  \\ 
+  Revenue (above 500 billion VND) & 0.00 & 0.00 & 0.26 &  \\ 
+  Size (5-9 people) & 0.35 & 0.33 & 0.15 &  \\ 
+  Size (10-49 people) & 0.22 & 0.23 & 0.77 &  \\ 
+  Size (50-199 people) & 0.06 & 0.05 & 0.24 &  \\ 
+  Size (200-299 people) & 0.01 & 0.01 & 0.93 &  \\ 
+  Size (300-499 people) & 0.00 & 0.00 & 0.43 &  \\ 
+  Size (500-1000 people) & 0.00 & 0.00 & 0.96 &  \\ 
+  Size (more than 1000 people) & 0.00 & 0.00 & 0.67 &  \\ 
+  Main customer (State) & 0.19 & 0.17 & 0.02 & ** \\ 
+  Main customer (Private) & 0.60 & 0.63 & 0.01 & ** \\ 
+  Main customer (Foreign in VN) & 0.04 & 0.04 & 0.96 &  \\ 
+  Main customer (Foreign, direct) & 0.03 & 0.03 & 0.85 &  \\ 
+  Main customer (Foreign, indirect) & 0.01 & 0.01 & 0.78 &  \\ 
+  Equitized local state-owned enterprise & 0.06 & 0.05 & 0.35 &  \\ 
+  Equitized central state-owned enterprise & 0.01 & 0.01 & 0.60 &  \\ 
+  Firm with some state-owned equities & 0.03 & 0.02 & 0.52 &  \\ 
+  Firm that was formerly household business & 0.73 & 0.70 & 0.00 & ** \\ 
+  Firm with shares listed & 0.00 & 0.00 & 0.78 &  \\ 
+  Firm owner graduated from university & 0.63 & 0.58 & 0.00 & *** \\ 
+  Firm owner with MBA & 0.04 & 0.03 & 0.06 & * \\ 
+  Firm owner was a leader of a State agency & 0.04 & 0.03 & 0.04 & ** \\ 
+  Firm owner was a military officer & 0.05 & 0.04 & 0.12 &  \\ 
+  Firm owner was a manager of SOE & 0.12 & 0.11 & 0.03 & ** \\ 
+  Firm owner was an employee at SOE & 0.15 & 0.14 & 0.48 &  \\ 
+   \hline
+\end{tabular}
+\caption{Covariate balance between firms that responded and firms that did not}
+\label{tab:balance_response}
+\end{table}

### 2014-11-21 writeups/experiment_result.tex
writing on survey result

\subsection{Result}

Given the experimental design of our survey experiment, estimating the treatment effect is straight forward with a simple logistic regression as reported in \autoref*{tab:survey_result}.

The treatment is highly significant ($p < 0.01$) with a coefficient of 0.264. This means that, when prompted to think about the inclusion of businessmen in the National Assembly, the respondent is 1.3 time more likely to think that participating in economic policy making via the National Assembly is effective.

\begin{table}[!htbp] \centering 
  \caption{Treatment effect in Survey experiment} 
  \label{tab:survey_result} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & Contacting the National Assembly is effective \\ 
\hline \\[-1.8ex] 
 Treatment prompt & 0.264$^{***}$ \\ 
  & (0.073) \\ 
  & \\ 
 Constant & 0.929$^{***}$ \\ 
  & (0.049) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 3,951 \\ 
Log Likelihood & $-$2,253.137 \\ 
Akaike Inf. Crit. & 4,510.274 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2014-11-21 R/pci_result.R

@@ -3,7 +3,7 @@ rm(list=ls())
 # Load external functions
 source("./R/functions.R")
 # Load packages
-packs <- c("arm", "foreign", "snow", "Matching", "lme4", "plyr", "dplyr")
+packs <- c("arm", "foreign", "snow", "Matching", "xtable", "stargazer", "plyr", "dplyr")
 f_install_and_load(packs)
 
 # ---- Constants ----
@@ -35,7 +35,31 @@ d_pci <- d_pci %>%
   rename(distance.from.hn = distance) %>%
   mutate(province = as.factor(province))
 
+# ---- Constant ----
+c_rownames <- c("Limited Liability", "Joint Stock", "Partnership", "Other form of ownership",
+              "Manufacturing", "Construction", "Service", "Agriculture", "Mining",
+              "Revenue (0.5-1 billion VND)", "Revenue (1-5 billion VND)", "Revenue (5-10 billion VND)",
+              "Revenue (10-50 billion VND)", "Revenue (50-200 billion VND)",
+              "Revenue (200-500 billion VND)", "Revenue (above 500 billion VND)",
+              "Size (5-9 people)", "Size (10-49 people)", "Size (50-199 people)",
+              "Size (200-299 people)", "Size (300-499 people)", "Size (500-1000 people)",
+              "Size (more than 1000 people)",
+              "Main customer (State)", "Main customer (Private)", "Main customer (Foreign in VN)",
+              "Main customer (Foreign, direct)", "Main customer (Foreign, indirect)",
+              "Equitized local state-owned enterprise",
+              "Equitized central state-owned enterprise", 
+              "Firm with some state-owned equities",
+              "Firm that was formerly household business",
+              "Firm with shares listed",
+              "Firm owner graduated from university",
+              "Firm owner with MBA",
+              "Firm owner was a leader of a State agency",
+              "Firm owner was a military officer",
+              "Firm owner was a manager of SOE",
+              "Firm owner was an employee at SOE")
+
 # ---- Check balance ----
+
 
 c_balance_vars <- c("a4", "a5_1", "a5_2", "a5_3", "a5_4", "a5_5", "a7_1", "a8_1", "a11",
[…]

### 2014-11-22 writeups/argument_overview.tex
done with all, doing references

\section{The Argument}
\label{sec:argument}

This article argues that if the authoritarian legislature indeed helps institutionalize the regime-dissident interaction, then we should see decreased level of violence between the two sides in the presence of an authoritarian legislature. Taking a page from the rationalist war literature, I explains how political violence should only happen when the regime and the opposition misjudge one another's capacity and preference, or when the bargaining game does not have the option of side payments. Given transparent information, a commitment device, and regular channels to negotiate side payments, reaching an agreement is always preferable to violence due to the savings in the social cost of violence.

Armed with this theoretical argument, I empirically examine the level of violence in regime-dissident interaction using a novel event dataset across authoritarian regime post Cold War. I constructed the data by looking explicitly at countries that create their legislature during their authoritarian spells and matched these countries with those of the same conditions but did not create legislature. In addition to this large-n investigation, I zoom in at the causal mechanism with a survey experiment implemented in Vietnam, testing whether the recent inclusion of businessmen as delegates in the National Assembly prompts business to participate in the legislature. This survey experiment achieves two goals. First, it allows us to have a cleaner causal inference compared to large-n observational data, especially since violence is potentially too complex a process to model completely. Second, it investigates the immediate behavioral response of business to co-optation attempts, which serves as the logical pre-requisite of any secondary material outcomes that relies on the regime and the dissident interacting with each other. I find that the presence of a legislature does reduce violence across regimes, albeit with a modest substantive effect size. On the other hand, the survey experiment conclusively shows that the legislature successfully works as a co-optation device, prompting more willingness to participate in the legislature from business. These two findings together complete the missing links in our understanding of authoritarian institutions. They ascertain that the legislature does foster positive regime-opposition interaction, a necessary condition for regime durability, increased investment, and economic growth.

### 2014-11-22 writeups/conclusion.tex
done with all, doing references

\section{Conclusion}
\label{sec:conclusion}

In this article, I have shown that authoritarian legislature does prompt the opposition to engage with the regime, resulting in regularized and transparent interactions that reduce the level of violence. These two findings contribute to the literature on authoritarian institutions by empirically ascertain two behavioral patterns in regime-opposition interaction that undergird all secondary material outcomes in the extant literature. Indeed, regime survival, increased investment, and economic performance are outcomes far down the causal chain from authoritarian institutions, the behavioral outcomes investigated in this paper most directly follow from institutional change and thus are the best evidence for its effect.

On the other hand, using event data with a high level of granularity, the cross-national hierarchical model also reveals that much of variation in violence across countries and times has not been satisfactorily explained. This finding calls for greater attention to the variation across authoritarian regimes, where institutions with the same name may serve different functions.

### 2014-11-22 writeups/experiment_checking.tex
done with all, doing references

@@
 
-Finally, to guard against systematic bias in non-response, I check the co-variate balance between firms that responded and those that did not in \autopageref{tab:balance_response}.
+Finally, to guard against systematic bias in non-response, I check the co-variate balance between firms that responded and those that did not in \autoref{tab:balance_response}.
 The results suggest some issues with co-variate balance: firms with educated CEOs and CEOs with former ties to state businesses respond slightly more.

### 2014-11-22 writeups/experiment_description.tex
writing on survey result
done with all, doing references

@@
 
-From the large-n analysis, we find suggestive evidence of an authoritarian legislature having a moderating effect on political violence.
+From the large-n analysis, we find suggestive evidence of an authoritarian legislature having a modest effect on political violence.
 However, while the matching design alleviates our concern about functional misspecification and incorrect counterfactual, the threat of selection on unobservable remains.
@@
 However, in our survey design we can prompt the respondents to think about the legislature as a bargaining arena.
-My survey question is included in Vietnam's annual business survey PCI (Provincial Competitiveness Index) as follows:
+My survey question is included in Vietnam's annual business survey PCI (Provincial Competitiveness Index) as follows:\footnote{The PCI is the largest annual business survey in Vietnam, which is designed to assess the ease of doing business, economic governance, and administrative reform efforts \citep{Malesky2013}.
+This year the surveys reaches 8,013 firms.
+The PCI is already well-known and implemented regularly, raising no concern that the business may respond differently if they are aware of being studied (i.e.
+the Hawthorne effect).}
 
@@
 The representation of businessmen and women in the National Assembly has also increased.
-In 2007 only 1 out of 30 self-nominated candidates won seat in the VNA, while in 2011 4 out of 15 candidates won seats, including two of the country's best known capitalists.
-(cite http://blogs.reuters.com/global/2011/06/04/party-wins-big-in-vietnam/)
+In 2007 only 1 out of 30 self-nominated candidates won seat in the VNA, while in 2011 4 out of 15 candidates won seats, including two of the country's best known capitalists \citep{Ruwitch2011}.

### 2014-11-22 writeups/experiment_result.tex
done with all, doing references

@@
 
-\begin{table}[!htbp] \centering 
+The size of this treatment effect is substantively significant given that the presence of businessmen in Vietnam's National Assembly is still limited.
+Furthermore, policy making in Vietnam is still dominated by the Executive branch, with the National Assembly mainly deliberating scripted agenda prepared by the Standing Committee \citep{Montesano2005}.
+Despite these limitations on the participation of business in policy making through the National Assembly, we see that business are still willing to participate in the legislature.
+Therefore, the treatment effect in this survey experiment is likely to be even larger in more open authoritarian legislatures.
+
+\begin{table}[H] 
+  \centering 
   \caption{Treatment effect in Survey experiment} 

### 2014-11-22 writeups/introduction.tex
done with all, doing references

@@
 \section{Introduction}
+\label{sec:introduction}
 
-Once disregarded as mere ``window-dressing'', authoritarian institutions have garnered the attention of scholars as an important tool for power sharing, which, in turn, leads to various substantive effect, including regime survival, increased investment, better economic performance.
+Once disregarded as mere ``window-dressing,'' authoritarian institutions have garnered the attention of scholars as an important tool for power sharing, which, in turn, leads to various substantive effects, including regime survival, increased investment, and better economic performance \citep{Gandhi2008}.
 
 While our understanding of authoritarian institution has branched to numerous substantive topics, its causal root deserves more careful studies.
-Given its common definition as the ``rule of the game'', institutions are fundamentally a set of constraints of human interactions, and thus its effect must be most evident in the interaction between the strategic actors itself.
-When scholars study the effect of institutions on various substantive areas, inevitably the causal chain must pass through the strategic actions of the actors, mostly through the logic of credible and regular spoil sharing (cite Przworski, Svolik).
-This causal step is theoretically crucial to all of our findings regarding authoritarian institutions – the goal of this article is, therefore, to empirically examine it.
+Given its common definition as the ``rule of the game'', institutions are fundamentally a set of constraints on human interactions, and thus its effect must be most evident in the interaction between strategic actors itself.
+When scholars study the effect of institutions on various substantive areas, inevitably the causal chain must pass through the strategic actions of the actors, mainly with the logic of credible and regular spoil sharing (Svolik, Przeworski).
+This causal step is theoretically crucial to all of our findings regarding authoritarian institutions.
+The goal of this article is, therefore, to empirically examine it.
 
 Beyond its theoretical contribution, a study of violence in partially liberalized dictatorship has immense real-world importance.
-Indeed, violence during political liberalization is the greatest concern of many would-be democrats living under authoritarian regimes.
+Indeed, violence during periods of political liberalization is the greatest concern of many would-be democrats living under authoritarian regimes.
 For example, Chinese citizens show overwhelming enthusiasm when asked about democratic features such as popular accountability, separation of power, and political liberalism, yet remain consistently cautious of instability caused by transition (Chu 2008, 309).
-Understanding whether and why countries experience increased violence during liberalization is crucial for the prospect of democracy.
+Therefore, understanding the pattern of violence during liberalization is crucial for the prospect of democracy.
 
-\section{Argument and Structure}
-
-This article argues that if the authoritarian legislature is indeed a credible commitment and informational device, then we should see decreased level of violence between the regime and the dissdent in the presence of an authoritarian legislature.
-Indeed, taking a page from the rationalist war literature, I explains how political violence should only happen when the regime and the opposition misjudge one another's capacity and preference.
-Given transparent information and a commitment device, regardless of the capacity and preference of both sides, negotiating to reach an agreement is always preferable to violence due to the savings in the social cost of violence.
-
-Armed with this theoretical argument, I empirically examine the level of violence in regime-dissident interaction using a novel event dataset across authoritarian regime post Cold War.
-I constructed the data by looking explicitly at countries that create their legislature during their authoritarian spells and matched these countries with those of the same conditions but did not create legislature.
-In addition to this large-n investigation, I zoom in at the causal mechanism with a survey experiment implemented in Vietnam, a hard case for the theory of legislature on regime-dissident interaction.
-These studies show that blah blah blah.
-
-The article will proceed as follows:
+The article will proceed as follows.
+\Cref{sec:argument} presents an overview of the theoretical argument and empirical analyses.
+\Cref{sec:theory} posits two theoretical explanations for the effect of legislature on violence.
+\Cref{sec:empirics_largeN} uses a Bayesian hierarchical model to analyze political violence in authoritarian regimes post-Cold War, showing that the legislature has a modest positive effect.
+\Cref{sec:empirics_survey} uses a survey experiment to demonstrate that co-optation strategy does prompt Vietnamese business to interact with the regime, a pre-requisite for any material outcome such as violence to change.
+\Cref{sec:conclusion} concludes.

### 2014-11-22 writeups/multilevel_datadescription.tex
done with all, doing references

--- 2014-11-21 writeups/empirics_largeN.tex
@@
-\section{Empirics}
-
 \subsection{Description of data}
@@
 \end{itemize}
-
-\subsection{Empirical strategy}
-
-First, my empirical strategy improves over the extant literature with a careful choice of country-years to study.
-Scholars in the authoritarian legislature have customarily count all authoritarian country-years with an existing legislature in the sample.
-However, this risks including dictatorships that passively inherited the legislature from the previous regime, who would rather abolish the institution if not for the fear of backlash.
-On the spreadsheet, such cases would look identical to an autocrat opening up to co-opt the opposition, yet the logic is entirely different.
-To use a cautionary example, in Preworski and Gandhi (1283), the legally enforced two-party legislature under the Brazilian junta government is not a reformist institution created by the autocrat to facilitate power sharing but a gutted down legislature when the election result did not go the regime's way.
-To guard against this possibility, I only look at authoritarian regimes that created  legislature during its rule as the ``treatment'' group.
-(From now on, I will use ``treatment'' as a shorthand for the creation of the legislature).
-
-Second, it is important to recognize that an authoritarian regime without a legislature is not the correct counter factual, and thus make a very poor control group.
-Indeed, a regime may not create a co-opting legislature because there is never a sufficient threat of violence from the opposition.
-Therefore, even though we may see that regimes without legislature are very peaceful, this does not mean that a legislature has no effect on regime-dissident interaction.
-Conversely, a regime under rising violent threat may institute a legislature that successfully puts a lid on the growing discontent.
-However, since the level of violence is now constant, it will look as though the legislature had no effect.
-
-To setup the correct counter factual, I use matching to create a sample of comparable cases.
-The crux of the strategy is to find two country years similar along all covariates in year $t$ (including $\text{violence}_t$), but one has a legislature in the next year while the other does not.
-Then, the difference in violence between these two cases in the ensuing period is attributable to the legislature.
-
-This strategy is implemented as follows.
-First, to construct the treated population, I look at all country years in which an authoritarian legislature is created and build a four-year panel around it, including the one year before the treatment, and the three years after.
-Second, to construct the control population, I build similar four-year panels from all the other authoritarian country years without a legislature.
-Finally, for each panel in my treated population, I find its closest match from the control population based on their first year (which is the pre-treatment year for the treated countries).
-I match on level of violence and other covariates as reported in \autoref{tab:matching_balance_largen}, significantly improving the balance across the board.
-The matched pairs of panel are reported in \autoref{tab:matched_pairs}.
-Given that factors that affect violence may have various non-linear effect, matching alleviates the serious concern about functional misspecification.
-
-In general, matching alone does not recover the correct causal inference when there is selection based on unobservables.
-However, in this case, it addresses the most important concerns.
-First, as discussed above, matching on the level of violence in the pre-treatment year creates a sample of regimes with similar violence trajectory, and thus sets up the correct counter factual.
-Second, even though there is a risk of regimes creating legislature in anticipation of violence, this requires a significant ability from the regime to monitor the capability and the preference of the opposition.
-In the absence of a legislature, this information is likely to come from the security apparatus---therefore, the military expenditure (as a percentage of GDP) is matched on as a proxy control for the regime's capacity to anticipate violence.
-
-\begin{sidewaystable}[ht]
-\centering
-\begin{tabular}{lrrlrrrl}
-  \hline
- & \multicolumn{2}{c}{Pre-Match} &   \multicolumn{2}{c}{Post-Match} \\
-Covariate & Treated mean & Control mean & p-value & Treated mean & Control mean & p-value &  \\ 
-  \hline
-Ethnic Fractionalization \_ & 0.61 & 0.59 & 0.59 & 0.61 & 0.60 & 0.81 &  \\ 
-Violence (Goldstein score) & -4.50 & -4.05 & 0.51 & -4.50 & -4.49 & 0.94 &  \\ 
-$\text{Violence}^2$ & 29.84 & 23.22 & 0.34 & 29.84 & 29.03 & 0.65 &  \\ 
-Regime duration (years) & 12.08 & 34.30 & 0.00*** & 12.08 & 12.71 & 0.71 &  \\ 
-$\text{Regime duration}^2$ & 278.00 & 2783.57 & 0.00** & 278.00 & 287.38 & 0.89 &  \\ 
-Military & 0.08 & 0.06 & 0.67 & 0.08 & 0.12 & 0.57 &  \\ 
-Monarchy & 0.04 & 0.25 & 0.00*** & 0.04 & 0.04 & 1.00 &  \\ 
-Party & 0.29 & 0.48 & 0.07* & 0.29 & 0.29 & 1.00 &  \\ 
-log(gdp) & 22.65 & 23.95 & 0.00*** & 22.65 & 22.78 & 0.67 &  \\ 
-log(gdp per capita) & 7.63 & 8.58 & 0.00*** & 7.63 & 7.65 & 0.95 &  \\ 
-Military expenditure (\% of GDP) & 2.44 & 4.34 & 0.00*** & 2.44 & 2.40 & 0.89 &  \\
-Land (1000 $\text{km}^2$)& 760.22 & 1674.68 & 0.00*** & 760.21 & 783.37 & 0.80 &  \\ 
-Population (million) & 22.62 & 140.73 & 0.00*** & 22.62 & 21.74 & 0.90 &  \\
-Natural Resource Export (\% of GDP) & 14.79 & 22.64 & 0.03** & 14.79 & 14.16 & 0.72 &  \\ 
-Resource $\times$ Ethnic & 8.61 & 14.43 & 0.01** & 8.61 & 8.33 & 0.82 &  \\ 
-   \hline
-\end{tabular}
-\caption{Pre and Post-Matching Balance}
-\label{tab:matching_balance_largen}
-\end{sidewaystable}
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{lrlr}
-  \hline
- \multicolumn{2}{c}{Treatment} &   \multicolumn{2}{c}{Control} \\
-Country & Year & Country & Year \\ 
-  \hline
-Algeria & 1996 & Sudan & 1992 \\ 
-  Angola & 1992 & Angola & 2000 \\ 
-  Azerbaijan & 1992 & Uganda & 1991 \\ 
-  Belarus & 2004 & Belarus & 2000 \\ 
-  Cambodia & 1993 & Laos & 1999 \\ 
-  Central African Republic & 2005 & Uganda & 2001 \\ 
-  Chad & 1997 & Central African Republic & 1992 \\ 
-  Congo, Republic & 2002 & Nigeria & 1994 \\ 
-  Congo, Dem Rep & 2006 & Congo, Dem Rep & 1996 \\ 
-  Ethiopia & 1995 & Ethiopia & 1993 \\ 
-  Gambia & 1996 & Belarus & 2001 \\ 
-  Ghana & 1995 & Belarus & 2000 \\ 
-  Jordan & 1993 & Swaziland & 2007 \\ 
-  Kazakhstan & 1995 & Sudan & 1994 \\ 
-  Kenya & 1992 & Laos & 1997 \\ 
-  Kyrgyzstan & 1995 & Belarus & 1998 \\ 
-  Pakistan & 2002 & Algeria & 1993 \\ 
-  Rwanda & 2003 & Rwanda & 1999 \\ 
-  Sudan & 2000 & Sudan & 2006 \\ 
-  Tajikistan & 1995 & Belarus & 1999 \\ 
-  Tanzania & 1995 & Sierra Leone & 1992 \\ 
-  Togo & 1994 & Togo & 1991 \\ 
-  Uganda & 2006 & Uganda & 1998 \\ 
-  Uzbekistan & 1999 & Ethiopia & 1993 \\ 
-   \hline
-\end{tabular}
-\caption{The matched sample of country years}
-\label{tab:matched_pairs}
-\end{table}

### 2014-11-22 writeups/multilevel_empiricalstrategy.tex
done with all, doing references

--- 2014-11-21 writeups/empirics_largeN.tex
@@
-\section{Empirics}
-
-\subsection{Description of data}
-
-\begin{itemize}
-
-\item Dependent variable: \textit{legislature}, operationalized as $LIEC \geq 5$
-
-As my theoretical argument emphasizes the role of the legislature as an informational and commitment device, I code a country-year as having a legislature if multiple parties are legal.
-Even if opposition parties do not win seat, the electoral process also conveys information about the organizational strength and the preference of both sides.
-This coding rule operationalizes as having LIEC (Legislative Index of Electoral Competitiveness) be 5 or higher in the DPI (Database of Political Institutions).\footnote{The values LIEC are as follows: 4---1 party, multiple candidates; 5---multiple parties are legal but only one party won seats; 6---multiple parties did win seats but the largest party received more than 75\% of the seats; 7---largest party got less than 75\% (DPI 14)}
-
-\item Independent variable: \textit{violence} in regime-dissident interaction
-
-Using a dataset of machine coded news reports around the world from 1991-2012, I am able to look at individual events that happened between the regime and the dissident, enabling an analysis at a highly granular level.
-These event data come from ICEWS (Integrated Crisis Early Warning System), a project funded by DARPA (Defense Advanced Research Projects Agency) to aid the US policy makers in predicting and responding to crises around the world .
-These news articles are harvested from ``over 75 international sources (AP, UPI, and BBC Monitor) as well as regional sources (India Today, Jakarta Post, Pakistan Newswire, and Saigon Times),'' ensuring comprehensive coverage  (cite O'Brien 2010 (94), 2013).
-While this dataset has been de-duplicated once so that an event covered by multiple news report only shows up once, I created my own filter to delete duplicates that share the same source actor, target actor, and happen at the same time and place.
-
-These text data are then processed with Schrodt's TABARI event data coding system to determine the nature and the intensity of the reported political activity.
-In addition, the event is matched with a dictionary of actors (with over 8,000 entries) that further divides into five broad categories: religious, governmental, dissidents, business, and other.
-In sum, from this database I am able to extract any interaction between the government and the dissident, where and when it happens, and its level of violence (measured by the Goldstein score\footnote{The Goldstein score is a measure of intensity of conflict or cooperation, developed by Joshua S.
-Goldstein.
-The score has values from -10 (Military attack, clash, assault), 0 (Explain or state policy, state future position) to 8.3(Extend military assistance) See Goldstein 375 for how the event types are coded into this scale).}
-\end{itemize}
-
 \subsection{Empirical strategy}
@@
 Second, to construct the control population, I build similar four-year panels from all the other authoritarian country years without a legislature.
-Finally, for each panel in my treated population, I find its closest match from the control population based on their first year (which is the pre-treatment year for the treated countries).
+Finally, for each panel in my treated population, I use genetic matching to find its closest match from the control population based on their first year (which is the pre-treatment year for the treated countries).
 I match on level of violence and other covariates as reported in \autoref{tab:matching_balance_largen}, significantly improving the balance across the board.
@@
  & \multicolumn{2}{c}{Pre-Match} &   \multicolumn{2}{c}{Post-Match} \\
-Covariate & Treated mean & Control mean & p-value & Treated mean & Control mean & p-value &  \\ 
+Covariate & Treated & Control & p-value & Treated & Control & p-value &  \\ 
   \hline
-Ethnic Fractionalization \_ & 0.61 & 0.59 & 0.59 & 0.61 & 0.60 & 0.81 &  \\ 
+Ethnic Fractionalization & 0.61 & 0.59 & 0.59 & 0.61 & 0.60 & 0.81 &  \\ 
 Violence (Goldstein score) & -4.50 & -4.05 & 0.51 & -4.50 & -4.49 & 0.94 &  \\ 
@@
 log(gdp per capita) & 7.63 & 8.58 & 0.00*** & 7.63 & 7.65 & 0.95 &  \\ 
-Military expenditure (\% of GDP) & 2.44 & 4.34 & 0.00*** & 2.44 & 2.40 & 0.89 &  \\
+Military expenditure (\%GDP) & 2.44 & 4.34 & 0.00*** & 2.44 & 2.40 & 0.89 &  \\
 Land (1000 $\text{km}^2$)& 760.22 & 1674.68 & 0.00*** & 760.21 & 783.37 & 0.80 &  \\ 
 Population (million) & 22.62 & 140.73 & 0.00*** & 22.62 & 21.74 & 0.90 &  \\
-Natural Resource Export (\% of GDP) & 14.79 & 22.64 & 0.03** & 14.79 & 14.16 & 0.72 &  \\ 
+Resource Export (\%GDP) & 14.79 & 22.64 & 0.03** & 14.79 & 14.16 & 0.72 &  \\ 
 Resource $\times$ Ethnic & 8.61 & 14.43 & 0.01** & 8.61 & 8.33 & 0.82 & \\

### 2014-11-22 writeups/multilevel_model.tex
done with all, doing references

--- 2014-11-21 writeups/multilevel.tex
@@
 This model choice is superior to the alternative option, which is to aggregate the event-level data up to the country-year level and run a fixed effect model.
-Doing so will 1) ignore the variation at the event level, resulting in standard errors that are too small; 2) leave the aggregation mechanisms up to the researcher with no clear theoretical reasoning.\footnote{Should we measure the level of violence within a country year by averaging across events?
+Doing so will 1) ignore the variation at the event level, resulting in standard errors that are too small and thus false positives; 2) leave the aggregation mechanisms up to the researcher with no clear theoretical reasoning.\footnote{Should we measure the level of violence within a country year by averaging across events?
 Why not the median?
@@
 
-I fit this model with a Gibbs sampler written in JAGS, running 3 chains, each has 11,000 iterations with 1,000 burn-ins.
-The mixing is excellent and the result is consistent across 3 chains.
-More model diagnostics details can be seen in \autopageref{sec:modeldiagnostic}
+I fit this model with a Gibbs sampler written in JAGS, running three chains, each has 11,000 iterations with 1,000 burn-ins.
+The mixing in the traceplot is excellent (i.e.
+having little autocorrelation) and does not vary across three chains, meaning that our sampling process has accurately approximated the true posterior distribution of the model's parameters.
+(See \autopageref{sec:modeldiagnostic} for more model diagnostics).

### 2014-11-22 writeups/multilevel_result.tex
done with all, doing references

@@
 
-From the posterior distribution, we know that the probability of legislature have$Pr(liec > 0) = 0.89$ close to significant.
+Having obtained the posterior distribution of the parameters, we can calculate their means, 95\% credible interval, and the probabilities of them being different from 0 (See \autoref{tab:hierarchical_estimate}).
+Having an legislature improves the positivity in regime-dissident interaction by 0.48 point along the Goldstein scale, and we are 89\% certain that this effect is truly positive.
+In addition, a party dictatorship improves the interaction by 3.09, a substantively significant effect.
 
-\begin{table}[ht]
+While this model result provides some support for the moderation effect of authoritarian legislature on political violence, the size of the substantive effect is quite small given that regime-dissdent interactions typically scatter along a 10-unit spectrum on the Goldstein scale (-10 to 0).
+Since our model allows full flexibility in the country-year and country intercepts, it reveals that much of the variation in violence is captured in these group-specific intercepts.
+This suggests that the included set of co-variates, which is standard in the literature, have not fully explained the pattern of violence.
+
+\begin{table}[H]
 \centering

### 2014-11-22 writeups/theory.tex
done with all, doing references

@@
 \section{Theory: Authoritarian legislature and its effect on political violence}
+\label{sec:theory}
 
@@
 However, this type model is not suited to analyze the bargaining under an authoritarian regime, where the institutional rules themselves are under constant threat of being revised by the final arbiter that is violence.
-In other words, the end game of legislative bargaining now has an extra node that is whether either side will violently suppress the other’s demand.
+In other words, the end game of legislative bargaining now has an extra node: whether either side will violently suppress the other’s demand.
 Given this context, the decision of the autocrat and the opposition is better characterized as a bargaining game in anarchy, very much like the bargaining between two sovereign states with the option of going to war (Fearon 1995).
 
-To formally model the interaction, let the negotiation between the opposition and the regime be about the share $x$, $(0 < x < 1)$ of a good (normalized as 1) given to the opposition.
-(For concreteness we can think of this as the share of the economy’s rent or capital stock).
+To formally model the interaction, let the negotiation between the opposition and the regime be about the share $x$, $(0 < x < 1)$ of a good (normalized as 1) given to the opposition.\footnote{For concreteness we can think of this as the share of the economy’s rent or capital stock}.
 Both sides have the option 1) to bargain and decide on x, or 2) to engage in violent protest / repression.
@@
 Thus, the expected utility of the opposition is $p – c_O$, while the expected utility of the ruling regime is $1 - p - c_A$.
-These two expected utilities sum to less than one, which raises the puzzle why the two sides fail to engage in ex-ante bargaining that splits the difference, giving both sides a higher payoff than the expected utility of violence.
+These two expected utilities sum to less than one ($1 - c_A - c_O < 1$), which raises the puzzle why two sides fail to engage in ex-ante bargaining that splits the difference, giving both sides a higher payoff than the expected utility of violence.
 Indeed, any amount of x between $(p - c_O, p + c_A)$, i.e.
@@
 
-\item The bargaining range $(p - c_O, p + c_A)$ depends on the value of $c_O and c_A$
+\item The bargaining range $(p - c_O, p + c_A)$ depends on the value of $c_O$ and $c_A$
 
@@
 
-H1: Authoritarian regimes that create a legislature will experience less violence in its interaction with the dissidents.
+\begin{quote}
+H1: Authoritarian regimes that create a legislature will experience less violence in their interaction with the dissidents.
+\end{quote}
 \end{enumerate}
@@
 \subsection{Legislature increasing violence}
+While the prevalent theory of legislature as an informational and commitment device favors hypothesis H1, it is important to note that there are reasons to susepct the opposite.
 Throughout the previous model, it is implied that the actors’ utility functions remain static with the only parameters being the cost of violence and the share of the issue space.
@@
 
-Speaking about this issue, Ted Gurr hypothesizes, “The potential for collective violence varies strongly with the intensity and the scope of relative deprivation among members of a collectivity.” Relative deprivation, in turn, is defined as the perceived discrepancy between value expectation (what people believe they are entitled to) and value capability (what the people believe they are able to attain) (1970, 24).
+Speaking about this issue, Ted Gurr hypothesizes, ``The potential for collective violence varies strongly with the intensity and the scope of relative deprivation among members of a collectivity.'' Relative deprivation, in turn, is defined as the perceived discrepancy between value expectation (what people believe they are entitled to) and value capability (what the people believe they are able to attain) (1970, 24).
 Seen under this light, repeated elections may increase the potential for political violence by raising the democratic expectation, which can lead to violent protest if unfulfilled.
@@
 If opposition’s expectation rises too quickly, the ruling regime may not have enough time to appropriate adjust their position especially if the hard-liners are also trying to retrench given signs of a political spiral.
-For this reason, it is plausible that electoral authoritarianism leads to more violent interaction between the ruling regime and the opposition.
+For this reason, it is plausible that electoral authoritarianism leads to more violent interaction between the ruling regime and the opposition, leading to the second hypothesis:
+
+\begin{quote}
+H2: Authoritarian regimes that create a legislature will experience more violence in their interaction with the dissidents.
+\end{quote}

### 2014-11-22 writeups/introduction.tex
working on references

@@
 
-Once disregarded as mere ``window-dressing,'' authoritarian institutions have garnered the attention of scholars as an important tool for power sharing, which, in turn, leads to various substantive effects, including regime survival, increased investment, and better economic performance \citep{Gandhi2008}.
+Once disregarded as mere ``window-dressing,'' authoritarian institutions have garnered the attention of scholars as an important tool for power sharing, which, in turn, leads to various substantive effects, including regime survival, increased investment, and better economic performance \citep{Gandhi2008, Wright2008, Boix2013}.
 
@@
 Given its common definition as the ``rule of the game'', institutions are fundamentally a set of constraints on human interactions, and thus its effect must be most evident in the interaction between strategic actors itself.
-When scholars study the effect of institutions on various substantive areas, inevitably the causal chain must pass through the strategic actions of the actors, mainly with the logic of credible and regular spoil sharing (Svolik, Przeworski).
+When scholars study the effect of institutions on various substantive areas, inevitably the causal chain must pass through the strategic actions of the actors, mainly with the logic of credible and regular spoil sharing \citep{Gandhi2007, Svolik2012}.
 This causal step is theoretically crucial to all of our findings regarding authoritarian institutions.

### 2014-11-22 writeups/argument_overview.tex
final version,, sent in

@@
 
-Armed with this theoretical argument, I empirically examine the level of violence in regime-dissident interaction using a novel event dataset across authoritarian regime post Cold War.
-I constructed the data by looking explicitly at countries that create their legislature during their authoritarian spells and matched these countries with those of the same conditions but did not create legislature.
+Armed with this theoretical argument, I empirically examine the level of violence in regime-dissident interaction using a novel event dataset across authoritarian regimes post Cold War.
+I construct the dataset by looking explicitly at countries that create a legislature during their authoritarian spells and matched these countries with those of the same conditions but do not create legislature.
 In addition to this large-n investigation, I zoom in at the causal mechanism with a survey experiment implemented in Vietnam, testing whether the recent inclusion of businessmen as delegates in the National Assembly prompts business to participate in the legislature.
@@
 Second, it investigates the immediate behavioral response of business to co-optation attempts, which serves as the logical pre-requisite of any secondary material outcomes that relies on the regime and the dissident interacting with each other.
-I find that the presence of a legislature does reduce violence across regimes, albeit with a modest substantive effect size.
+I find that the presence of a legislature does reduce violence across regimes, albeit with a modest substantive effect size since the model's flexibility lets most of the effects is captured in country and country-year intercepts.
 On the other hand, the survey experiment conclusively shows that the legislature successfully works as a co-optation device, prompting more willingness to participate in the legislature from business.

### 2014-11-22 writeups/experiment_description.tex
final version,, sent in

@@
 In its 1992 Constitution, drafted when economic reform was already started, the Vietnamese Communist Party (VCP) asserted its role as the vanguard party that commanded the leadership role of the country.
-At the same time, economic liberalization has created a new class of private entrepreneurs, whose growth becomes increasingly crucial to the country's prosperity and the regime's stability especially when the state-owned sector continues to sluggishly perform.
+At the same time, economic liberalization has created a new class of private entrepreneurs, whose growth becomes increasingly crucial to the country's prosperity and the regime's stability especially when the state-owned sector continues to sluggishly perform \citep{Avery1993}.
 

### 2014-11-22 writeups/experiment_result.tex
final version,, sent in

@@
 Therefore, the treatment effect in this survey experiment is likely to be even larger in more open authoritarian legislatures.
+
+Given this result, we are more confident that the positive effect of legislature on reducing regime-opposition violence is genuine.
+Indeed, the willingness of the political outsiders to partipate and communicate when given the chance is the necessary ingredient for the legislature to function as an informational and commitment device.
 

### 2014-11-22 writeups/introduction.tex
final version,, sent in

--- 2014-11-22 writeups/introduction.tex
@@
 
-Once disregarded as mere ``window-dressing,'' authoritarian institutions have garnered the attention of scholars as an important tool for power sharing, which, in turn, leads to various substantive effects, including regime survival, increased investment, and better economic performance \citep{Gandhi2008}.
+Once disregarded as mere ``window-dressing,'' authoritarian institutions have garnered the attention of scholars as an important tool for power sharing.
+These institutions are found to have various substantive effects, including regime survival, increased investment, and better economic performance \citep{Gandhi2008, Wright2008, Boix2013, Jensen2012}.
 
 While our understanding of authoritarian institution has branched to numerous substantive topics, its causal root deserves more careful studies.
-Given its common definition as the ``rule of the game'', institutions are fundamentally a set of constraints on human interactions, and thus its effect must be most evident in the interaction between strategic actors itself.
-When scholars study the effect of institutions on various substantive areas, inevitably the causal chain must pass through the strategic actions of the actors, mainly with the logic of credible and regular spoil sharing (Svolik, Przeworski).
-This causal step is theoretically crucial to all of our findings regarding authoritarian institutions.
-The goal of this article is, therefore, to empirically examine it.
+Given its common definition as the ``rule of the game,'' institutions are fundamentally a set of constraints on human interactions, and thus its effect must be most evident in the interaction between strategic actors itself \citep{North1990}.
+And yet most studies have focused on the secondary socioeconomic effects of authoritarian legislature instead of investigating the dynamics of regime-opposition interaction, which is causally prior \citep{Gandhi2007, Svolik2012}.
+The goal of this article is, therefore, to empirically examine this interaction, arguing that authoritarian legislature should reduce poliltical violence by providing information, lengthening the bargaining game, and enabling side payments.
 
@@
 Indeed, violence during periods of political liberalization is the greatest concern of many would-be democrats living under authoritarian regimes.
-For example, Chinese citizens show overwhelming enthusiasm when asked about democratic features such as popular accountability, separation of power, and political liberalism, yet remain consistently cautious of instability caused by transition (Chu 2008, 309).
+For example, Chinese citizens show overwhelming enthusiasm when asked about democratic features such as popular accountability, separation of power, and political liberalism, yet remain consistently cautious of instability caused by transition \citep[309]{Chu2008}.
 Therefore, understanding the pattern of violence during liberalization is crucial for the prospect of democracy.

### 2014-11-22 writeups/multilevel_datadescription.tex
final version,, sent in

@@
 
-\item Dependent variable: \textit{legislature}, operationalized as $LIEC \geq 5$
+\item Independent variable: \textit{legislature}, operationalized as $LIEC \geq 5$
 
-As my theoretical argument emphasizes the role of the legislature as an informational and commitment device, I code a country-year as having a legislature if multiple parties are legal.
+As my theoretical argument emphasizes the role of the legislature as an informational and commitment device, a country-year is coded as as having a legislature if multiple parties are legal.
 Even if opposition parties do not win seat, the electoral process also conveys information about the organizational strength and the preference of both sides.
-This coding rule operationalizes as having LIEC (Legislative Index of Electoral Competitiveness) be 5 or higher in the DPI (Database of Political Institutions).\footnote{The values LIEC are as follows: 4---1 party, multiple candidates; 5---multiple parties are legal but only one party won seats; 6---multiple parties did win seats but the largest party received more than 75\% of the seats; 7---largest party got less than 75\% (DPI 14)}
+This coding rule operationalizes as having LIEC (Legislative Index of Electoral Competitiveness) be 5 or higher in the DPI (Database of Political Institutions).\footnote{The values LIEC are as follows: 4---1 party, multiple candidates; 5---multiple parties are legal but only one party won seats; 6---multiple parties did win seats but the largest party received more than 75\% of the seats; 7---largest party got less than 75\% \citep[14]{Keefer2002}.}
 
-\item Independent variable: \textit{violence} in regime-dissident interaction
+\item Dependent variable: \textit{violence} in regime-dissident interaction
 
@@
 These event data come from ICEWS (Integrated Crisis Early Warning System), a project funded by DARPA (Defense Advanced Research Projects Agency) to aid the US policy makers in predicting and responding to crises around the world .
-These news articles are harvested from ``over 75 international sources (AP, UPI, and BBC Monitor) as well as regional sources (India Today, Jakarta Post, Pakistan Newswire, and Saigon Times),'' ensuring comprehensive coverage  (cite O'Brien 2010 (94), 2013).
+These news articles are harvested from ``over 75 international sources (AP, UPI, and BBC Monitor) as well as regional sources (India Today, Jakarta Post, Pakistan Newswire, and Saigon Times),'' ensuring comprehensive coverage \citep[94]{OBrien2010, OBrien2013}.
 While this dataset has been de-duplicated once so that an event covered by multiple news report only shows up once, I created my own filter to delete duplicates that share the same source actor, target actor, and happen at the same time and place.
 
-These text data are then processed with Schrodt's TABARI event data coding system to determine the nature and the intensity of the reported political activity.
+These text data are then processed with \citet{Schrodt2011}'s TABARI event data coding system to determine the nature and the intensity of the reported political activity.
 In addition, the event is matched with a dictionary of actors (with over 8,000 entries) that further divides into five broad categories: religious, governmental, dissidents, business, and other.
-In sum, from this database I am able to extract any interaction between the government and the dissident, where and when it happens, and its level of violence (measured by the Goldstein score\footnote{The Goldstein score is a measure of intensity of conflict or cooperation, developed by Joshua S.
-Goldstein.
-The score has values from -10 (Military attack, clash, assault), 0 (Explain or state policy, state future position) to 8.3(Extend military assistance) See Goldstein 375 for how the event types are coded into this scale).}
+In sum, from this database I am able to extract any interaction between the government and the dissident, where and when it happens, and its level of violence (measured by the Goldstein score).\footnote{The Goldstein score is a measure of intensity of conflict or cooperation.
+The score has values from -10 (Military attack, clash, assault), 0 (Explain or state policy, state future position) to 8.3(Extend military assistance).
+See \citet[375]{Goldstein1992} for how the event types are coded into this scale).}
 \end{itemize}

### 2014-11-22 writeups/multilevel_empiricalstrategy.tex
final version,, sent in

@@
 First, my empirical strategy improves over the extant literature with a careful choice of country-years to study.
-Scholars in the authoritarian legislature have customarily count all authoritarian country-years with an existing legislature in the sample.
+Scholars in the authoritarian legislature have customarily counted all authoritarian country-years with an existing legislature in the sample.
 However, this risks including dictatorships that passively inherited the legislature from the previous regime, who would rather abolish the institution if not for the fear of backlash.
 On the spreadsheet, such cases would look identical to an autocrat opening up to co-opt the opposition, yet the logic is entirely different.
-To use a cautionary example, in Preworski and Gandhi (1283), the legally enforced two-party legislature under the Brazilian junta government is not a reformist institution created by the autocrat to facilitate power sharing but a gutted down legislature when the election result did not go the regime's way.
+To use a cautionary example, in \citet[1283]{Gandhi2007}, the legally enforced two-party legislature under the Brazilian junta government is not a reformist institution created by the autocrat to facilitate power sharing but a gutted down legislature when the election result did not go the regime's way \citep{Stepan1976}.
 To guard against this possibility, I only look at authoritarian regimes that created  legislature during its rule as the ``treatment'' group.
@@
 Finally, for each panel in my treated population, I use genetic matching to find its closest match from the control population based on their first year (which is the pre-treatment year for the treated countries).
-I match on level of violence and other covariates as reported in \autoref{tab:matching_balance_largen}, significantly improving the balance across the board.
-The matched pairs of panel are reported in \autoref{tab:matched_pairs}.
+I match on level of violence and other covariates as reported in the next page, significantly improving the balance across the board.
+The matched pairs of panel are reported in \Cref{tab:matched_pairs}.
 Given that factors that affect violence may have various non-linear effect, matching alleviates the serious concern about functional misspecification.
@@
 
-\begin{sidewaystable}[ht]
+\begin{sidewaystable}
 \centering
@@
 \end{tabular}
-\caption{Pre and Post-Matching Balance}
+\end{sidewaystable}
 \label{tab:matching_balance_largen}
-\end{sidewaystable}
 
-\begin{table}[ht]
+\begin{table}[H]
 \centering

### 2014-11-22 writeups/multilevel_model.tex
final version,, sent in

@@
 \text{legis}_j & dummy variable for legislature. This is our parameter of interest. \\
-X_j & matrix of other control variables, including log(GDP), log(GDP per capita), military expenditure (as \% of GDP), oil and mineral export (as \% of GDP), regime duration (years), and authoritarian typology (military, personal, and party as coded by Geddes et.
-al)
+X_j & matrix of other control variables, including log(GDP), log(GDP per capita), military expenditure (as \% of GDP), oil and mineral export (as \% of GDP) from \citet{WorldBank2012}; regime duration (years), and authoritarian typology (military, personal, and party as coded by \citet{Geddes2014})
 \end{conditions*}
@@
 \begin{conditions*}
-\text{ethnic} & level of ethnic fractionalization as defined by Fearon \\
+\text{ethnic} & level of ethnic fractionalization as defined by \citet{Fearon2003} \\
 \text{region} & matrix of regional dummies
@@
 The mixing in the traceplot is excellent (i.e.
-having little autocorrelation) and does not vary across three chains, meaning that our sampling process has accurately approximated the true posterior distribution of the model's parameters.
+having little autocorrelation) and does not vary across three chains, meaning that our sampling process has accurately approximated the true posterior distribution of the model's parameters \citep{Gelman2006}.
 (See \autopageref{sec:modeldiagnostic} for more model diagnostics).

### 2014-11-22 writeups/theory.tex
final version,, sent in

@@
 To consider whether violent means is chosen to reach their goal, we need a theoretical framework to understand how the opposition and the regime engage in the bargaining game.
-A possible starting point is the bargaining models developed for democratic legislatures, where bargaining outcomes are driven by various institutional rules (positive and negative rule, sequencing of these powers, first-mover advantage, etc.) (Baron and Ferejohn 1989; Cox 2006).
+A possible starting point is the bargaining models developed for democratic legislatures, where bargaining outcomes are driven by various institutional rules (positive and negative rule, sequencing of these powers, first-mover advantage, etc.) \citep{Baron1989, Cox2006}.
 However, this type model is not suited to analyze the bargaining under an authoritarian regime, where the institutional rules themselves are under constant threat of being revised by the final arbiter that is violence.
 In other words, the end game of legislative bargaining now has an extra node: whether either side will violently suppress the other’s demand.
-Given this context, the decision of the autocrat and the opposition is better characterized as a bargaining game in anarchy, very much like the bargaining between two sovereign states with the option of going to war (Fearon 1995).
+Given this context, the decision of the autocrat and the opposition is better characterized as a bargaining game in anarchy, very much like the bargaining between two sovereign states with the option of going to war \citep{Fearon1995}.
 
-To formally model the interaction, let the negotiation between the opposition and the regime be about the share $x$, $(0 < x < 1)$ of a good (normalized as 1) given to the opposition.\footnote{For concreteness we can think of this as the share of the economy’s rent or capital stock}.
-Both sides have the option 1) to bargain and decide on x, or 2) to engage in violent protest / repression.
+To formally model the interaction, let the negotiation between the opposition and the regime be about the share $x$, $(0 < x < 1)$ of a good (normalized as 1) given to the opposition.\footnote{For concreteness we can think of this as the share of the economy’s rent or capital stock} Both sides have the option 1) to bargain and decide on $x$, or 2) to engage in violent protest / repression.
 Violence is costly compared to peaceful negotiation---we call this difference in relative cost $c_A$ and $c_O$ for the autocrat and the opposition, respectively.
-If violence happens, whichever side emerges victorious decides the share x to his heart’s desire---i.e.
+If violence happens, whichever side emerges victorious decides the share $x$ to his heart’s desire---i.e.
 the winning autocrat would give 0 to the opposition and the winning opposition would give 1 to itself.
@@
 the cost of violence compared to peaceful negotiation.
-First, elections provide the opposition with a platform to influence policy making without resorting to violence (Rigger 1999, 14).
+First, elections provide the opposition with a platform to influence policy making without resorting to violence \citep[14]{Rigger1999}.
 Despite inevitable electoral manipulations, voters still know who the candidates are and can vote in support of their message.
@@
 
-Second, in Dahlian terms, elections also tempt the ruling regime to stay within the institutionalized game by raising the cost of repression (Dahl 1971, 15).
-Indeed, elections “open up avenues of collective protest” by creating convergent social expectations that are both large in scope (affecting all citizens) and concentrated in time frame (Schedler 2009).
-Furthermore, by participating in elections, the opposition builds up its organizational strength, which can be used to mobilizing votes as well as organizing protest (Thompson and Kuntz 2004).
+Second, in Dahlian terms, elections also tempt the ruling regime to stay within the institutionalized game by raising the cost of repression \citep[15]{Dahl1971a}.
+Indeed, elections “open up avenues of collective protest” by creating convergent social expectations that are both large in scope (affecting all citizens) and concentrated in time frame \citep{Schedler2009}.
+Furthermore, by participating in elections, the opposition builds up its organizational strength, which can be used to mobilizing votes as well as organizing protest \citep{Thompson2004}.
 
-In addition, upholding elections and institutional bargaining is an attractive option for regimes to build their legitimacy and assuage grievances about past infractions (Lindberg 2009, 339).
+In addition, upholding elections and institutional bargaining is an attractive option for regimes to build their legitimacy and assuage grievances about past infractions \citep[339]{Lindberg2009}.
 By adapting its policies based on election results, the regime can also bring its position closer to the popular will in incremental steps, each with acceptable cost.
@@
 A final possibility that leads to violence is that the opposition and the ruling regime may be fighting over issues that cannot be continuously divided.
-For example, were the contested issue about whether religious law should be adopted, it may not be possible to split the issue space to arrive at a compromise within the (p - cO, p + cA) range.
+For example, if the contested issue were about whether religious law should be adopted, it may not be possible to split the issue space to arrive at a compromise within the $(p - c_O, p + c_A)$ range.
 An elected legislature again ameliorates this problem.
@@
 In game theoretic sense, by lengthening the horizon and improve the regularity of stakes, repeated interaction encourage players to think about the future and deter the temptation to radicalize.
-Overall, these effects encourage incremental changes over radical tactic and favor cooperation over defection (Axelrod 1984).
+Overall, these effects encourage incremental changes over radical tactic and favor cooperation over defection \citep{Axelrod1984}.
 This leads to our hypothesis that:
@@
 
-Speaking about this issue, Ted Gurr hypothesizes, ``The potential for collective violence varies strongly with the intensity and the scope of relative deprivation among members of a collectivity.'' Relative deprivation, in turn, is defined as the perceived discrepancy between value expectation (what people believe they are entitled to) and value capability (what the people believe they are able to attain) (1970, 24).
+Speaking about this issue, \citet[24]{Gurr1970} hypothesizes, ``The potential for collective violence varies strongly with the intensity and the scope of relative deprivation among members of a collectivity.'' Relative deprivation, in turn, is defined as the perceived discrepancy between value expectation (what people believe they are entitled to) and value capability (what the people believe they are able to attain).
 Seen under this light, repeated elections may increase the potential for political violence by raising the democratic expectation, which can lead to violent protest if unfulfilled.
@@
 If opposition’s expectation rises too quickly, the ruling regime may not have enough time to appropriate adjust their position especially if the hard-liners are also trying to retrench given signs of a political spiral.
-For this reason, it is plausible that electoral authoritarianism leads to more violent interaction between the ruling regime and the opposition, leading to the second hypothesis:
+For this reason, it is plausible that electoral authoritarianism leads to more violent interactions between the ruling regime and the opposition, leading to the second hypothesis:
 

### 2014-12-03 writeups/argument_overview.tex
preparing slides

@@
 This article argues that if the authoritarian legislature indeed helps institutionalize the regime-dissident interaction, then we should see decreased level of violence between the two sides in the presence of an authoritarian legislature.
-Taking a page from the rationalist war literature, I explains how political violence should only happen when the regime and the opposition misjudge one another's capacity and preference, or when the bargaining game does not have the option of side payments.
+Taking a page from the rationalist war literature, I explain how political violence should only happen when the regime and the opposition misjudge each other's capacity and preference, or when the bargaining game does not have the option of side payments.
 Given transparent information, a commitment device, and regular channels to negotiate side payments, reaching an agreement is always preferable to violence due to the savings in the social cost of violence.
@@
 Armed with this theoretical argument, I empirically examine the level of violence in regime-dissident interaction using a novel event dataset across authoritarian regimes post Cold War.
-I construct the dataset by looking explicitly at countries that create a legislature during their authoritarian spells and matched these countries with those of the same conditions but do not create legislature.
+I construct the dataset by looking explicitly at countries that create a legislature during their authoritarian spells and matched these countries with those with the same conditions but do not create legislature.
 In addition to this large-n investigation, I zoom in at the causal mechanism with a survey experiment implemented in Vietnam, testing whether the recent inclusion of businessmen as delegates in the National Assembly prompts business to participate in the legislature.
@@
 First, it allows us to have a cleaner causal inference compared to large-n observational data, especially since violence is potentially too complex a process to model completely.
-Second, it investigates the immediate behavioral response of business to co-optation attempts, which serves as the logical pre-requisite of any secondary material outcomes that relies on the regime and the dissident interacting with each other.
-I find that the presence of a legislature does reduce violence across regimes, albeit with a modest substantive effect size since the model's flexibility lets most of the effects is captured in country and country-year intercepts.
+Second, it investigates the immediate behavioral response of business to co-optation attempts, which serves as the logical pre-requisite to any secondary material outcomes that relies on the regime and the dissident interacting with each other.
+I find that the presence of a legislature does reduce violence across regimes, albeit with a modest substantive effect size since the model's flexibility lets most of the effects be captured in country and country-year intercepts.
 On the other hand, the survey experiment conclusively shows that the legislature successfully works as a co-optation device, prompting more willingness to participate in the legislature from business.

### 2014-12-03 writeups/introduction.tex
preparing slides

@@
 While our understanding of authoritarian institution has branched to numerous substantive topics, its causal root deserves more careful studies.
-Given its common definition as the ``rule of the game,'' institutions are fundamentally a set of constraints on human interactions, and thus its effect must be most evident in the interaction between strategic actors itself \citep{North1990}.
+Given the common definition as the ``rule of the game,'' institutions are fundamentally a set of constraints on human interactions, and thus its effect must be most evident in the interaction between strategic actors itself \citep{North1990}.
 And yet most studies have focused on the secondary socioeconomic effects of authoritarian legislature instead of investigating the dynamics of regime-opposition interaction, which is causally prior \citep{Gandhi2007, Svolik2012}.

### 2014-12-03 writeups/multilevel_datadescription.tex
preparing slides

@@
 As my theoretical argument emphasizes the role of the legislature as an informational and commitment device, a country-year is coded as as having a legislature if multiple parties are legal.
-Even if opposition parties do not win seat, the electoral process also conveys information about the organizational strength and the preference of both sides.
+Even if opposition parties do not win seat, the electoral process still conveys information about the organizational strength and the preference of both sides.
 This coding rule operationalizes as having LIEC (Legislative Index of Electoral Competitiveness) be 5 or higher in the DPI (Database of Political Institutions).\footnote{The values LIEC are as follows: 4---1 party, multiple candidates; 5---multiple parties are legal but only one party won seats; 6---multiple parties did win seats but the largest party received more than 75\% of the seats; 7---largest party got less than 75\% \citep[14]{Keefer2002}.}
@@
 Using a dataset of machine coded news reports around the world from 1991-2012, I am able to look at individual events that happened between the regime and the dissident, enabling an analysis at a highly granular level.
-These event data come from ICEWS (Integrated Crisis Early Warning System), a project funded by DARPA (Defense Advanced Research Projects Agency) to aid the US policy makers in predicting and responding to crises around the world .
+These event data come from ICEWS (Integrated Crisis Early Warning System), a project funded by DARPA (Defense Advanced Research Projects Agency) to aid the US policy makers in predicting and responding to crises around the world.
 These news articles are harvested from ``over 75 international sources (AP, UPI, and BBC Monitor) as well as regional sources (India Today, Jakarta Post, Pakistan Newswire, and Saigon Times),'' ensuring comprehensive coverage \citep[94]{OBrien2010, OBrien2013}.

### 2014-12-03 writeups/multilevel_empiricalstrategy.tex
preparing slides

@@
 
-Second, it is important to recognize that an authoritarian regime without a legislature is not the correct counter factual, and thus make a very poor control group.
+Second, it is important to recognize that an authoritarian regime without a legislature is not the correct counter factual, and thus makes a very poor control group.
 Indeed, a regime may not create a co-opting legislature because there is never a sufficient threat of violence from the opposition.

### 2014-12-03 writeups/prelim_presentation.tex
preparing slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass{beamer}

\mode<presentation> {
\usetheme{Madrid}
}
\setbeamertemplate{navigation symbols}{}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{adjustbox}
\usepackage{amsmath}               % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments

\title[Effect of Authoritarian Legislature]{The Effect of Authoritarian Legislature on Regime-Opposition interaction} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{Anh Le} % Your name
\institute[Duke] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{Duke University \\ % Your institution for the title page
\medskip
\textit{anh.le@duke.edu} % Your email address
}
\date{\today} % Date, can be changed to a custom date

\begin{document}
\setbeamercovered{transparent}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

\section{Motivation}
\begin{frame}
\frametitle{Motivation}
\centering
\includegraphics[width=0.8\textwidth]{legislature_to_pe}
\end{frame}

\begin{frame}
\frametitle{Motivation}
\centering
\includegraphics[width=0.8\textwidth]{legislature_to_behavior}
\end{frame}

\begin{frame}
\frametitle{Overview}
\tableofcontents
\end{frame}

\AtBeginSection[]
{
   \begin{frame}
       \frametitle{Outline}
       \tableofcontents[currentsection]
   \end{frame}
}

\section{The Argument}

\begin{frame}
\frametitle{The Argument}
\begin{itemize}
\item<1-> Theory: Authoritarian legislature provides information, raises cost of violence, and enables side payment. Given these conditions, negotiated peace is more likely than costly violence
\item<2-> Empirical (experimental): A survey vignette experiment that prime Vietnamese businesses to think about the inclusion of businessmen in Vietnam National Assembly. Test whether businesses are more willing to participate in the legislature when primed
\item<3-> Empirical (large-n): Use event data to examine violence in regime-dissident interaction. Use matched panels to construct better counter-factual
\end{itemize}
\end{frame}

%------------------------------------------------

\section{Theory}
\begin{frame}
\frametitle{Regime-Opposition Bargaining Game}
\begin{itemize}
\item Violence is the final arbiter in authoritarian politics
\item Regime-opposition interaction is best modeled as a bargaining game, similar to the bargain between two sovereign states with the option of going to war
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{The Model}
\centering
\begin{itemize}
\item Negotiation about the share $x$ ($0 < x < 1$) of a good given to the opposition
\item Violence costs the autocrat $c_A$ and the opposition $c_O$
\item Expected utility depends on the probability of the opposition winning, $p$
\item<2-> Violence should never happen since $x$ that falls within the bargaining range $(p - c_O, p + c_A)$ is preferable to both sides
\end{itemize}
\includegraphics[width=0.7\textwidth]{general_model}
\end{frame}

\begin{frame}
\frametitle{The Model}
\centering
Violence can still happen if there is:
\begin{itemize}
\item Information asymmetry regarding $p$ leading to non-overlapping bargaining ranges
\only<1>{\includegraphics[width=0.8\textwidth]{information_asymmetry}}
\item<2-> The bargaining range $(p - c_O, p + c_A)$ is too small
\only<2>{\includegraphics[width=0.8\textwidth]{small_range}}
\item<3-> Unit indivisibility
\only<3>{\includegraphics[width=0.8\textwidth]{unit_indivisibility}}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{The Model}
However, authoritarian legislature solves all of these issues
\begin{itemize}
\item Elections and legislative session provide information about both sides' capacity
\item Cost of violent uprising and repression is increased relative to negotiation
\item Negotiations over multiple issues in the legislature enable side payments
\end{itemize}
\end{frame}
\section{Experimental Design}
%------------------------------------------------
\begin{frame}
\frametitle{Experimental Design}

(Control prompt) We want to understand how business participate in the process of economic policy making\\~\\

(Treatment prompt) We want to understand how business participate in the process of economic policy making, \textit{especially since the National Assembly has recently included more delegates that are businessmen} (emphasis added)\\~\\

Question: Is approaching National Assembly delegates to express opinions about economic polices effective or not?

\end{frame}

\begin{frame}
\frametitle{Co-variate Balance}
\begin{columns}[T] % align columns
\begin{column}{.48\textwidth}
\adjustbox{max height=\textheight,
           max width=\textwidth}{
\begin{tabular}{rrrrl}
  \hline
 & Mean treated & Mean control & p-value &   \\ 
  \hline
Limited Liability & 0.54 & 0.57 & 0.09 & * \\ 
  Joint Stock & 0.23 & 0.23 & 0.84 &  \\ 
  Partnership & 0.00 & 0.00 & 0.38 &  \\ 
  Other form of ownership & 0.01 & 0.00 & 0.03 & ** \\ 
  Manufacturing & 0.08 & 0.09 & 0.57 &  \\ 
  Construction & 0.28 & 0.27 & 0.93 &  \\ 
  Service & 0.66 & 0.67 & 0.47 &  \\ 
  Agriculture & 0.10 & 0.08 & 0.01 & ** \\ 
  Mining & 0.02 & 0.03 & 0.09 & * \\ 
  Revenue (0.5-1 billion VND) & 0.22 & 0.22 & 0.98 &  \\ 
  Revenue (1-5 billion VND) & 0.43 & 0.43 & 0.71 &  \\ 
  Revenue (5-10 billion VND) & 0.07 & 0.08 & 0.23 &  \\ 
  Revenue (10-50 billion VND) & 0.05 & 0.06 & 0.39 &  \\ 
  Revenue (50-200 billion VND) & 0.01 & 0.01 & 0.94 &  \\ 
  Revenue (200-500 billion VND) & 0.00 & 0.00 & 0.81 &  \\ 
  Revenue (above 500 billion VND) & 0.00 & 0.00 & 0.53 &  \\ 
  Size (5-9 people) & 0.36 & 0.34 & 0.12 &  \\ 
  Size (10-49 people) & 0.21 & 0.24 & 0.05 & ** \\ 
  Size (50-199 people) & 0.06 & 0.05 & 0.49 &  \\ 
  Size (200-299 people) & 0.01 & 0.01 & 0.58 &  \\ 
  Size (300-499 people) & 0.00 & 0.00 & 0.20 &  \\ 
  Size (500-1000 people) & 0.00 & 0.00 & 0.81 &  \\ 
  Size (more than 1000 people) & 0.00 & 0.00 & 0.08 & * \\ 
  Main customer (State) & 0.19 & 0.19 & 0.57 &  \\ 
  Main customer (Private) & 0.58 & 0.62 & 0.02 & ** \\ 
  Main customer (Foreign in VN) & 0.05 & 0.04 & 0.33 &  \\ 
  Main customer (Foreign, direct) & 0.03 & 0.03 & 0.25 &  \\ 
  Main customer (Foreign, indirect) & 0.02 & 0.01 & 0.14 &  \\ 
  Equitized local state-owned enterprise & 0.05 & 0.06 & 0.21 &  \\ 
  Equitized central state-owned enterprise & 0.01 & 0.01 & 0.28 &  \\ 
  Firm with some state-owned equities & 0.03 & 0.02 & 0.26 &  \\ 
  Firm that was formerly household business & 0.74 & 0.73 & 0.24 &  \\ 
  Firm with shares listed & 0.01 & 0.00 & 0.39 &  \\ 
  Firm owner graduated from university & 0.62 & 0.63 & 0.91 &  \\ 
  Firm owner with MBA & 0.03 & 0.04 & 0.45 &  \\ 
  Firm owner was a leader of a State agency & 0.04 & 0.03 & 0.37 &  \\ 
  Firm owner was a military officer & 0.05 & 0.04 & 0.26 &  \\ 
  Firm owner was a manager of SOE & 0.13 & 0.12 & 0.22 &  \\ 
  Firm owner was an employee at SOE & 0.15 & 0.15 & 0.87 &  \\ 
   \hline
\end{tabular}       
}
\end{column}%
\begin{column}{.48\textwidth}
\onslide<2->
\adjustbox{max height=\textheight,
           max width=\textwidth}{
\begin{tabular}{rrrrl}
  \hline
 & Mean (resp) & Mean (non-resp) & p-value &   \\ 
  \hline
Limited Liability & 0.55 & 0.56 & 0.81 &  \\ 
  Joint Stock & 0.23 & 0.20 & 0.01 & ** \\ 
  Partnership & 0.00 & 0.00 & 0.75 &  \\ 
  Other form of ownership & 0.00 & 0.00 & 0.04 & ** \\ 
  Manufacturing & 0.09 & 0.08 & 0.42 &  \\ 
  Construction & 0.27 & 0.24 & 0.00 & *** \\ 
  Service & 0.67 & 0.68 & 0.15 &  \\ 
  Agriculture & 0.09 & 0.07 & 0.00 & *** \\ 
  Mining & 0.02 & 0.02 & 0.03 & ** \\ 
  Revenue (0.5-1 billion VND) & 0.22 & 0.22 & 0.98 &  \\ 
  Revenue (1-5 billion VND) & 0.43 & 0.41 & 0.20 &  \\ 
  Revenue (5-10 billion VND) & 0.08 & 0.08 & 0.84 &  \\ 
  Revenue (10-50 billion VND) & 0.05 & 0.05 & 0.91 &  \\ 
  Revenue (50-200 billion VND) & 0.01 & 0.01 & 0.52 &  \\ 
  Revenue (200-500 billion VND) & 0.00 & 0.00 & 0.85 &  \\ 
  Revenue (above 500 billion VND) & 0.00 & 0.00 & 0.26 &  \\ 
  Size (5-9 people) & 0.35 & 0.33 & 0.15 &  \\ 
  Size (10-49 people) & 0.22 & 0.23 & 0.77 &  \\ 
  Size (50-199 people) & 0.06 & 0.05 & 0.24 &  \\ 
  Size (200-299 people) & 0.01 & 0.01 & 0.93 &  \\ 
  Size (300-499 people) & 0.00 & 0.00 & 0.43 &  \\ 
  Size (500-1000 people) & 0.00 & 0.00 & 0.96 &  \\ 
  Size (more than 1000 people) & 0.00 & 0.00 & 0.67 &  \\ 
  Main customer (State) & 0.19 & 0.17 & 0.02 & ** \\ 
  Main customer (Private) & 0.60 & 0.63 & 0.01 & ** \\ 
  Main customer (Foreign in VN) & 0.04 & 0.04 & 0.96 &  \\ 
  Main customer (Foreign, direct) & 0.03 & 0.03 & 0.85 &  \\ 
  Main customer (Foreign, indirect) & 0.01 & 0.01 & 0.78 &  \\ 
  Equitized local state-owned enterprise & 0.06 & 0.05 & 0.35 &  \\ 
  Equitized central state-owned enterprise & 0.01 & 0.01 & 0.60 &  \\ 
  Firm with some state-owned equities & 0.03 & 0.02 & 0.52 &  \\ 
  Firm that was formerly household business & 0.73 & 0.70 & 0.00 & ** \\ 
  Firm with shares listed & 0.00 & 0.00 & 0.78 &  \\ 
  Firm owner graduated from university & 0.63 & 0.58 & 0.00 & *** \\ 
  Firm owner with MBA & 0.04 & 0.03 & 0.06 & * \\ 
  Firm owner was a leader of a State agency & 0.04 & 0.03 & 0.04 & ** \\ 
  Firm owner was a military officer & 0.05 & 0.04 & 0.12 &  \\ 
  Firm owner was a manager of SOE & 0.12 & 0.11 & 0.03 & ** \\ 
  Firm owner was an employee at SOE & 0.15 & 0.14 & 0.48 &  \\ 
   \hline
\end{tabular}          
}
\end{column}%
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Covariate Balance: Respondent vs Non-respondents}
\framezoom<1><2>[border=1](0cm,6.1cm)(7cm,1.5cm)
\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
           max width=\textwidth}{
\begin{tabular}{rrrrl}
  \hline
 & Mean (resp) & Mean (non-resp) & p-value &   \\ 
  \hline
Limited Liability & 0.55 & 0.56 & 0.81 &  \\ 
  Joint Stock & 0.23 & 0.20 & 0.01 & ** \\ 
  Partnership & 0.00 & 0.00 & 0.75 &  \\ 
  Other form of ownership & 0.00 & 0.00 & 0.04 & ** \\ 
  Manufacturing & 0.09 & 0.08 & 0.42 &  \\ 
  Construction & 0.27 & 0.24 & 0.00 & *** \\ 
  Service & 0.67 & 0.68 & 0.15 &  \\ 
  Agriculture & 0.09 & 0.07 & 0.00 & *** \\ 
  Mining & 0.02 & 0.02 & 0.03 & ** \\ 
  Revenue (0.5-1 billion VND) & 0.22 & 0.22 & 0.98 &  \\ 
  Revenue (1-5 billion VND) & 0.43 & 0.41 & 0.20 &  \\ 
  Revenue (5-10 billion VND) & 0.08 & 0.08 & 0.84 &  \\ 
  Revenue (10-50 billion VND) & 0.05 & 0.05 & 0.91 &  \\ 
  Revenue (50-200 billion VND) & 0.01 & 0.01 & 0.52 &  \\ 
  Revenue (200-500 billion VND) & 0.00 & 0.00 & 0.85 &  \\ 
  Revenue (above 500 billion VND) & 0.00 & 0.00 & 0.26 &  \\ 
  Size (5-9 people) & 0.35 & 0.33 & 0.15 &  \\ 
  Size (10-49 people) & 0.22 & 0.23 & 0.77 &  \\ 
  Size (50-199 people) & 0.06 & 0.05 & 0.24 &  \\ 
  Size (200-299 people) & 0.01 & 0.01 & 0.93 &  \\ 
  Size (300-499 people) & 0.00 & 0.00 & 0.43 &  \\ 
  Size (500-1000 people) & 0.00 & 0.00 & 0.96 &  \\ 
  Size (more than 1000 people) & 0.00 & 0.00 & 0.67 &  \\ 
  Main customer (State) & 0.19 & 0.17 & 0.02 & ** \\ 
  Main customer (Private) & 0.60 & 0.63 & 0.01 & ** \\ 
  Main customer (Foreign in VN) & 0.04 & 0.04 & 0.96 &  \\ 
  Main customer (Foreign, direct) & 0.03 & 0.03 & 0.85 &  \\ 
  Main customer (Foreign, indirect) & 0.01 & 0.01 & 0.78 &  \\ 
  Equitized local state-owned enterprise & 0.06 & 0.05 & 0.35 &  \\ 
  Equitized central state-owned enterprise & 0.01 & 0.01 & 0.60 &  \\ 
  Firm with some state-owned equities & 0.03 & 0.02 & 0.52 &  \\ 
  Firm that was formerly household business & 0.73 & 0.70 & 0.00 & ** \\ 
  Firm with shares listed & 0.00 & 0.00 & 0.78 &  \\ 
  Firm owner graduated from university & 0.63 & 0.58 & 0.00 & *** \\ 
  Firm owner with MBA & 0.04 & 0.03 & 0.06 & * \\ 
  Firm owner was a leader of a State agency & 0.04 & 0.03 & 0.04 & ** \\ 
  Firm owner was a military officer & 0.05 & 0.04 & 0.12 &  \\ 
  Firm owner was a manager of SOE & 0.12 & 0.11 & 0.03 & ** \\ 
  Firm owner was an employee at SOE & 0.15 & 0.14 & 0.48 &  \\ 
   \hline
\end{tabular}          
}
\end{frame}

\begin{frame}
\frametitle{Experimental Result}
\begin{table}
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & Contacting the National Assembly is effective \\ 
\hline \\[-1.8ex] 
 Treatment prompt & 0.264$^{***}$ \\ 
  & (0.073) \\ 
  & \\ 
 Constant & 0.929$^{***}$ \\ 
  & (0.049) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 3,951 \\ 
Log Likelihood & $-$2,253.137 \\ 
Akaike Inf. Crit. & 4,510.274 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
\end{frame}

\section{Large-N event data analysis}
\begin{frame}
\frametitle{Description of Data}
\begin{itemize}
\item Independent variable (\textit{legislature}): multiple parties are legal
\item Dependent variable (\textit{violence}): event data from news report, recording individual regime-opposition interaction. Violence is measured by the Goldstein scale (-10 to 10)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Empirical strategy}
\begin{itemize}
\item Create short panels of four country years
\item Treatment panel: no legislature in the first year, legislature in the next three years
\item Control panel: no legislature throughout the panel
\item Match panels based on the co-variates of the first years
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Matching result}
\centering
\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
           max width=\textwidth}{
\begin{tabular}{lrrlrrrl}
  \hline
 & \multicolumn{3}{c}{Pre-Match} &   \multicolumn{3\textbf{}}{c}{Post-Match} \\
Covariate & Treated & Control & p-value & Treated & Control & p-value &  \\ 
  \hline
Ethnic Fractionalization & 0.61 & 0.59 & 0.59 & 0.61 & 0.60 & 0.81 &  \\ 
Violence (Goldstein score) & -4.50 & -4.05 & 0.51 & -4.50 & -4.49 & 0.94 &  \\ 
$\text{Violence}^2$ & 29.84 & 23.22 & 0.34 & 29.84 & 29.03 & 0.65 &  \\ 
Regime duration (years) & 12.08 & 34.30 & 0.00*** & 12.08 & 12.71 & 0.71 &  \\ 
$\text{Regime duration}^2$ & 278.00 & 2783.57 & 0.00** & 278.00 & 287.38 & 0.89 &  \\ 
Military & 0.08 & 0.06 & 0.67 & 0.08 & 0.12 & 0.57 &  \\ 
Monarchy & 0.04 & 0.25 & 0.00*** & 0.04 & 0.04 & 1.00 &  \\ 
Party & 0.29 & 0.48 & 0.07* & 0.29 & 0.29 & 1.00 &  \\ 
log(gdp) & 22.65 & 23.95 & 0.00*** & 22.65 & 22.78 & 0.67 &  \\ 
log(gdp per capita) & 7.63 & 8.58 & 0.00*** & 7.63 & 7.65 & 0.95 &  \\ 
Military expenditure (\%GDP) & 2.44 & 4.34 & 0.00*** & 2.44 & 2.40 & 0.89 &  \\
Land (1000 $\text{km}^2$)& 760.22 & 1674.68 & 0.00*** & 760.21 & 783.37 & 0.80 &  \\ 
Population (million) & 22.62 & 140.73 & 0.00*** & 22.62 & 21.74 & 0.90 &  \\
Resource Export (\%GDP) & 14.79 & 22.64 & 0.03** & 14.79 & 14.16 & 0.72 &  \\ 
Resource $\times$ Ethnic & 8.61 & 14.43 & 0.01** & 8.61 & 8.33 & 0.82 & \\
  \hline
\end{tabular}
}
\end{frame}

\begin{frame}
\frametitle{Matching result}
\centering
\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
           max width=\textwidth}{
\begin{tabular}{lrlr}
  \hline
 \multicolumn{2}{c}{Treatment} &   \multicolumn{2}{c}{Control} \\
Country & Year & Country & Year \\ 
  \hline
Algeria & 1996 & Sudan & 1992 \\ 
  Angola & 1992 & Angola & 2000 \\ 
  Azerbaijan & 1992 & Uganda & 1991 \\ 
  Belarus & 2004 & Belarus & 2000 \\ 
  Cambodia & 1993 & Laos & 1999 \\ 
  Central African Republic & 2005 & Uganda & 2001 \\ 
  Chad & 1997 & Central African Republic & 1992 \\ 
  Congo, Republic & 2002 & Nigeria & 1994 \\ 
  Congo, Dem Rep & 2006 & Congo, Dem Rep & 1996 \\ 
  Ethiopia & 1995 & Ethiopia & 1993 \\ 
  Gambia & 1996 & Belarus & 2001 \\ 
  Ghana & 1995 & Belarus & 2000 \\ 
  Jordan & 1993 & Swaziland & 2007 \\ 
  Kazakhstan & 1995 & Sudan & 1994 \\ 
  Kenya & 1992 & Laos & 1997 \\ 
  Kyrgyzstan & 1995 & Belarus & 1998 \\ 
  Pakistan & 2002 & Algeria & 1993 \\ 
  Rwanda & 2003 & Rwanda & 1999 \\ 
  Sudan & 2000 & Sudan & 2006 \\ 
  Tajikistan & 1995 & Belarus & 1999 \\ 
  Tanzania & 1995 & Sierra Leone & 1992 \\ 
  Togo & 1994 & Togo & 1991 \\ 
  Uganda & 2006 & Uganda & 1998 \\ 
  Uzbekistan & 1999 & Ethiopia & 1993 \\ 
   \hline
\end{tabular}
}
\end{frame}

\begin{frame}
\frametitle{Multilevel model}
\begin{alignat*}{2}
&{event}_i &&\sim N(\alpha^{countryyear}_{j[i]} + A \cdot \text{sector}_i, \sigma^2_{event}) \\
&\alpha_j^{countryyear} &&\sim N(\beta_{k[j]}^{country} + \gamma \cdot \text{legis}_j + \Gamma X_j, \sigma_{\alpha}^2) \\
&\beta_k^{country} &&\sim N(\delta_0 + \delta_{ethnic} \cdot \text{ethnic}_k + D \cdot \text{region}, \sigma_\beta^2) 
\end{alignat*}
\end{frame}

\begin{frame}
\frametitle{Multilevel result}
\begin{table}[H]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & mean & 2.5\% & 97.5\% & Pr( $>$ 0) & Pr( $<$ 0) \\ 
  \hline
legislature & 0.48 & -0.29 & 1.25 & 0.89 &  \\ 
  log(GDP percap) & -0.39 & -1.31 & 0.52 &  & 0.81 \\ 
  log(GDP) & 0.37 & -0.19 & 0.92 & 0.91 &  \\ 
  resource (\%GDP) & -0.01 & -0.04 & 0.02 &  & 0.78 \\ 
  military exp (\%GDP) & -0.04 & -0.27 & 0.19 &  & 0.63 \\ 
  regime duration & 0.02 & -0.03 & 0.08 & 0.78 &  \\ 
  military regime & 2.10 & -1.79 & 5.84 & 0.86 &  \\ 
  personal regime & 1.60 & -1.65 & 4.89 & 0.83 &  \\ 
  party regime & 3.09 & -0.10 & 6.31 & 0.97 &  \\ 
   \hline
\end{tabular}
\caption{Hierarchical model parameter estimates}
\label{tab:hierarchical_estimate}
\end{table}
\end{frame}
%------------------------------------------------

\begin{frame}
\Huge{\centerline{The End}}
\end{frame}

\end{document}

### 2014-12-03 writeups/theory.tex
preparing slides

@@
 However, this type model is not suited to analyze the bargaining under an authoritarian regime, where the institutional rules themselves are under constant threat of being revised by the final arbiter that is violence.
-In other words, the end game of legislative bargaining now has an extra node: whether either side will violently suppress the other’s demand.
+In other words, the end game of legislative bargaining now has an extra node: whether either side will violently suppress the other's demand.
 Given this context, the decision of the autocrat and the opposition is better characterized as a bargaining game in anarchy, very much like the bargaining between two sovereign states with the option of going to war \citep{Fearon1995}.
@@
 Violence is costly compared to peaceful negotiation---we call this difference in relative cost $c_A$ and $c_O$ for the autocrat and the opposition, respectively.
-If violence happens, whichever side emerges victorious decides the share $x$ to his heart’s desire---i.e.
+If violence happens, whichever side emerges victorious decides the share $x$ to his heart’s desire---e.g.
 the winning autocrat would give 0 to the opposition and the winning opposition would give 1 to itself.
@@
 Given the uncertain nature of collective action battles, the utility of engaging in violence for the two sides is best formulated as an expected utility that depends on the probability of the opposition winning (call this probability $p$).
-Thus, the expected utility of the opposition is $p – c_O$, while the expected utility of the ruling regime is $1 - p - c_A$.
+Thus, the expected utility of the opposition is $p - c_O$, while the expected utility of the ruling regime is $1 - p - c_A$.
 These two expected utilities sum to less than one ($1 - c_A - c_O < 1$), which raises the puzzle why two sides fail to engage in ex-ante bargaining that splits the difference, giving both sides a higher payoff than the expected utility of violence.
@@
 \subsection{Legislature increasing violence}
-While the prevalent theory of legislature as an informational and commitment device favors hypothesis H1, it is important to note that there are reasons to susepct the opposite.
-Throughout the previous model, it is implied that the actors’ utility functions remain static with the only parameters being the cost of violence and the share of the issue space.
-Yet this assumption may miss the dynamism of the opposition’s democratic expectation, which becomes increasingly demanding as the regime starts liberalizing.
+While the prevalent theory of legislature as an informational and commitment device favors hypothesis H1, it is important to note that there are reasons to suspect the opposite.
+Throughout the previous model, it is implied that the actors' utility functions remain static with the only parameters being the cost of violence and the share of the issue space.
+Yet this assumption may miss the dynamism of the opposition's democratic expectation, which becomes increasingly demanding as the regime starts liberalizing.
 

### 2014-12-03 writeups/prelim_presentation.tex
more tweaks

@@
 
-\title[Effect of Authoritarian Legislature]{The Effect of Authoritarian Legislature on Regime-Opposition interaction} % The short title appears at the bottom of every slide, the full title is only on the title page
+\title[Effect of Authoritarian Legislature]{The Effect of Authoritarian Legislature on Regime-Opposition Interaction} % The short title appears at the bottom of every slide, the full title is only on the title page
 
@@
 \item Violence is the final arbiter in authoritarian politics
-\item Regime-opposition interaction is best modeled as a bargaining game, similar to the bargain between two sovereign states with the option of going to war
+\item Regime-opposition interaction is best modeled as a bargaining game, similar to the bargain between two sovereign states with the option of going to war (Fearon 1995)
 \end{itemize}
@@
 \begin{frame}
-\frametitle{The Model}
+\frametitle{Regime-Opposition Bargaining Game}
 \centering
@@
 \begin{frame}
-\frametitle{The Model}
+\frametitle{Regime-Opposition Bargaining Game}
 However, authoritarian legislature solves all of these issues
 \begin{itemize}
-\item Elections and legislative session provide information about both sides' capacity
-\item Cost of violent uprising and repression is increased relative to negotiation
-\item Negotiations over multiple issues in the legislature enable side payments
+\item<1> (Information Asymmetry) Elections and legislative session provide information about both sides' capacity
+\item<2> (Small Bargaining Range) Cost of violent uprising and repression is increased relative to negotiation
+\item<3> (Unit indivisibility) Negotiations over multiple issues in the legislature enable side payments
 \end{itemize}
@@
 \section{Experimental Design}
-%------------------------------------------------
+
+\begin{frame}
+\frametitle{Business in Vietnam}
+\end{frame}
+
 \begin{frame}
@@
 \begin{frame}
-\frametitle{Co-variate Balance}
+\frametitle{Checking Experimental Assumption}
+\centering
+\begin{itemize}
+\item<1-2> Balance between the Treated and the Control
+\item<3> Same response rate between the Treated and the Control
+\item<4-5> Balance between Respondents and Non-Respondents
+\end{itemize}
 \begin{columns}[T] % align columns
 \begin{column}{.48\textwidth}
-\adjustbox{max height=\textheight,
+\only<2,5>{\adjustbox{max height=0.3\textheight,
            max width=\textwidth}{
@@
 \end{tabular}       
-}
+}}
 \end{column}%
 \begin{column}{.48\textwidth}
-\onslide<2->
-\adjustbox{max height=\textheight,
+\only<5>{\adjustbox{max height=0.3\textheight,
            max width=\textwidth}{
@@
 \end{tabular}          
-}
+}}
 \end{column}%
@@
 \begin{frame}
-\frametitle{Empirical strategy}
+\frametitle{Empirical Strategy}
 \begin{itemize}
@@
 \begin{frame}
-\frametitle{Matching result}
+\frametitle{Matching Result}
 \centering
@@
 &{event}_i &&\sim N(\alpha^{countryyear}_{j[i]} + A \cdot \text{sector}_i, \sigma^2_{event}) \\
-&\alpha_j^{countryyear} &&\sim N(\beta_{k[j]}^{country} + \gamma \cdot \text{legis}_j + \Gamma X_j, \sigma_{\alpha}^2) \\
-&\beta_k^{country} &&\sim N(\delta_0 + \delta_{ethnic} \cdot \text{ethnic}_k + D \cdot \text{region}, \sigma_\beta^2) 
+&\alpha_j^{countryyear} &&\sim N(\beta_{k[j]}^{country} + \gamma \cdot \text{legislature}_j + \Gamma X_j, \sigma_{\alpha}^2) \\
+&\beta_k^{country} &&\sim N(\delta_0 + \delta_{ethnic} \cdot \text{ethnic fraction}_k + D \cdot \text{region}, \sigma_\beta^2) 
 \end{alignat*}
+where
+\begin{itemize}
+\item $\text{sector}_i$: fundamentalist, popular protest, insurgent, etc.
+\item $X_j$: log(GDP), log(GDP percap), resource rent, military expenditure, regime duration, type of autocracy
+\end{itemize}
 \end{frame}
